---
title: "IOTC ROS Data Reporting: Form ROS-LL"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  word_document2:
    reference_docx: "../../templates/doc_template.docx"
    number_sections: FALSE
    reference_num: TRUE
    fig_caption: TRUE

  html_document2:
    css: "../../templates/html_template.css"
    includes: 
      in_header: "../../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---

# Description

This form provides for the reporting of operational and catch data collected by scientific observers at sea, or from data reviewed through Electronic Monitoring Systems, for longline fisheries under the IOTC Regional Observer Scheme (ROS). It is designed to capture verified information on fishing activities, catch composition, bycatch associated with longline operations, and the implementation of mitigation measures. The reporting format follows standards adopted by the IOTC Scientific Committee (SC) and incorporates multiple hierarchical data levels, ranging from trip and set information to species-specific catch and bycatch records.

Click [here](./Form-ROS-LL.xlsx) to download a blank version of Form ROS-LL, or [return](../index.html) to the list of all IOTC data reporting forms.

# Data Content

Form ROS-LL is an XLSX workbook comprising 19 sheets, designed to report the mandatory (<span style="color: blue;">M; blue cells</span>) and optional (<span style="color: green;">O; green cells</span>) data fields defined by the SC. The current version builds on the most recent revision of ROS fields endorsed at the 27^th^ session of the SC ([IOTC-2024-SC27-DATA01](https://iotc.org/documents/SC/27/DATA01)). The sheets are interconnected through technical identifiers (e.g., observer trip ID, set ID), enabling the hierarchical organisation of the observations to be maintained.

| Sheet | Data Components | Resolution |  Description |
| :------------- | :----------: | :--------: | :--------------------------- |
| [META](#meta) |    Metadata | Trip | Information on the data submission by reporting fleet |
| [O-INFO](#oInfo) | Metadata | Trip | Observer identification and information of the observed fishing trip |
| [V-INFO](#vInfo) | Metadata | Trip | Identification of the fishing vessel and personnel information |
| [V-TRIP](#vTrip) | Metadata | Trip | Information on the fishing trip’s course |
| [V-ATTRIBUTES](#vAttributes) | Technology / Equipment | Trip | Information on the vessel’s attributes and equipment |
| [G-GENERAL](#gGeneral) | Gear configuration | Trip | Information on the fishing gear’s equipment and machinery | 
| [G-CONFIG-BRANCHLINES](#gConfigBranchlines) | Gear configuration | Trip | Information on longline branchline configurations |
| [G-CONFIG-MITIGATION-DEVICES](#gConfigMitigationDevices) | Gear configuration | Trip | Information on mitigation devices | 
| [E-SET](#eSet) | Gear Technology / Equipment | Operation | Information on setting by operations |
| [E-SET-LIGHTS](#eSetLights) | Gear Technology / Equipment | Operation | Information on the lights used for fish attraction |
| [E-SET_MITIGATION_MEASURES](#eSetMitigationMeasures) | Gear Technology / Equipment | Operation | Information on  configuration of mitigation devices |
| [E-SET-HOOKS](#eSetHooks) | Gear Technology / Equipment | Operation | Information on fishing hooks by operation |
| [E-SET-BAITS](#eSetBaits) | Gear Technology / Equipment | Operation | Information on fishing bait use by operation |
| [E-SET-HAULING](#eSetHauling) | Gear Technology / Equipment | Operation | Hauling  information by operation | 
| [E-SET-HAULING-BITEOFFS](#eSetHaulingBiteoffs) | Catch | Operation | Information on depredation events recorded during hauling |
| [E-SET-CATCHES](#eSetCatches) | Catch | Operation | Information on magnitude, composition, and fate of catch |
| [E-SET-CATCH-SPECIMENS](#eSetCatchSpecimens) | Catch | Species| Information on fish biology (size, sex, maturity), samples, and depredation |
| [E-SET-CATCH-SPECIMENS-SSI](#eSetCatchSpecimensSSI) | Catch | Species | Information Species of Special Interest (SSI) caught in the observed trip |
| [E-SET-TAG-DETAILS](#eSetTagDetails) | Catch | Species | Information on tag release or recovery by specimen |

# META {#meta}

## Submission Information

| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| Liaison officer full name | M | Name of the liaison officer in charge of the compilation of the data  | String | e.g., `John Doe`  |
| Liaison officer email | M | Email address of the liaison officer in charge of the compilation of the data | Valid email address | e.g., `John.Doe@fao.org` |
| Organisation name | M | Name of the organisation in charge of the compilation of the data | String | e.g., `Institute of Fisheries` |
| Organisation email | O | Email address of the organisation in charge of the compilation of the data | Valid email address | e.g., `nif@gov.sc` |
| Finalisation date | M | Date of finalisation of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | e.g., `1996-03-27` |
| [Submission date]{#subdate} | M | Date of submission of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | e.g., `1997-03-21` |

## General Information

| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| Reporting year | M | Gregorian calendar year of the fishing activities reported through the dataset | 4-digit integer | e.g., `1996` |
| Reporting entity | M | Three-letter (alpha-3) code of the entity reporting the dataset to the IOTC Secretariat | **Code** from [Entities](#entities) | e.g., `ABW` |
| Flag / Chartering state | M | The country registration of the fishing vessels or chartering flag in case of chartering agreement | **Code** from [Countries](#countries) | e.g., `FRA` |
| Data source | M | The source of the data, i.e., collected by observers at sea or derived from Electronic Monitoring Systems | **Code** from [Data Sources](#dataSources) | e.g., `OB` |

# O-INFO {#oInfo}

This section of the form includes information about the observer and an overview of the fishing trip they observed.

| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| observed_trip_id | M | Unique identifier of the fishing trip defined as the concatenation of (i) the observation or trip start date (YYYY-MM-DD), (ii) the IOTC observer identifier, (iii) the IOTC vessel identifier as per Record of Authorised Vessels ([RAV](https://rav.iotc.org/)) and the vessel [gear group](https://data.iotc.org/reference/latest/domain/fisheries/#gearGroups) code as per IOTC classification | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |

## Observer Identification

| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| observer_iotc_id | M | The unique registration identifier assigned to each observer by the IOTC Secretariat | Alphanumeric | e.g., `IOTC_0976` |
| observer_full_name | M | The full name of the scientific observer who collected the data onboard the fishing vessel, or of the Electronic Monitoring reviewer, recorded as first and last names | String | e.g., `John Doe` |

## Observed Trip Details

| **Embarkation:** The starting port. If the first observation is available after the departure from the port while the vessel is within port limits, this is still recorded as the observation starting port. If the observation starts at sea outside port limits (onboard observer boarding the vessel via a vessel transfer or EM records not available at the trip starting date due to a recording failure), record "at sea".

::: {style="margin-left:40px"}
| **In port**
:::

::: {style="margin-left:80px"}
| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| country | O | The country or EEZ of the observation starting location | **Code** from [Countries](#countries) | e.g.,`FRA` |
| port | O | The port of the observation starting location | **Code** from [Ports](#ports) | e.g., `REUREU` |
:::

::: {style="margin-left:40px"}
| **At sea**
:::

::: {style="margin-left:80px"}
| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| latitude  | O | The latitude of the observation starting location | Decimal degrees (two decimal places) | e.g., `-20.88` |
| longitude | O | The longitude of the observation starting location | Decimal degrees (two decimal places) | e.g., `55.53` |
:::

::: {style="margin-left:40px"}
||||||
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| date_time_UTC | O | The date and time of the start of observations | YYYY-MM-DD hh:mm | e.g., `2025-09-15 12:00` |
:::

| **Disembarkation:** The ending port. If the last observation is available after a port launch while the vessel is within port limits, this is still recorded as the observation ending port. If the observation ends at sea outside port limits (onboard observer disembarking the vessel via a vessel transfer or EM records not available at the end of observations due to a recording failure) , record "at sea"
|

::: {style="margin-left:40px"}
| **In port**
:::

::: {style="margin-left:80px"}
| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| country | O | The country or EEZ of the observation ending location | **Code** from [Countries](#countries) | e.g.,`FRA` |
| port | O | The port of the observation ending location | **Code** from [Ports](#ports) | e.g., `REUREU` |
:::

::: {style="margin-left:40px"}
| **At sea**
:::

::: {style="margin-left:80px"}
| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| latitude | O | The latitude of the observation ending location | Decimal degrees (two decimal places) | e.g., `-20.88` |
| longitude | O | The longitude of the observation ending location | Decimal degrees (two decimal places) | e.g., `55.53` |
:::

::: {style="margin-left:40px"}
|  |  |  |  |  |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| date_time_UTC | O | The date and time of the end of observations | YYYY-MM-DD hh:mm | e.g., `2025-09-15 12:00` |
:::

## Observed Trip Summary

| **Number of fishing sets:** The total number of longline sets deployed by the vessel or observed by the scientific observer during a single fishing trip. Each set corresponds to one complete deployment of the longline gear.

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| conducted | M | The total number of fishing sets conducted by the vessel from the observation starting date to the observation ending date, regardless their catch and data collection activities | Integer | `20`  |
| observed | M | The total number of fishing sets monitored by the observer. In the case of Electronic Monitoring, only processed sets to be included | Integer | `17` |
:::

| **Number of days:** The total number of calendar days the vessel is on a fishing trip, with each day defined as a 24-hour period. These days can be further categorised by activity type (e.g. searching, transiting, actively fishing, or present in fishing areas).

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| searching | O | The number of days searching during the observation period | Integer | e.g., `31.2` |
| actively_fishing | O | The number of active fishing days during the observation period | Integer | e.g., `43.1` |
| in_fishing_area | O | The number of days in the fishing area during the observation period | Integer | e.g., `45.8` |
| transiting | O | The number of days transiting during the observation period | Integer | e.g., `5.0` |
| lost | O | The number of days lost during the observation period | Integer | e.g., `1.1` |
:::

| **Reasons for lost days:** Record the reason(s) a vessel was unable to fish: (i) adverse weather conditions, (ii) mechanical breakdown or inoperative gear or (iii) unforeseen events (specify).

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| reason | O | The main reasons for days at sea lost to fishing activity | **Code** from [Reasons for Days Lost](#reasonsDaysLost) | e.g., `AW` |
:::

# V-INFO {#vInfo}

This section of the form includes specific vessel information.

| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:------------------------|:---------:|:----------------:|
| observed_trip_id | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |

## Vessel Information

| **Identification:** Unique identifiers and key details of the vessel to uniquely identify the vessel in fisheries and observer records.

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| name | M | The vessel full name as recorded on vessel official documentation or record the vessel full name as imprinted on the vessel itself or Electronic Monitoring records | String | e.g., `HAWWA` |
| flag_or_chartering_state | M | The country code of registration or chartering | **Code** from [Countries](#countries) | e.g., `OMN` |
| iotc_ID | M | The unique identification number assigned to the vessel by the IOTC when it is included in the Record of Authorised Vessels | Alphanumeric | e.g., `IOTC003810` |
| imo_number | O | The unique vessel identification number assigned by the International Maritime Organization | Seven-digit number | e.g., `9359698` |
| ircs | O | The unique alphanumeric code (International Radio Call Sign; IRCS) assigned to the vessel for radio communications, as recorded in official registration documents radio call sign (when available) | Alphanumeric | e.g., `A4DP6` |
:::

| **Registration:** Official vessel registration details to uniquely identify the vessel within the national or regional registry.

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| country | O | The vessel's country of registry | **Code** from [Countries](#countries) | e.g., `FRA` |
| port | O | The vessel's port of registry (also called home port) shown on its registration documents and lettered on the stern of the ship's hull | **Code** from [Ports](#ports) | e.g., `REUREU` |
| registration_number | O | The number issued by country in which the vessel is registered, shown on its registration documents and written on the hull of the vessel | Alphanumeric or numeric entry according to CPC standards | e.g., `CBG303` |
:::

| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| licensed_target_species | O | The licensed target species as specified in vessel licences or permit conditions | **Code** from [Target Species](#targetSpecies) | e.g., `AL` |
| main_fishing_gear | M | The vessel main fishing gear | **Code** from [Fishing Gear](#fishingGear) | e.g., `DL` |

| **Vessel Personnel:** Details of the individuals working onboard during the fishing trip as well as the total number of crew members onboard.

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| fishing_master_name | M | The full name of the fishing master recorded as first and last names | String | e.g., `John Doe` |
| fishing_master_nationality | M | The nationality of the fishing master | **Code** from [Countries](#countries) | e.g., `FRA` |
| skipper_captain_name | M | Name of the skipper or captain recorded as first and last names| String | e.g., `John Doe` |
| skipper_captain_nationality | M | Nationality of the skipper or captain | **Code** from [Countries](#countries) | e.g., `FRA` |
| crew_number | O | The number of crew onboard the vessel during the trip | Integer | e.g., `26` |
:::

# V-TRIP {#vTrip}

This section of the form includes information on the course and duration of the vessel's fishing trip.

| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:------------------------|:---------:|:----------------:|
| observed_trip_id | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |  

## Trip Details

| **Vessel departure:** The name and/or geographical coordinates of the port from where the vessel sailed – also include the country. If the vessel started a new trip at sea following transshipment record 'at-sea’ plus the geographical coordinates corresponding to the location the trip started.

::: {style="margin-left:40px"}
| **In port**
:::

::: {style="margin-left:80px"}
| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| country | O | The country or EEZ of the observation starting location | **Code** from [Countries](#countries) | e.g., `FRA` |
| port | O | The port of the observation starting location | **Code** from [Ports](#ports) | e.g., `REUREU` |
| latitude | O | The latitude of the observation starting location | Decimal degrees (two decimal places) | e.g., `-20.88` |
| longitude | O | The longitude of the observation starting location | Decimal degrees (two decimal places) | e.g., `55.53` |
:::

::: {style="margin-left:40px"}
|               |     |     |                  |                       |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| date_time_utc |  O  | The date and time (in Coordinated Universal Time, UTC) corresponding to the start of the observation period at the reported location | YYYY-MM-DD hh:mm | e.g., `2025-09-15 12:00` |
:::

| **Vessel return:** The name and/or geographical coordinates of the port where the vessel returned – also include the country. If the vessel arrived at a transshipment location record 'at-sea' plus the geographical coordinates corresponding to the location the transshipment started. If the observer disembarked before the vessel returned then record expected port of return as provided by the vessel.

::: {style="margin-left:40px"}
| **In port**
:::

::: {style="margin-left:80px"}
| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| country | O | The country or EEZ of the observation ending location | **Code** from [Countries](#countries) | e.g., `FRA` |
| port | O | The port of the observation ending location | **Code** from [Ports](#ports) | e.g., `REUREU` |
| latitude | O | The latitude of the observation ending location | Decimal degrees (two decimal places) | e.g., `-20.88` |
| longitude | O | The longitude of the observation ending location | Decimal degrees (two decimal places) | e.g., `55.53` |
:::

::: {style="margin-left:40px"}
|               |     |     |                  |                        |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| date_time_UTC |  O  | The date and time (in Coordinated Universal Time, UTC) corresponding to the end of the observation period at the reported location | YYYY-MM-DD hh:mm | e.g., `2025-09-15 12:00` |
:::

# V-ATTRIBUTES {#vAttributes}

This section of the form includes details on vessel attributes.

| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:------------------------|:---------:|:----------------:|
| observed_trip_id | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |

## Vessel Attributes

| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| gross_tonnage | O | Gross tonnage (GT), a dimensionless measure of vessel's internal volume from registration documents | Integer | e.g., `2319` |
| loa_m | O | The vessel overall length (m) as specified in vessel registration documents | Floats | e.g., `84.1` |
| hull_material | O | The primary material used in the construction of the vessel's hull | **Code** from [Hull Material Types](#hullMaterialTypes) | e.g., `AL` |

| **Main engines:** The make (brand) and power of the two main engines.

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| make | O | The manufacturer or brand name of the vessel's engine, as specified in the official vessel registration or engine documentation | String | e.g., `MAN Energy Solutions`  |
| power_value | O | The rated power output of the vessel's main engine as specified in the official vessel registration or engine documentation | Integer | e.g., `5000` |
| power_unit | O | Rated output of the vessel's main engine, as specified in official registration or engine documentation in kilowatts (kW), horsepower (hp), or break horsepower (bhp) | String | e.g., `kW` |
:::

||||||
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| fish_storage_capacity_m3 | O | Total volume of fish hold(s)(cubic metres; m^3^) | Float | e.g., `1100` |

::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| preservation_method | O | The fish preservation methods used by the vessel to preserve the catch. Up to four preservation methods may be reported on the form | **Code** from [Fish Preservation Methods](#fishPreservationMethods) | e.g., `BR` |
::: 

::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| storage_type | O | The type of structure(s) onboard used by the vessel to store its catch. Up to three storage types may be reported on the form. |  **Code** from [Fish Storage Types](#fishStorageTypes) | e.g., `BF` |
:::

| **Autonomy range:** Vessel autonomy, expressed as the number of days a vessel can remain at sea without refuelling. If this information is not available, autonomy may be expressed as cruising distance (nm).

<!--FOR OBSEVER GUIDELINES -  If a figure for the range cannot be obtained, the observer should calculate vessel range as follows: Vessel range (nm)\> = \<Vessel average cruising distance per metric tonne (nm/t)\> : \<Tonnage of fuel carried (t)\> -->

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| range_value | O | The vessel's operational endurance, expressed either as the maximum number of days it can remain at sea without resupply, or as the maximum distance it can cover (in nautical miles, nm) | Float | e.g., `30` |
| range_unit  | O | The unit used to describe the value of autonomy range | days or nm | e.g., `days` |
:::

## Vessel Electronics

| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| gnss | O | Indicates whether or not one or more Global Navigation Satellite System systems (GNSS) such as the US Global Positioning System (GPS) were present on the vessel (Yes/No/Unk) | String | e.g., `Yes` |
| vms | O | Indicates whether or not one or more Vessel Monitoring Systems (VMS) were present on the vessel (Yes/No/Unk)  | String | e.g., `Yes` |
| ais | O | Indicates whether or not one or more Automatic Identification Systems (AIS) were present on the vessel (Yes/No/Unk) | String | e.g., `Yes` |
| radars | O | Indicates whether or not one or more radars were present on the vessel (Yes/No/Unk) | String | e.g., `Yes`  |
| track_plotter | O | Indicates whether or not one or more track plotters were present on the vessel (Yes/No/Unk) | String | e.g., `Yes` |
| depth_sounder | O | Indicates whether or not one or more depth sounders were present on the vessel (Yes/No/Unk)| String | e.g., `Yes` |
| sonar | O | Indicates whether one or more sonars were present on the vessel (Yes/No/Unk) | String | e.g., `Yes` |
| doppler_current_meter | O | Indicates whether one or more doppler current meters were present on the vessel | String | e.g., `Yes` |
| xbt | O | Indicates whether or not one or more expendable bathythermographs (XBT) were present on the vessel | String | e.g., `Yes` |
| vhf_radios | O | Indicates whether or not one or more VHF radios weere present on the vessel | String | e.g., `Yes` |
| hf_radios | O | Indicates whether one or more HF radios were present or not on the vessel | String | e.g., `Yes` |
| satcom | O | Indicate whether or not one or more satellite communication systems were present on the vessel | String | e.g., `Yes` |
| fis | O | Indicates whether or not one or more Fisheries Information Services were present on the vessel | String | e.g., `Yes` |

## Waste Management Details

::: {style="margin-left:40px"}
| Waste Management Details: Up to four categories of waste and storage disposal may be reported on the form.
:::

::: {style="margin-left:80px"}
| Field | Requirement | Description | Format | Input value |
|:-----------------|:------------:|:------------------------|:------------:|:------------:|
| waste_management_category | O | The category of the waste produced by the vessel | **Code** from [Waste Categories](#wasteCategories) | e.g., `CP` |
| waste_storage_disposal_method | O |	The method used to dispose of the waste | **Code** from [Storage / Disposal Methods](#storageDisposalMethods)| e.g., `AS` |
:::

# G-GENERAL {#gGeneral}

This section of the form includes general longline gear configuration.

| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| observed_trip_id | M | The parent observed trip identifier | Alphanumeric | `2024-01-23/IOTCFRA001/IOTC012345/LL` |

## Special Equipment or Machinery

| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| line_setter | M | Indicates whether or not the vessel is equipped with a line setter or shooter (Yes/No/Unk) | String | e.g., `Yes` |
| line_hauler | M | Indicates whether or not the vessel is equipped with a line hauler (Yes/No/Unk) | String | e.g., `Yes` |
| bait_casting_machine | M | Indicates whether or not the vessel is equipped with a bait cast machine (Yes/No/Unk) | String | e.g., `Yes` |

# G-CONFIG-BRANCHLINES {#gConfigBranchlines}

| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:------------------------|:---------:|:----------------:|
| observed_trip_id | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |

## Branchline Configurations

| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| configuration_id | O | The identifier for a specific branchline specification as detailed based on the fields below | Integer | e.g., `BL_1` |
| section_id | O | The identifier for a specific branchline section  | Integer | e.g., `BL_1#1` |
| material_type | O | The type of material used in each of the four sections of the branchline, where section 1 is that closest to the mainline and section 4 is the leader; note that wire trace may be sheathed by a plastic or nylon coating | **Code** from [Line Material Types](#lineMaterialTypes) | e.g., `NL` |
| branchline_length_m | O | The value of the length (m) of the branchline for each of the four sections where section 1 is that closest to the mainline and section 4 is the leader | Float | e.g., `15.3` |
| branchline_diameter_cm | O | The value of the diameter (cm) of the branchline for each of the four sections where section 1 is that closest to the mainline and section 4 is the leader | Float | e.g., `1.2` |

## Additional Branchline Details

| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| storage | O | The storage method for the branchlines. Up to four storage methods may be reported on the form | **Code** from [Branchline Storages](#branchlineStorages) | e.g., `BA` |

# G-CONFIG-MITIGATION-DEVICES {#gConfigMitigationDevices}

This section of the form includes information about the mitigation devices present on the vessel.

| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:------------------------|:---------:|:----------------:|
| observed_trip_id | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |

## Tori Line Details

A tori line is a mitigation device used in longline fisheries to reduce seabird bycatch. It is a streamer line towed from a high point at the stern of the vessel during line setting. The device consists of a main line with brightly coloured streamers attached at intervals, which flutter in the wind and touch the water surface, creating a visual barrier that deters seabirds from approaching and taking baited hooks as they sink.

| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| tori_line_length | M | The total length (m) of the tori line, excluding streamers | Float | e.g.,`150` |
| streamer_type | M | The type of streamers which are used with the tori line | **Code** from [Streamer Types](#streamerTypes) | e.g., `MU` |
| reach_surface | O | Indicates whether or not the streamers are long enough to touch the surface of the water in calm conditions (Yes/No/Unk) | String | `No` |
| streamer_line_length_max_m | M | The value of the maximum length (m) of individual streamer lines | Float |e.g., `10` |
| streamer_line_length_min_m | O | The value of the minimum length (m) of individual streamer lines | Float | e.g.,`1` |
| streamer_number_per_line | M | The number of streamers that are attached to a single tori line | Integer | e.g., `20` |
| distance_between_streamers_m | O | The distance (m) between streamers | Float | e.g., `5` |
| tori_line_attached_height_m | M | The height that the tori line is attached above the water level | Float | e.g., `8` |
| towed_objects_type | O | The type of object used to maintain tori line tension and to achieve aerial extent when deployed | `tbd` | `tbd` |
| towed_objects_number | O | Number of objects used to maintain tori line tension and to achieve aerial extent when deployed | Integer | Integer | `tbd` |

## Other Mitigation Devices

| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| device | O | Equipment used onboard to minimise bycatch. Up to five additional devices may be reported on the form | **Code** from [Mitigation Devices](#mitigationDevices) | e.g., `AA` |

# E-SET {#eSet}

This section of the form includes information regarding individual sets that were observed during the fishing trip.

| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| observed_trip_id | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` | 
| set_id | M | The unique four-digit numerical code for each fishing set, beginning with 0001 and assigned consecutively from the first to the last line set of the observed trip | 4-digit number | e.g, `0007` |

## Setting Operations

| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| start_setting |||||

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| date_time_utc | M | The date and time (in Coordinated Universal Time, UTC) the first dhan buoy and / or radio buoy is deployed to start the setting of the line | YYYY-MM-DD hh:mm | e.g., `2025-09-15 12:00` |
| latitude | M | The latitude of the position at the start of the setting operation | Decimal degrees (two decimal places) | e.g., `-20.88` |
| longitude | M | The longitude of the position at the start of the setting operation | Decimal degrees (two decimal places) | e.g., `55.53` |
:::

| End setting

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| date_time_utc | M | The date and the time (in Coordinated Universal Time, UTC) that the last dhan buoy and / or radio buoy is deployed | YYYY-MM-DD hh:mm | e.g., `2023-07-01 12:00` |
| latitude | M | The latitude of the position at the end of the setting operation | Decimal degrees (two decimal places) | e.g., `-20.88` |
| longitude | M | The longitude of the position at the end of the setting operation | Decimal degrees (two decimal places) | e.g., `55.53` |
:::

||||||
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| vessel_speed_kn | M | The vessel's average speed expressed in knots (kn) during setting | Float | `5.5` |
| line_setter_speed_ms | M | The speed setting (m/s) of the line setter | Float | `0.4` |

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| mainline_material | O | The type of material used to construct the mainline of the longline gear | **Code** from [Line Material Types](#lineMaterialTypes) | e.g., `NL` |
| mainline_length_value | O | The total deployed length of the mainline for the specific set. Usually calculated by multiplying the total time to set the line and the average line setter speed, taking into account any interruption times | Float | `120.2` |
| mainline_length_unit | O | The unit used to report the length of the mainline, expressed in kilometres (km) or nautical miles (nm) | `km` |
:::

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| clip_on_time_branchline | O | The average time interval, in seconds (s), between the audible signals ('beeps') that indicate to the crew when to clip on a branchline | Float | `10` |
| clip_on_time_buoys | O | The average time interval, in seconds (s), between the audible signals ('beeps') that indicate to the crew when to clip on a buoy | Float | `850` |
:::

||||||
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| number_of_total_hooks_set | M | The total number of hooks deployed for the set. Usually calculated by multiplying number of baskets by the average number of hooks between the baskets | Integer | e.g., `3000` |
| number_of_total_floats_on_set | O | The total number of floats deployed during the set, excluding radio/dhan buoys. Usually calculated by subtracting the number of buoys in their holders before setting by the number of buoys in their holders after setting | Integer | e.g., `6` |
| number_of_hooks_between_floats | M | The number of hooks set between floats, corresponding to the number of hooks stored in each basket, tub, or reel, and equivalent to the number of branchlines deployed | Integer | e.g., `1000` |

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| shark_lines_set | M | Indicates whether or not shark lines were set during the operation (Yes/No/Unk) | String | e.g., `No` |
| shark_lines_number | O | The number of shark lines set during the operation | Integer | e.g., `0` |
:::

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| leader_material_type | M | The type of material used to construct the leader type used in the set | **Code** from [Line Material Types](#lineMaterialTypes) | e.g., `NL` |
| leader_material_percentage | M | The percentage of total branchlines in the set estimated for each leader type used | Float |  e.g., `25` |
:::

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| branchline_length_minimum | M | The minimum value of the total lengths of the branchlines deployed during the fishing set | Float | e.g., `12` |
| branchline_length_minimum_unit | M | The unit of measurement of the minimum value of branchline length (cm or m) | Float | `m` | 
| branchline_length_maximum | M | The maximum value of the total lengths of the branchlines deployed during the fishing set | Float | e.g., `20` |
| branchline_length_maximum_unit | M | The unit of measurement of the maximum value of branchline length (cm or m) | Float | `m` | 
:::

||||||
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| target_species | M | The list of species that are intentionally targeted in the fishery. Up to four target species may be reported on the form | **Code** from [Target Species](#targetSpecies) | e.g., `AL` |

# E-SET-LIGHTS {#eSetLights}

This section of the form includes information about the lights present for each set that were observed during the fishing trip.

| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| observed_trip_id | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |
| set_id | M | The parent set identifier | 4-digit number | e.g., `0001` |

## Attached Lights

| Attached lights: Lights attached to the branchlines.

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| light_type | M | The type of lights attached to the longline when deployed, classified according to their source of illumination | **Code** from [Light Types](#lightTypes) | e.g., `CL` |
| light_colour | M | The colour of lights attached to the longline when deployed, recorded according to the dominant visible light colour | **Code** from [Light Colours](#lightColours) | e.g., `BU` |
| number_of_lights | M | The number of lights deployed | Integer |  e.g., `546` |
:::

# E-SET-MITIGATION-MEASURES {#eSetMitigationMeasures}

This section of the form includes information about the mitigation measures observed in each set of the fishing trip.

| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| observed_trip_id | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |
| set_id | M | The parent set identifier | 4-digit number | e.g., `0001` |

## Mitigation Measures

| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| number_of_tori_lines_deployed | M | The total number of tori lines deployed during the setting operation | Integer | e.g., `8` |
| minimum_deck_lighting_used | M | Indicates whether or not minimum deck lighting was used during night setting (Yes/No/Unk) | String | e.g., `Yes` |
| branchline_weighted | O | Indicates whether or not the branchline was weighted (Yes/No/Unk) | String | `No` |
| average_sinker_weight_g | M | The average weight (g) of weights or sinkers attached to the branchlines (weights deployed on the snood prior to setting) | Float |  e.g., `60` |
| percent_branchline_weighted | M | The proportion of branchlines weighted (%) | Float |  e.g., `100` |
| hook_sinker_distance | M | The distance (cm) of the weights/sinkers from the eye of the hook | Float |  e.g., `765` |
| hook_pods | M | Indicates whether or not the bait is protected by hook pods on the branchlines until they are a certain depth below the surface (Yes/No/Unk) | String | e.g., `No` |

## Branchline Details

| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| configuration_id | O | Identifier of the branchline configuration | Alphanumeric code | e.g., `BL_1` |
| number_of_branchlines_set | O | The number of branchlines set by type | Integer | e.g.,`20`  |

## Other Mitigation Measures Used

| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| measure | M | Any other mitigation measures observed. Up to four measures can be reported on the form | **Code** from [Mitigation Devices](#mitigationDevices) | e.g., `AA` |

# E-SET-HOOKS {#eSetHooks}

This section of the form includes information about the specific hooks observed in each set of the fishing trip.

| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:------------------------|:---------:|:----------------:|
| observed_trip_id | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |
| set_id | M | The parent set identifier | 4-digit number | e.g., `0004` |

## Hook Details

| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| hook_type | M | The type of hooks used | **Code** from [Hook Types](#hookTypes) | e.g., `C13` |
| percentage | O | The percentage (%) of hooks set by type | Float | **100** |
| variations | O | Indicates any variations in hook type, hook material, and presence/absence of hook ring where possible | String | `tbd` |

# E-SET-BAITS {#eSetBaits}

This section of the form includes information about the specific baits observed in each set of the trip.

| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| observed_trip_id | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |
| set_id | M | The parent set identifier | 4-digit number | e.g., `0095` |

## Bait Details

| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| condition | M | The bait type condition used | **Code** from [Bait Conditions](#baitConditions) | e.g., `DE`  |
| species | M | The species/species group of bait used | **Code** from [Bait Species](#baitSpecies) | e.g., `ANX` |
| percentage | M | The approximate proportion (%) of bait species and condition used across all hooks in the set | Float | e.g., `70` |
| dye_colour | O | The colour(s) that the different baits are dyed | String | e.g., `blue`  |

# E-SET-HAULING {#eSetHauling}

This section includes specific hauling information observed for each set of the fishing trip.

| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| observed_trip_id | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |
| set_id | M | The parent set identifier | 4-digit number | e.g., `0084` |

## Hauling Operations

| **Start hauling**

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| date_time_utc | M | The date and the time (in Coordinated Universal Time, UTC) when the first dhan buoy and / or radio buoy is hauled back on-board to start hauling the line | YYYY-MM-DD hh:mm | e.g., `2025-09-15 12:00` |
| latitude | O | The latitude of the position at the start of the hauling operation | Decimal degrees (two decimal places) | e.g., `-20.88` |
| longitude | O | The longitude of the position at the start of the hauling operation | Decimal degrees (two decimal places) | e.g., `55.53` |
:::

| **End hauling**

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| date_time_utc | M | The date and the time (in Coordinated Universal Time, UTC) when the last component of the longline gear (dhan buoy and / or radio buoy) is hauled back on-board | YYYY-MM-DD hh:mm | e.g., `2025-09-15 12:00` |
| latitude | O | The latitude of the position at the end of the hauling operation | Decimal degrees (two decimal places) | e.g., `-20.88` |
| longitude | O | The longitude of the position at the end of the hauling operation | Decimal degrees (two decimal places) | e.g., `55.53` |
:::

||||||
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| offal_management | O | The fate given to the offal (fish heads, guts, etc.) and bait produced during the observed set | **Code** from [Offal Management Types](#offalManagementTypes) | e.g., `AH` |
::: {style="margin-left:40px"}
| Field | Requirement | Description | Format  | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| position | O | The position(s) where offal and used bait was disposed. Up to four positions of offal and bait disposal may be reported on the form |  **Code** from [Vessel Section](#vesselSection) | e.g., `BW`  |
:::

||||||
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| bird_scaring_device_at_hauler | M | Indicates whether or not a bird scaring device was deployed during hauling operations (Yes/No/Unk) | String | e.g., `No`  |
| number_of_branchline_haulings_observed | M | The number of branchline haulings observed | Integer | e.g., `800` |
| number_of_hooks_retrieved_during_observation | M | The number of hooks retrieved observed | Integer | e.g., `1274` |
| sampling_protocol | M | Sampling protocol followed by the observer | **Code** from [Sampling Protocol](#samplingProtocol) | e.g., `EP` |

# E-SET-HAULING-BITEOFFS {#eSetHaulingBiteoffs}

This section of the form includes information about individual biteoffs for each set within a fishing trip.

| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| observed_trip_id | M | Refers to parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |
| set_id | M | Refers to parent set identifier | 4-digit number | e.g., `0023` |

## Biteoff Details - Branchline

For each branchline configuration set-up previously identified how many have had the hook bitten off. This only includes biteoffs observed while the observer was in a position to observe and record the hooks coming directly out of the water.

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format  | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| branchline_configuration_id | O | The identifier of the branchline configuration | Integer | e.g.,`-` |
| number_of_biteoffs | O | The number of biteoffs observed | Integer | e.g., `1680` |
:::

# E-SET-CATCHES {#eSetCatches}

This section of the reporting form includes information on individual species from a subset of a set that is observed.

| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| observed_trip_id | M | Refers to parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |
| set_id | M | Refers to parent set identifier | 4-digit number | e.g., `0285` |
| catch_id | M | Unique identifier of the species-specific part of the catch, within a trip | Alphanumeric code | e.g., `02851` |

## Catch Details

| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| species | M | Species of individual specimen | **Code** from [All Species](#allSpecies) | e.g., `ABL` |

| **Fate**: The fate which includes whether it was retained or discarded and the reason.

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format  | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| fate_type | M | The outcome of the catch, indicating whether a fish was retained on board or discarded | **Code** from [Types of Fate](#fateType) | e.g., `DI` |
| fate | M | The final disposition of the catch or sampled portion of the catch, indicating whether it was retained on board or discarded, with specification of the reason where applicable | **Code** from [Fates](#fates) | e.g., `DL` |
:::

||||||
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| sampling_method | M | Method applied to derive the total catch from the samples collected during observation | **Code** from [Sampling Methods for Catch Estimation](#samplingMethodsCatchEstimation) | e.g., `EP` |
| number_of_fish | M | The numbers of individuals observed/caught by species and fate (including if recording at an individual animal level) | Integer | e.g., `7` |

**Weight:** The catch weight corresponding to the specified species and product type recorded in processing type. If the fish has not been processed, it corresponds to the unprocessed weight.

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| processing_type | O | Form in which the fish is processed prior to storage | **Code** from  [Fish Processing Types](#fishProcessingTypes) | e.g., `DR` |
| value_kg | O | The value of fish weight expressed in kilograms (kg) | Float | `153` |
| estimation_method | O | Method applied to derive the weight from the samples collected during observation | **Code** from [Sampling Methods for Catch Estimation](#samplingMethodsCatchEstimation) | e.g., `EP` |
:::

# E-SET-CATCH-SPECIMENS {#eSetCatchSpecimens}

This section of the form is for the recording of biological information of the specimens sampled during individual sets.

| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| observed_trip_id | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |
| set_id | M | The parent set identifier | 4-digit number | e.g., `0003` |
| catch_id | M | The parent catch identifier | Alphanumeric code | `C188` |
| specimen_id | M | A unique four-digit numerical code for each specimen, beginning with 0001, assigned consecutively within the same catch detail of a set during the observed trip | 4-digit number | e.g., `0005` |

## Specimen Details

| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| sampling_period | M | Stage period when the specimen was sampled | **Code** from [Sampling Period](#samplingPeriod) | e.g., `BS` |
| sampling_method | M | The sampling method used for the collection of biological sub-sample(s) | **Code** from [Biological Sampling Method](#biologicalSamplingMethod) | e.g., `ES` |

| Length : The specimen's individual length corresponding to the specified length type. Up to two length measurements may be reported on the form.

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| length_type | M | The type of length used for the measurement | **Code** from [Length Measurements](#lengthMeasurements) | e.g., `CF` |
| length_value_cm | M | The value of length corresponding to the length type taken rounded to the lower centimetre | Float | e.g., `34` |
| length_measuring_tool tool | M | The tool used for the measurement of the fish length | **Code** from [Length Measurement Tools](#lengthMeasurementTools) | e.g., `CA`  |
| is_straight | M | Indicates whether the size measurement was made straight (Yes/No/Unk) | String | e.g., `Yes` |
:::

| **Weight**: The specimen's individual weight corresponding to the specified specie and product type. Unprocessed weight when the fish has not been processed.

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| weight_processing_type | O | The processing/dressing used for the weight measurement | **Code** from [Weight Measurements](#weightMeasurements)  | e.g., `GG` |
| weight_value_kg | O | The weight corresponding to the weight measurement type code | Float | e.g., `43.2` |
| weight_estimation_method | O | The method used to estimate the weight of the specimen | **Code** from [Weight Measurement Tools](#weightMeasurementTools) | e.g., `BR` |
:::

| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| sex | O | The sex of the sampled fish specimen | **Code** from [Sex](#sex) | e.g., `F` |

| Maturity: The stage of maturity of the specimen according to standard maturity scales approved by the IOTC.

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| maturity_scale | O | The standardised system used to classify the reproductive development of fish (i.e., source) | String | e.g., `ICCAT` |
| maturity_stage | O | The reproductive stage of a fish determined through visual inspection of the gonads without the aid of a microscope | **Code** from [Maturity Stages](#maturityStages) | e.g., `DEV` | 
:::

| Sample collected: Details on the collection of samples: a) type (e.g., otoliths, spine clippings, and genetic samples), b) preservation method (e.g., alcohol, frozen, etc.), c) destination (i.e., location to be sent/stored)

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| sample_type | O | The type of sample collected by the observer | **Code** from [Sampling Type](#samplingMethodsForSamplingCollections) | e.g., `WM`|
| sample_preservation_method | O | The type of preservation method used to preserve the sample collected by the observer | **Code** from [Sample Preservation Method](#fishPreservationMethods) | e.g., `FR20` |
| sample_destination | O | Destination of the collected sample after the trip (institution or lab of analysis) | Free entry | e.g., `University of Tasmania` |
:::

| Depredation method:

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| depredation_source | O | For depredated specimens/or catch, the depredation source should be based on depredation scar characteristics. For non-depredated specimens, the value should be 'NA' (not available) | **Code** from [Depredation Sources](#depredationSources) | e.g., `BA` |
| observed_predator | O | For depredated specimens/or catch, the predator species directly observed and identified. If the predator was not observed, the value is 'UNK' (unknown). For non-depredated specimens, the value should be 'NA' (not available) | **Code** from [Predator Species](#predatorSpecies) | e.g., AG15 |
:::

# E-SET-CATCHES-SSI  {#eSetCatchSpecimensSSI}

This section of the form includes information about SSI species observed within the subset of each observed set.

| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| observed_trip_id | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |
| set_id | M | The parent set identifier | 4-digit number | e.g., `0004` |
| catch_id | M | The parent catch identifier | Alphanumeric code | e.g., `0004#1` |
| specimen_id | M | The parent specimen identifier | 4-digit code | e.g., `01` |

## Additional Catch Details on SSI

| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| condition_at_capture | M | The condition of the specimen at capture | **Code** from [Individual Conditions](#individualConditions) | e.g., `A0` |
| condition_at_release | M | The condition of the specimen at the time of release | **Code** from [Individual Conditions](#individualConditions) | e.g., `A0` |
| gear_interaction | M | The type of interaction of the specimen with the fishing gear ("UK" if unknown as not possible to collect) | **Code** from [Gear Interactions](#gearInteractions) | e.g., `EF` |
| hook_type | O | The type of hook the individual was hauled on | **Code** [Hook Types](#hookTypes) from | e.g., `C11` |

| **Bait:** The type and condition of the bait the individual was hauled on 

::: {style="margin-left:40px"}
| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| bait_condition | O | | **Code** from [Bait Conditions](#baitConditions) | e.g., `DE` |
| bait_type | O |   | **Code** from [Bait Types](#baitTypes) | e.g., `FF` | 
:::

| **Leader**
::: {style="margin-left:40px"}

| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| material | M | The leader material the SSI individual was hauled on | **Code** from [Line Material Types](#lineMaterialTypes)| e.g., `MN` |
| diameter | O | The thickness (mm) of the leader the SSI individual was hauled on | Float |  |
:::

| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| dehooker_device | O | The dehooking or line cutting device used to extract the hook | **Code** [Dehooker Types](#dehookerTypes) from | e.g., HD  |
| brought_onboard | O | Indicates whether or not the specimen was brought onboard (Yes/No/Unk) | String | e.g., `Yes` |
| handling_method | O | Detail how the specimen was brought onboard | **Code** from [Handling Methods](#handlingMethods) | e.g., `AN` |
| revival | O | Indicates whether or not the release took place with resuscitation for turtles (Yes/No/Unk) | String | e.g., `Yes`  |
| photo_id | O | The unique identifier of the photo taken of a specimen | Alphanumeric code | e.g., `Doe_Hawwa_20260302_1435_hawksbill.png` |

<!-- | **Depredation details** -->

<!--Depredation details for SSi are not included in the SC document-->

<!-- ::: {style="margin-left:40px"} -->
<!-- | Field | Requirement | Description | Format | Input value | -->
<!-- |:------- |:-----:|:------------------------|:---------:|:----------------:| -->
<!-- | depredation_source | O | The depredation source based on depredation scar characteristics for depredated specimens (NA for non-depredated specimens) | **Code** from [Depredation Sources](#depredationSources) | e.g., `BA` | -->
<!-- | observed_predator | O | The predator species directly observed and identified or unknown (UNK) when not observed (NA for non-depredated specimens) | **Code** from [Predator Species](#predatorSpecies) | e.g., `AG15` | -->
<!-- ::: -->

# E-SET-TAG-DETAILS {#eSetTagDetails}

This section of the form is for the reporting of each of the tags recovered during the observed portion of the fishing trip.

| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| observed_trip_id | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` | 
| set_id | M | The parent set identifier | 4-digit number | e.g., `0023` |
| catch_id | M | The parent catch identifier | Alphanumeric | e.g., `0023#1` |
| specimen_id | M | The parent specimen identifier | 4-digit number | e.g., `02` |

## Tag Details

| Field | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| release | O |  Indicates whether or not the individual was re-released with a tag attached (Yes/No/Unk) | String | e.g., `No` |
| recovery | O | Indicates whether or not the individual was recovered with a tag attached (Yes/No/Unk) | String  | e.g., `Yes`  |
| type | O | The type of tag used | **Code** from [Tag Types](#tagTypes) | e.g., `CP` |
| tag_id | O | The tag identifier(s). Up to two identifier may be reported on the form | Alphanumeric | e.g., `AA19051` |
| finder_name | O | The full name of the person who found the tag, recorded as first and last names | String | e.g., `Jane Doe` |
| finder_contact_details | O | The contact details (e.g., address, email, telephone) of the person who found the tag | String | e.g., `jane.doe@fishing.org | (650) 214-6369` |

# Reporting Deadlines

-   **Longline fisheries**: 30 June

# Reference Code Lists

## Entities {#entities}

-   [Permalink](https://data.iotc.org/reference/latest/domain/admin/#entities)
-   **Version**: `r version_number("ENTITIES")`
-   **Last update**: `r last_update("ENTITIES")`

```{r collapse = TRUE}
out_dt(ENTITIES, "ENTITIES")
```

## Countries {#countries}

-   [Permalink](https://data.iotc.org/reference/latest/domain/admin/#countries)
-   **Version**: `r version_number("COUNTRIES")`
-   **Last update**: `r last_update("COUNTRIES")`

```{r collapse = TRUE}
out_dt(COUNTRIES, "COUNTRIES")
```

## Data Sources {#dataSources}

-   [Permalink](https://data.iotc.org/reference/latest/domain/data/#sourcesRO)
-   **Version**: `r version_number("SOURCES")`
-   **Last update**: `r last_update("SOURCES")`

```{r collapse = TRUE, warning = FALSE, message = FALSE}
out_dt(DATA_SOURCES_RO[, -c("DATASET_CODE")], "DATA_SOURCES")
```

## Ports {#ports}

-   [Permalink](https://data.iotc.org/reference/latest/domain/admin/#Ports)
-   **Version**: `r version_number("PORTS")`
-   **Last update**: `r last_update("PORTS")`

```{r collapse = TRUE, warning = FALSE, message = FALSE}
out_dt(PORTS[, -c("POINT")], "PORTS")
```

## Reasons for Days Lost {#reasonsDaysLost}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#reasonsDaysLost)
-   **Version**: `r version_number("REASONS_DAYS_LOST")`
-   **Last update**: `r last_update("REASONS_DAYS_LOST")`

```{r collapse = TRUE}
out_dt(REASONS_DAYS_LOST, "REASONS_DAYS_LOST")
```

## Target Species {#targetSpecies}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#targetSpecies)
-   **Version**: `r version_number("TARGET_SPECIES")`
-   **Last update**: `r last_update("TARGET_SPECIES")`

```{r collapse = TRUE}
out_dt(TARGET_SPECIES, "TARGET_SPECIES")
```

## Fishing Gears {#fishingGear}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#gears)
-   **Version**: `r version_number("GEAR_TYPES")`
-   **Last update**: `r last_update("GEAR_TYPES")`

```{r collapse = TRUE}
out_dt(GEAR_TYPES, "GEAR_TYPES")
```

## Hull Material Types {#hullMaterialTypes}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#hullMaterialTypes)
-   **Version**: `r version_number("HULL_MATERIAL_TYPES")`
-   **Last update**: `r last_update("HULL_MATERIAL_TYPES")`

```{r collapse = TRUE}
out_dt(HULL_MATERIAL_TYPES, "HULL_MATERIAL_TYPES")
```

## Fish Preservation Methods {#fishPreservationMethods}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#fishPreservationMethods)
-   **Version**: `r version_number("FISH_PRESERVATION_METHODS")`
-   **Last update**: `r last_update("FISH_PRESERVATION_METHODS")`

```{r collapse = TRUE}
out_dt(FISH_PRESERVATION_METHODS, "FISH_PRESERVATION_METHODS")
```

## Vessel Size Types

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#vesselSizeTypes)
-   **Version**: `r version_number("VESSEL_SIZE_TYPES")`
-   **Last update**: `r last_update("VESSEL_SIZE_TYPES")`

```{r collapse = TRUE}
out_dt(VESSEL_SIZE_TYPES, "VESSEL_SIZE_TYPES")
```

## Fish Storage Types {#fishStorageTypes}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#fishStorageTypes)
-   **Version**: `r version_number("FISH_STORAGE_TYPES")`
-   **Last update**: `r last_update("FISH_STORAGE_TYPES")`

```{r collapse = TRUE}
out_dt(FISH_STORAGE_TYPES, "FISH_STORAGE_TYPES")
```

## Waste Categories {#wasteCategories}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#wasteCategories)
-   **Version**: `r version_number("WASTE_CATEGORIES")`
-   **Last update**: `r last_update("WASTE_CATEGORIES")`

```{r collapse = TRUE}
out_dt(WASTE_CATEGORIES, "WASTE_CATEGORIES")
```

## Storage / Disposal Methods {#storageDisposalMethods}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#wasteDisposalMethods)
-   **Version**: `r version_number("WASTE_DISPOSAL_METHODS")`
-   **Last update**: `r last_update("WASTE_DISPOSAL_METHODS")`

```{r collapse = TRUE}
out_dt(WASTE_DISPOSAL_METHODS, "WASTE_DISPOSAL_METHODS")
```

## Line Material Types {#lineMaterialTypes}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#lineMaterialTypes)
-   **Version**: `r version_number("LINE_MATERIAL_TYPES")`
-   **Last update**: `r last_update("LINE_MATERIAL_TYPES")`

```{r collapse = TRUE}
out_dt(LINE_MATERIAL_TYPES, "LINE_MATERIAL_TYPES")
```

## Branchline Storages {#branchlineStorages}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#branchlineStorages)
-   **Version**: `r version_number("BRANCHLINE_STORAGES")`
-   **Last update**: `r last_update("BRANCHLINE_STORAGES")`

```{r collapse = TRUE}
out_dt(BRANCHLINE_STORAGES, "BRANCHLINE_STORAGES")
```

## Streamer Types {#streamerTypes}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#streamerTypes)
-   **Version**: `r version_number("STREAMER_TYPES")`
-   **Last update**: `r last_update("STREAMER_TYPES")`

```{r collapse = TRUE}
out_dt(STREAMER_TYPES, "STREAMER_TYPES")
```

## Mitigation Devices {#mitigationDevices}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#mitigationDevices)
-   **Version**: `r version_number("MITIGATION_DEVICES")`
-   **Last update**: `r last_update("MITIGATION_DEVICES")`

```{r collapse = TRUE}
out_dt(MITIGATION_DEVICES, "MITIGATION_DEVICES")
```

## Light Types {#lightTypes}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#lightTypes)
-   **Version**: `r version_number("LIGHT_TYPES")`
-   **Last update**: `r last_update("LIGHT_TYPES")`

```{r collapse = TRUE}
out_dt(LIGHT_TYPES, "LIGHT_TYPES")
```

## Light Colours {#lightColours}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#lightColours)
-   **Version**: `r version_number("LIGHT_COLOURS")`
-   **Last update**: `r last_update("LIGHT_COLOURS")`

```{r collapse = TRUE}
out_dt(LIGHT_COLOURS, "LIGHT_COLOURS")
```

## Hook Types {#hookTypes}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#hookTypes)
-   **Version**: `r version_number("HOOK_TYPES")`
-   **Last update**: `r last_update("HOOK_TYPES")`

```{r collapse = TRUE}
out_dt(HOOK_TYPES, "HOOK_TYPES")
```

## Bait Conditions {#baitConditions}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#baitConditions)
-   **Version**: `r version_number("BAIT_CONDITIONS")`
-   **Last update**: `r last_update("BAIT_CONDITIONS")`

```{r collapse = TRUE}
out_dt(BAIT_CONDITIONS, "BAIT_CONDITIONS")
```

## Bait Species {#baitSpecies}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#baits)
-   **Version**: `r version_number("SPECIES_BAITS")`
-   **Last update**: `r last_update("SPECIES_BAITS")`

```{r collapse = TRUE}
out_dt(SPECIES_BAITS, "SPECIES_BAITS")
```

## Offal Management Types {#offalManagementTypes}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#offalManagementTypes)
-   **Version**: `r version_number("OFFAL_MANAGEMENT_TYPES")`
-   **Last update**: `r last_update("OFFAL_MANAGEMENT_TYPES")`

```{r collapse = TRUE}
out_dt(OFFAL_MANAGEMENT_TYPES, "OFFAL_MANAGEMENT_TYPES")
```

## Vessel Sections {#vesselSections}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#vesselSections)
-   **Version**: `r version_number("VESSEL_SECTIONS")`
-   **Last update**: `r last_update("VESSEL_SECTIONS")`

```{r collapse = TRUE}
out_dt(VESSEL_SECTIONS, "VESSEL_SECTIONS")
```

## Sampling protocols {#samplingProtocols}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#samplingProtocols)
-   **Version**: `r version_number("SAMPLING_PROTOCOLS")`
-   **Last update**: `r last_update("SAMPLING_PROTOCOLS")`

```{r collapse = TRUE}
out_dt(SAMPLING_PROTOCOLS, "SAMPLING_PROTOCOLS")
```

## All Species {#allSpecies}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#allSpecies)
-   **Version**: `r version_number("SPECIES")`
-   **Last update**: `r last_update("SPECIES")`

```{r collapse = TRUE}
out_dt(SPECIES, "SPECIES")
```

## Types of Fate {#fateType}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#typesOfFate)
-   **Version**: `r version_number("TYPES_OF_FATE")`
-   **Last update**: `r last_update("TYPES_OF_FATE")`

```{r collapse = TRUE}
out_dt(TYPES_OF_FATE, "TYPES_OF_FATE")
```

## Fates {#fates}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#fates)
-   **Version**: `r version_number("FATES")`
-   **Last update**: `r last_update("FATES")`

```{r collapse = TRUE}
out_dt(FATES, "FATES")
```

## Sampling Method for Catch Estimation {#samplingMethodsCatchEstimation}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#samplingMethodsForCatchEstimation)
-   **Version**: `r version_number("SAMPLING_METHODS_FOR_CATCH_ESTIMATION")`
-   **Last update**: `r last_update("SAMPLING_METHODS_FOR_CATCH_ESTIMATION")`

```{r collapse = TRUE}
out_dt(SAMPLING_METHODS_FOR_CATCH_ESTIMATION, "SAMPLING_METHODS_FOR_CATCH_ESTIMATION")
```

## Maturity Stages {#maturityStages}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#Maturity_Stages)
-   **Version**: `r version_number("MATURITY_STAGES")`
-   **Last update**: `r last_update("MATURITY_STAGES")`

```{r collapse = TRUE}
out_dt(MATURITY_STAGES, "MATURITY_STAGES")
```

## Fish Processing Types {#fishProcessingTypes}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#fishProcessingTypes)
-   **Version**: `r version_number("FISH_PROCESSING_TYPES")`
-   **Last update**: `r last_update("FISH_PROCESSING_TYPES")`

```{r collapse = TRUE}
out_dt(FISH_PROCESSING_TYPES, "FISH_PROCESSING_TYPES")
```

<!-- ## Total Catch Estimation {#totalCatchEstimation} -->

<!-- -   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#samplingMethodsForCatchEstimation) -->
<!-- -   **Version**: `r version_number("SAMPLING_METHODS_FOR_CATCH_ESTIMATION")` -->
<!-- -   **Last update**: `r last_update("SAMPLING_METHODS_FOR_CATCH_ESTIMATION")` -->

<!-- ```{r collapse = TRUE} -->
<!-- out_dt(SAMPLING_METHODS_FOR_CATCH_ESTIMATION, "SAMPLING_METHODS_FOR_CATCH_ESTIMATION") -->
<!-- ``` -->

## Sampling Period {#samplingPeriod}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#samplingPeriods)
-   **Version**: `r version_number("SAMPLING_PERIODS")`
-   **Last update**: `r last_update("SAMPLING_PERIODS")`

```{r collapse = TRUE}
out_dt(SAMPLING_PERIODS, "SAMPLING_PERIODS")
```

## Biological Sampling Method {#biologicalSamplingMethod}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#samplingMethodsForSamplingCollection)
-   **Version**: `r version_number("SAMPLING_METHODS_FOR_SAMPLING_COLLECTIONS")`
-   **Last update**: `r last_update("SAMPLING_METHODS_FOR_SAMPLING_COLLECTIONS")`

```{r collapse = TRUE}
out_dt(SAMPLING_METHODS_FOR_SAMPLING_COLLECTIONS, "SAMPLING_METHODS_FOR_SAMPLING_COLLECTIONS")
```

## Length Measurements {#lengthMeasurements}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#lengthMeasurements)
-   **Version**: `r version_number("MEASUREMENTS")`
-   **Last update**: `r last_update("MEASUREMENTS")`

```{r collapse = TRUE}
out_dt(LENGTH_MEASUREMENTS, "LENGTH_MEASUREMENTS")
```

## Length Measurement Tools {#lengthMeasurementTools}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#lengthMeasurementTools)
-   **Version**: `r version_number("MEASUREMENT_TOOLS")`
-   **Last update**: `r last_update("MEASUREMENTS_TOOLS")`

```{r collapse = TRUE}
out_dt(LENGTH_MEASUREMENT_TOOLS, "MEASUREMENT_TOOLS")
```

## Weight Measurements {#weightMeasurememts}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#weightMeasurements)
-   **Version**: `r version_number("WEIGHT_MEASUREMENTS")`
-   **Last update**: `r last_update("WEIGHT_MEASUREMENTS")`

```{r collapse = TRUE}
out_dt(WEIGHT_MEASUREMENTS, "WEIGHT_MEASUREMENTS")
```

## Weight Measurement Tools {#weightMeasurementTools}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#weightMeasurementTools)
-   **Version**: `r version_number("WEIGHT_MEASUREMENT_TOOLS")`
-   **Last update**: `r last_update("WEIGHT_MEASUREMENT_TOOLS")`

```{r collapse = TRUE}
out_dt(WEIGHT_MEASUREMENT_TOOLS, "WEIGHT_MEASUREMENT_TOOLS")
```

## Sex {#sex}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#sex)
-   **Version**: `r version_number("SEX")`
-   **Last update**: `r last_update("SEX")`

```{r collapse = TRUE}
out_dt(SEX, "SEX")
```

## Maturity Stages {#maturityStages}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#Maturity_Stages)
-   **Version**: `r version_number("MATURIY_STAGES")`
-   **Last update**: `r last_update("MATURITY_STAGES")`

```{r collapse = TRUE}
out_dt(MATURITY_STAGES, "MATURITY_STAGES")
```

## Sampling Type {#samplingMethodsForSamplingCollections}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#samplingMethodsForSamplingCollection)
-   **Version**: `r version_number("SAMPLING_METHODS_FOR_SAMPLING_COLLECTIONS")`
-   **Last update**: `r last_update("SAMPLING_METHODS_FOR_SAMPLING_COLLECTIONS")`

```{r collapse = TRUE}
out_dt(SAMPLING_METHODS_FOR_SAMPLING_COLLECTIONS, "SAMPLING_METHODS_FOR_SAMPLING_COLLECTIONS")
```

## Sample Preservation Methods {#fishPreservationMethods}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#fishStorageTypes)
-   **Version**: `r version_number("FISH_PRESERVATION_METHODS")`
-   **Last update**: `r last_update("FISH_PRESERVATION_METHODS")`

```{r collapse = TRUE}
out_dt(FISH_PRESERVATION_METHODS, "FISH_PRESERVATION_METHODS")
```

## Depredation Sources {#depredationSources}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#depredationSources)
-   **Version**: `r version_number("DEPREDATION_SOURCES")`
-   **Last update**: `r last_update("DEPREDATION_SOURCES")`

```{r collapse = TRUE}
out_dt(DEPREDATION_SOURCES, "DEPREDATION_SOURCES")
```

## Predator Species {#predatorSpecies}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#predators)
-   **Version**: `r version_number("SPECIES_PREDATORS")`
-   **Last update**: `r last_update("SPECIES_PREDATORS")`

```{r collapse = TRUE}
out_dt(SPECIES_PREDATORS, "SPECIES_PREDATORS")
```

## Individual Conditions {#individualConditions}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#individualConditions)
-   **Version**: `r version_number("INDIVIDUAL_CONDITIONS")`
-   **Last update**: `r last_update("INDIVIDUAL_CONDITIONS")`

```{r collapse = TRUE}
out_dt(INDIVIDUAL_CONDITIONS, "INDIVIDUAL_CONDITIONS")
```

## Gear Interactions {#gearInteractions}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#gearInteractions)
-   **Version**: `r version_number("GEAR_INTERACTIONS")`
-   **Last update**: `r last_update("GEAR_INTERACTIONS")`

```{r collapse = TRUE}
out_dt(GEAR_INTERACTIONS, "GEAR_INTERACTIONS")
```

## Hook Types {#hookTypes}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#hookTypes)
-   **Version**: `r version_number("HOOK_TYPES")`
-   **Last update**: `r last_update("HOOK_TYPES")`

```{r collapse = TRUE}
out_dt(HOOK_TYPES, "HOOK_TYPES")
```

## Bait Conditions {#baitConditions}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#baitConditions)
-   **Version**: `r version_number("BAIT_CONDITIONS")`
-   **Last update**: `r last_update("BAIT_CONDITIONS")`

```{r collapse = TRUE}
out_dt(BAIT_CONDITIONS, "BAIT_CONDITIONS")
```

## Dehooker Types {#dehookerTypes}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#dehookerTypes)
-   **Version**: `r version_number("DEHOOKER_TYPES")`
-   **Last update**: `r last_update("DEHOOKER_TYPES")`

```{r collapse = TRUE}
out_dt(DEHOOKER_TYPES, "DEHOOKER_TYPES")
```

## Handling Methods {#handlingMethods}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#handlingMethods)
-   **Version**: `r version_number("HANDLING_METHODS")`
-   **Last update**: `r last_update("HANDLING_METHODS")`

```{r collapse = TRUE}
out_dt(HANDLING_METHODS, "HANDLING_METHODS")
```

## Tag Types {#tagTypes}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#tagTypes)
-   **Version**: `r version_number("TAG_TYPES")`
-   **Last update**: `r last_update("TAG_TYPES")`

```{r collapse = TRUE}
out_dt(TAG_TYPES, "TAG_TYPES")
```
