---
title: "IOTC ROS Data Reporting: Form ROS-LL"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  word_document2:
    reference_docx: "../../templates/doc_template.docx"
    number_sections: FALSE
    reference_num: TRUE
    fig_caption: TRUE

  html_document2:
    css: "../../templates/html_template.css"
    includes: 
      in_header: "../../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---

# Description

This form provides for the reporting of operational and catch data from longline fisheries under the IOTC Regional Observer Scheme (ROS). The form is designed to capture verified information on fishing activity, catch composition, and bycatch associated with longline operations, including IOTC species, and other bycatch species. The reporting format follows the standards adopted by the IOTC Scientific Committee and includes multiple hierarchical data levels, ranging from trip and set information to species-specific catch and bycatch records. Data collected through this form contribute to scientific assessments of tuna and tuna-like species and support monitoring of the impact of longline fisheries on associated and dependent species. CPCs are required to complete the form for longline operations covered by the ROS, ensuring consistency, transparency, and quality of the data collected by scientific observers at sea or reviewing data collected with Electronic Monitoring Systems.

Click [here](./Form-ROS-LL.xlsx) to download a blank version of Form ROS-LL, or [return](../index.html) to the list of all IOTC data reporting forms.

# Data Content

Vessel and trip identifiers; effort and gear characteristics (hooks, soak time, set position); operational details of each set; catch and bycatch by species in number and weight; fate of catch (retained/discarded); interactions with sharks, seabirds, turtles, and other species; mitigation measures used; size measurements of catch as well as some biological samples.

# Reporting Metadata

## Submission Information

<!-- Focal point (full name, email, finalisation date, and submission date) and organisation information (name, email). -->

## General Information

| Element | Requirement | Description | Format | Input value |
|:--------- |:----:|:-------------------------|:-------:|:---------:|
| Reporting year | M | Gregorian calendar year of the fishing activities reported through the dataset | 4-digit integer | e.g., `1996` |
| Reporting entity | M | Three-letter (alpha-3) code of the entity reporting the dataset to the IOTC Secretariat | **Code** from [Entities](#entities) | e.g., `ABW` |
| Flag / Chartering state | M | The country registration of the fishing vessels or chartering flag in case of chartering agreement | **Code** from [Countries](#countries) | e.g., `FRA` |
| Data source | M | The source of data provided: 'OAS' for data collected by Observers at sea and 'EMS' for data derived from Electronic Monitoring Systems | String | e.g., `OAS` |

<!-- Code list of data sources to define: OAS/EMS -->

# O-INFO | Observer and Observed Trip Information

| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| observed_trip_id | M | Unique identifier of the fishing trip defined as the concatenation of (i) the observation or trip start date (YYYY-MM-DD), (ii) the IOTC observer identifier, (iii) the IOTC vessel identifier as per Record of Authorised Vessels ([RAV](https://rav.iotc.org/)) and the vessel [gear group](https://data.iotc.org/reference/latest/domain/fisheries/#gearGroups) code as per IOTC classification | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |

## Observer Identification

| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| observer_iotc_id | M | The unique registration identifier assigned to each observer by the IOTC Secretariat | Alphanumeric | e.g., `IOTC_0976` |
| observer_full_name | M | The full name of the scientific observer who collected the data onboard the fishing vessel, or of the Electronic Monitoring reviewer, recorded as first and last names | String | e.g., `John Doe` |

## Observer Trip Details

| **Embarkation:** The starting port. If the first observation is available after the departure form the port while the vessel is within port limits, this is still recorded as the observation starting port. If the observation starts at sea outside port limits (onboard observer boarding the vessel via a vessel transfer or EM records not available at the trip starting date due to a recording failure), record "at sea".

::: {style="margin-left:40px"}
| **In port**
:::

::: {style="margin-left:80px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| country | O | The country or EEZ of the observation starting location | **Code** from [Countries](#countries) | e.g.,`FRA` |
| port | O | The port of the observation starting location | **Code** from [Ports](#ports) | e.g., `REUREU` |
:::

::: {style="margin-left:40px"}
| **At sea**
:::

::: {style="margin-left:80px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| latitude  | O | The latitude of the observation starting location | Decimal degrees (two decimal places) | e.g., `-20.88` |
| longitude | O | The longitude of the observation starting location | Decimal degrees (two decimal places) | e.g., `55.53` |
:::

::: {style="margin-left:40px"}
||||||
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| date_time_UTC | O | The date and time of the start of observations | YYYY-MM-DD hh:mm | e.g., `2025-09-15 12:00` |
:::


| **Disembarkation:** The ending port. If the last observation is available after a port launch while the vessel is within port limits, this is still recorded as the observation ending port. If the observation ends at sea outside port limits (onboard observer disembarking the vessel via a vessel transfer or EM records not available at the end of observations due to a recording failure) , record "at sea"
| 

::: {style="margin-left:40px"}
| **In port**
:::

::: {style="margin-left:80px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| country | O | The country or EEZ of the observation ending location | **Code** from [Countries](#countries) | e.g.,`FRA` |
| port | O | The port of the observation ending location | **Code** from [Ports](#ports) | e.g., `REUREU` |
:::

::: {style="margin-left:40px"}
| **At sea**
:::

::: {style="margin-left:80px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| latitude | O | The latitude of the observation ending location | Decimal degrees (two decimal places) | e.g., `-20.88` |
| longitude | O | The longitude of the observation ending location | Decimal degrees (two decimal places) | e.g., `55.53` |
:::

::: {style="margin-left:40px"}
|  |  |  |  |  |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| date_time_UTC | O | The date and time of the end of observations | YYYY-MM-DD hh:mm | e.g., `2025-09-15 12:00` |
:::

## Observed Trip Summary

| **Number of fishing sets:** The total number of longline sets deployed by the vessel or observed by the scientific observer during a single fishing trip. Each set corresponds to one complete deployment of the longline gear.

::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| conducted | M | The total number of fishing sets conducted by the vessel from the observation starting date to the observation ending date, regardless their catch and data collection activities | Integer | **EXAMPLE TO ADD**  |
| observed | M | The total number of fishing sets/events monitored by the observer. In the case of Electronic Monitoring, only processed events to be included | Integer | **EXAMPLE TO ADD** |
:::

| **Number of days:** The total number of hours or calendar days the vessel is on a fishing trip. This can be further categorised by type of activity (e.g., searching, transiting, actively fishing, or present in fishing areas).

::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| searching | O | The number of hours/days searching during the observation period | Integer | **EXAMPLE TO ADD** |
| actively fishing | O | The number of active fishing hours/days during the observation period | Integer | **EXAMPLE TO ADD** |
| in_fishing_area | O | The number of hours/days in the fishing area during the observation period | Integer | **EXAMPLE TO ADD** |
| transiting | O | The number of hours/days transiting during the observation period | Integer | **EXAMPLE TO ADD** |
| lost | O | The number of hours/days lost during the observation period | Integer | **EXAMPLE TO ADD** |
:::

| **Reasons for lost days:**  Record the reason(s) a vessel was unable to fish: (i) adverse weather conditions, (ii) mechanical breakdown or inoperative gear or (iii) unforeseen events (specify).

<!-- iI removed HOURS from the definitions -->

| **Reasons for lost days:** Record the reason(s) a vessel was unable to fish: (i) adverse weather conditions, (ii) mechanical breakdown or inoperative gear or (iii) unforeseen events (specify).

::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| reason | O | The main reasons for days at sea lost to fishing activity | **Code** from [Reasons for Days Lost](#reasonsDaysLost) | e.g., `AW` |
:::

# (V-INFO) Vessel \> General Information

| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| observed_trip_id | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |

## Vessel Information

| **Identification:** Unique identifiers and key details of the vessel to uniquely identify the vessel in fisheries and observer records.

::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| name | M | The vessel full name as recorded on vessel official documentation or record the vessel full name as imprinted on the vessel itself or Electronic Monitoring records | String | e.g., `HAWWA` |
| flag_or_chartering_state | M | The country code of registration or chartering | **Code** from [Countries](#countries) | e.g., `OMN` |
| iotc_number | M | The unique identification number assigned to the vessel by the IOTC when it is included in the Record of Authorised Vessels | Alphanumeric | e.g., `IOTC003810` |
| imo_number | O | The unique vessel identification number assigned by the International Maritime Organization | Seven-digit number | e.g., `9359698` |
| ircs | O | The unique alphanumeric code (International Radio Call Sign; IRCS) assigned to the vessel for radio communications, as recorded in official registration documents radio call sign (when available) | Alphanumeric | e.g., `A4DP6` |
:::

| **Registration:** Official vessel registration details to uniquely identify the vessel within the national or regional registry.

::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| country | O | The vessel's country of registry | **Code** from [Countries](#countries) | e.g., `FRA` |
| port | O | The vessel's port of registry (also called home port) shown on its registration documents and lettered on the stern of the ship's hull | **Code** from [Ports](#ports) | e.g., `REUREU` |
| registration_number | O | The number issued by country in which the vessel is registered, shown on its registration documents and written on the hull of the vessel | Alphanumeric or numeric entry according to CPC standards | e.g., `CBG303` |
:::

| Element | Requirement | Description | Format | Input value |
<!-- Change Reg number to registration number? -->

| Field | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| licensed_target_species | O | The licensed target species as specified in vessel licences or permit conditions | **Code** from [Target Species](#targetSpecies) | e.g., `AL` |
| Main Fishing Gear | M | The vessel main fishing gear | **Code** from [Fishing Gear](#fishingGear) | e.g., `DL` |

| **Vessel Personnel:** Details of the individuals working onboard during the fishing trip as well as the total number of crew members onboard.

::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| fishing_master_name | M | The full name of the fishing master recorded as first and last names | String | e.g., `John Doe` |
| fishing_master_nationality | M | The nationality of the fishing master | **Code** from [Countries](#countries) | e.g., `FRA` |
| skipper_captain_name | M | Name of the skipper or captain recorded as first and last names| String | e.g., `John Doe` |
| skipper_captain_nationality | M | Nationality of the skipper or captain | **Code** from [Countries](#countries) | e.g., `FRA` |
| crew_number | O | The number of crew onboard the vessel | Integer | e.g., `26` |
:::

# (V-TRIP) Vessel \> Trip details

| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| observed_trip_id | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |  

## Trip Details

| **Vessel departure:** The name and/or geographical coordinates of the port from where the vessel sailed – also include the country. If the vessel started a new trip at sea following transshipment record 'at-sea’ plus the geographical coordinates corresponding to the location the trip started

::: {style="margin-left:40px"}
| **In port**
:::

::: {style="margin-left:80px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| country | O | The country or EEZ of the observation starting location | **Code** from [Countries](#countries) | e.g., `FRA` |
| port | O | The port of the observation starting location | **Code** from [Ports](#ports) | e.g., `REUREU` |
| latitude | O | The latitude of the observation starting location | Decimal degrees (two decimal places) | e.g., `-20.88` |
| longitude | O | The longitude of the observation starting location | Decimal degrees (two decimal places) | e.g., `55.53` |
:::

::: {style="margin-left:40px"}
|               |     |     |                  |                       |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| date_time_utc |  O  | The date and time (in Coordinated Universal Time, UTC) corresponding to the start of the observation period at the reported location | YYYY-MM-DD hh:mm | e.g., `2025-09-15 12:00` |
:::

::: {style="margin-left:40px"}
| **At sea**
:::

::: {style="margin-left:80px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| country | O | The country or EEZ of the observation starting location | **Code** from [Countries](#countries) | e.g., `FRA` |
| latitude | O | The latitude of the observation starting location | Decimal degrees (two decimal places) | e.g., `-20.88` |
| longitude | O | The longitude of the observation starting location | Decimal degrees (two decimal places) | e.g., `55.53` |
:::

::: {style="margin-left:40px"}
|  |  |  |  |  |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| date_time_UTC | O | The date and time the vessel departed from port or from a transshipment location | YYYY-MM-DD hh:mm | e.g., `2025-09-15 12:00` |
:::

| **Vessel return:** The name and/or geographical coordinates of the port where the vessel returned – also include the country. If the vessel arrived at a transshipment location record 'at-sea' plus the geographical coordinates corresponding to the location the transshipment started. If the observer disembarked before the vessel returned then record expected port of return as provided by the vessel

::: {style="margin-left:40px"}
| **In port**
:::

::: {style="margin-left:80px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| country | O | The country or EEZ of the observation ending location | **Code** from [Countries](#countries) | e.g., `FRA` |
| port | O | The port of the observation ending location | **Code** from [Ports](#ports) | e.g., `REUREU` |
| latitude | O | The latitude of the observation ending location | Decimal degrees (two decimal places) | e.g., `-20.88` |
| longitude | O | The longitude of the observation ending location | Decimal degrees (two decimal places) | e.g., `55.53` |
:::

::: {style="margin-left:40px"}
|               |     |     |                  |                        |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| date_time_UTC |  O  | The date and time (in Coordinated Universal Time, UTC) corresponding to the end of the observation period at the reported location | YYYY-MM-DD hh:mm | e.g., `2025-09-15 12:00` |
:::

::: {style="margin-left:40px"}
| **At sea**
:::

::: {style="margin-left:80px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| country | O | The country or EEZ of the observation ending location | **Code** from [Countries](#countries) | e.g., `FRA` |
| latitude | O | The latitude of the observation ending location | Decimal degrees (two decimal places) | e.g., `-20.88` |
| longitude | O | The longitude of the observation ending location | Decimal degrees (two decimal places) | e.g., `55.53` |
:::

::: {style="margin-left:40px"}
|  |  |  |  |  |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| date_time_utc | O | The date and time the fishing vessel finishes its fishing campaign, i.e., returns to port or to a transshipment location for unloading. If is the expected date and time of arrival (ETA) if the observer disembarks before the vessel returns | YYYY-MM-DD hh:mm | e.g., `2025-09-15 12:00` |
:::

# (V-ATTRIBUTES) Vessel \> Vessel Attributes

| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| observed_trip_id | M | The parent observed trip identifier | Alphanumeric | `2024-01-23/IOTCFRA001/IOTC012345/LL` |

## Vessel Attributes

| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| Tonnage | O | The vessel gross tonnage (no unit) as specified in vessel registration documents | Float | e.g., `2319` |
| Length | O | The vessel overall length (m) as specified in vessel registration documents | Floats | e.g., `84.1` |
| Hull material code | O | The vessel hull material | **Code** from [Hull Material Types](#hullMaterialTypes) | e.g., `AL` |
| gross_tonnage | O | Gross tonnage (GT), a dimensionless measure of vessel's internal volume from registration documents | Integer | e.g., `2319` |
| LOA_m | O | The vessel overall length (m) as specified in vessel registration documents | Floats | e.g., `84.1` |
| Hull material | O | The primary material used in the construction of the vessel's hull | **Code** from [Hull Material Types](#hullMaterialTypes) | e.g., `AL` |

| **Main engines:** The make (brand) and power of the two main engines.

::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| make | O | The manufacturer or brand name of the vessel's engine, as specified in the official vessel registration or engine documentation | String | e.g., `MAN Energy Solutions`  |
| power_value | O | The rated power output of the vessel's main engine as specified in the official vessel registration or engine documentation | Integer | e.g., `5000` |
| power_unit | O | Rated output of the vessel's main engine, as specified in official registration or engine documentation in kilowatts (kW), horsepower (hp), or break horsepower (hp) | String | e.g., `kW` |

<!-- I think we should remove BHP from the possibilities following Res. [19/04](https://www.iotc.org/cmm/resolution-1904-concerning-iotc-record-vessels-authorised-operate-iotc-area-competence) -->
:::

||||||
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| fish_storage_capacity_m3 | O | The vessel total maximum capacity (cubic metres; m^3^) to store catches | Float | e.g., `1100` |
<!-- | fish_storage_capacity_unit | O | The standard measurement units for fish storage capacity | **Code** from [Vessel Size Types](#vesselSizeTypes) | e.g., `CC` | -->
| Make | O | **DESCRIPTION TO ADD** | String | e.g., `MAN Energy Solutions`  |
| Power value | O | **DESCRIPTION TO ADD** | Float | e.g., `5000` |
| Power unit | O | **DESCRIPTION TO ADD** | Power units: kilowatts (kW), horsepower (hp), or break horsepower (hp) | e.g., `kW` |
:::


|  |  |  |  |  |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| Fish storage capacity | O | The vessel total maximum capacity to store catches | Float | e.g., `1100` |

| **Fish preservation methods:** The fish preservation methods used by the vessel to preserve the catch, e.g., iced, frozen in brine, deep-frozen
::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| preservation_method_1 | O |  | **Code** from [Fish Preservation Methods](#fishPreservationMethods) | e.g., `BR` |
| preservation_method_2 | O |  | **Code** from [Fish Preservation Methods](#fishPreservationMethods) | e.g., `BR` |
| preservation_method_3 | O |  | **Code** from [Fish Preservation Methods](#fishPreservationMethods) | e.g., `BR` |
| preservation_method_4 | O |  | **Code** from [Fish Preservation Methods](#fishPreservationMethods) | e.g., `BR` |
::: 
| **Fish storage types:** The type of structure(s) present on-board used by the vessel to store the catch
::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| storage_type_1 | O |  |  **Code** from [Fish Storage Types](#fishStorageTypes) | e.g., `BF` |
| storage_type_2 | O |  |  **Code** from [Fish Storage Types](#fishStorageTypes) | e.g., `BF` |
| storage_type_3 | O |  |  **Code** from [Fish Storage Types](#fishStorageTypes) | e.g., `BF` |

| **Autonomy range:** Vessel autonomy, expressed by the time (days) a vessel can spend at sea without refuelling. If this information is not available then record vessel range expressed in cruising distance (nm). If a figure for the range cannot be obtained, the observer should calculate vessel range as follows: Vessel range (nm)\> = \<Vessel average cruising distance per metric tonne (nm/t)\> : \<Tonnage of fuel carried (t)\> Note: specify units (days or nautical miles)"
:::

| **Autonomy range:** Vessel autonomy, expressed by the time (days) a vessel can spend at sea without refuelling. If this information is not available then record vessel range expressed in cruising distance (nm). If a figure for the range cannot be obtained, the observer should calculate vessel range as follows: Vessel range (nm)\> = \<Vessel average cruising distance per metric tonne (nm/t)\> : \<Tonnage of fuel carried (t)\> Note: specify units (days or nautical miles)

<!-- Fish storage capacity unit TO ADD IN REPORTING FORMS -->

::: {style="margin-left:40px"}
| Element | Requirement | Description |      Format       | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| autonomy_range_value | O | The vessel's operational endurance, expressed either as the maximum number of days it can remain at sea without resupply, or as the maximum distance it can cover (in nautical miles, nm) | Float | e.g., `30` |
| autonomy_range_unit  | O | The unit used to describe the value of autonomy range | days or nm | e.g., `days` |
:::

<!-- "Days/NM" renamed to Autonomy range unit: To be populated to the reporting forms -->

## Vessel Electronics

| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| GNSS | O | Indicates whether or not one or more Global Navigation Satellite System systems (GNSS) such as the US Global Positioning System (GPS) were present on the vessel (Yes/No/Unk) | String | e.g., `Yes` |
| VMS | O | Indicates whether or not one or more Vessel Monitoring Systems (VMS) were present on the vessel (Yes/No/Unk)  | String | e.g., `Yes` |
| AIS | O | Indicates whether or not one or more Automatic Identification Systems (AIS) were present on the vessel (Yes/No/Unk) | String | e.g., `Yes` |
| Radars | O | Indicates whether or not one or more radars were present on the vessel (Yes/No/Unk) | String | e.g., `Yes`  |
| Track plotter | O | Indicates whether or not one or more track plotters were present on the vessel (Yes/No/Unk) | String | e.g., `Yes` |
| Depth sounder | O | Indicates whether or not one or more depth sounders were present on the vessel (Yes/No/Unk)| String | e.g., `Yes` |
| Sonar | O | Indicates whether one or more sonars were present on the vessel (Yes/No/Unk) | String | e.g., `Yes` |
| Doppler current meter | O | Indicates whether one or more doppler current meters were present on the vessel | String | e.g., `Yes` |
| XBT | O | Indicates whether or not one or more expendable bathythermographs (XBT) were present on the vessel | String | e.g., `Yes` |
| VHF radios | O | Indicates whether or not one or more VHF radios weere present on the vessel | String | e.g., `Yes` |
| HF radios | O | Indicates whether one or more HF radios were present or not on the vessel | String | e.g., `Yes` |
| Satellite comms | O | Indicate whether or not one or more satellite communication systems were present on the vessel | String | e.g., `Yes` |
| FIS | O | Indicates whether or not one or more Fisheries Information Services were present on the vessel | String | e.g., `Yes` |

## Waste Management Detail
::: {style="margin-left:40px"}
| Waste Management Detail 1
:::
::: {style="margin-left:80px"}
| Element | Requirement | Description | Format | Input value |
|:-----------------|:------------:|:------------------------|:------------:|:------------:|
| Category | O | The category of the waste produced by the vessel |**Code** from [Waste Categories](#wasteCategories) | e.g., `CP` |
| Storage/disposal method | O |	The method used to dispose of the waste | **Code** from [Storage/Disposal Methods](#storageDisposalMethods)| e.g., `AS` |
:::
::: {style="margin-left:40px"}
| Waste Management Detail 2
:::
::: {style="margin-left:80px"}
| Element | Requirement | Description | Format | Input value |
|:-----------------|:------------:|:------------------------|:------------:|:------------:|
| Category  | O  |	The category of the waste produced by the vessel | **Code** from [Waste Categories](#wasteCategories) | e.g., `CP` |
| Storage/disposal method | O |	The method used to dispose of the waste | **Code** from [Storage/Disposal Methods](#storageDisposalMethods)| e.g., `AS` |
:::
::: {style="margin-left:40px"}
| Waste Management Detail 3
:::
::: {style="margin-left:80px"}
| Element | Requirement | Description | Format | Input value |
|:-----------------|:------------:|:------------------------|:------------:|:------------:|
| Category | O |	The category of the waste produced by the vessel | **Code** from [Waste Categories](#wasteCategories) | e.g., `CP` |
| Storage/disposal method | O |	The method used to dispose of the waste | **Code** from [Storage/Disposal Methods](#storageDisposalMethods)| e.g., `AS` |
:::
::: {style="margin-left:40px"}
| Waste Management Detail 4
:::
::: {style="margin-left:80px"}
| Element | Requirement | Description | Format | Input value |
|:-----------------|:------------:|:------------------------|:------------:|:------------:|
| category   |O  |	The category of the waste produced by the vessel  |**Code** from [Waste Categories](#wasteCategories) | e.g., `CP` |
| storage_disposal_method | O |	The method used to dispose of the waste | **Code** from [Storage/Disposal Methods](#storageDisposalMethods)| e.g., `AS` |
:::

# (G-GENERAL) Longline General Gear Specifications

| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| observed_trip_id | M | The parent observed trip identifier | Alphanumeric | `2024-01-23/IOTCFRA001/IOTC012345/LL` |

## Special Equipment or Machinery

| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| line setter/line shooter | M | Indicates whether of not the vessel is equipped with this technology (Yes/No/Unk) | String | e.g., `Yes` |
| Line hauler | M | Indicates whether or not the vessel is equipped with this technology (Yes/No/Unk) | String | e.g., `Yes` |
| Bait casting machine | M | Indicates whether or not the vessel is equipped with this technology (Yes/No/Unk) | String |  e.g., `Yes` |

# (G-CONFIG-BRANCHLINES) Longline General Gear Specifications > Branchline Configurations

| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| Observed trip ID | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |

## Branchline Configurations

| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| Configuration identifier | O | The unique number for a specific branchline specification as detailed based on the fields below | Integer | **EXAMPLE TO ADD** |
| Section identifier | O | **DESCRIPTION TO ADD**  | Integer | **EXAMPLE TO ADD** |
| Material type | O | The branchline material for each of the four sections where section 1 is that closest to the mainline and section 4 is the leader; note that wire trace may be sheathed by a plastic or nylon coating | **Code** from [Line Material Types](#lineMaterialTypes) | e.g., `NL` |
| Length | O | The value of the length (m) of the branchline for each of the four sections where section 1 is that closest to the mainline and section 4 is the leader | Float | **EXAMPLE TO ADD** |
| Diameter | O | The value of the diameter (cm) of the branchline for each of the four sections where section 1 is that closest to the mainline and section 4 is the leader | Float | **EXAMPLE TO ADD** |

<!-- CHANGE "CONFIGURATION NUMBER AND SECTION NUMBER TO CONFIGURATION IDENTIFIER AND SECTION IDENTIFIER, RESPECTIVELY?? -->
<!-- SO I GUESS WE NEED 4 FIELDS HERE FOR THE LENGTHS AND DIAMETERS -->

## Additional Branchline Details

| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| storage_1 | O | The storage method for the branchlines | **Code** from [Branchline Storages](#branchlineStorages) | e.g., `BA` |
| storage_2 | O | The storage method for the branchlines | **Code** from [Branchline Storages](#branchlineStorages) | e.g., `BA` |
| storage_3 | O | The storage method for the branchlines | **Code** from [Branchline Storages](#branchlineStorages) | e.g., `BA` |
| storage_4 | O | The storage method for the branchlines | **Code** from [Branchline Storages](#branchlineStorages) | e.g., `BA` |

# (G-CONFIG-MITIGATION-DEVICES) Longline Gear Specifications > Mitigation Devices

| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| observed_ _trip_id | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |

## Tori Line Details

**ADD DEFINITION OF TORI LINE??**

<!-- Note: If the vessel was equipped with a tori line, provide tori line details below. If not tori line was present on board, fill in NA for not applicable. \_ from original ROS description form\*\* -->

| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| tori_line_length | M | The total length (m) of the tori line, excluding streamers | Float | **EXAMPLE TO ADD** |
| streamer_type | M | The type of streamers which are used with the tori line | **Code** from [Streamer Types](#streamerTypes) | e.g., `MU` |
| reach_surface | O | Indicates whether or not the streamers are long enough to touch the surface of the water in calm conditions (Yes/No/Unk) | String | `No` |
| streamer_line_length_max_m | M | The value of the maximum length (m) of individual streamer lines | Float | **EXAMPLE TO ADD** |
| streamer_line_length_min_m | O | The value of the minimum length (m) of individual streamer lines | Float | **EXAMPLE TO ADD** |
| streamer_number_per_line | M | The number of streamers that are attached to a single tori line | Integer | **EXAMPLE TO ADD** |
| distance_between_streamers_m | O | The distance (m) between streamers | Float | **EXAMPLE TO ADD** |
| tori_line_attached_height_m | M | The height that the tori line is attached above the water level | Float | **EXAMPLE TO ADD** |

| **Towed objects:** The total number and type of towed objects used to maintain tori line tension and achieve aerial extent when deployed 
::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| Number | O || Integer ||
| Type | O || **Code list to develop based on CPC feedback** || 
:::


## Other Mitigation Devices

| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| Device_1 | O | **DESCRIPTION TO ADD** | **Code** from [Mitigation Devices](#mitigationDevices) | e.g., `AA` |
| Device_2 | O | **DESCRIPTION TO ADD** | **Code** from [Mitigation Devices](#mitigationDevices) | e.g., `AA` |
| Device 3 | O | **DESCRIPTION TO ADD** | **Code** from [Mitigation Devices](#mitigationDevices) | e.g., `AA` |
| Device 4 | O | **DESCRIPTION TO ADD** | **Code** from [Mitigation Devices](#mitigationDevices) | e.g., `AA` |
| Device 5 | O | **DESCRIPTION TO ADD** | **Code** from [Mitigation Devices](#mitigationDevices) | e.g., `AA` |

# (E-SET) Longline Fishing Events > Setting Operations

| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| Observed trip ID | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` | 
| Set ID | M | The unique four-digit numerical code for each fishing set, beginning with 0001 and assigned consecutively from the first to the last line set of the observed trip | 4-digit number | e.g, `0007` |

## Setting Operations

| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| Start setting |||||

::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| Date and time | M | The date and the time in GMT/UTC the first dhan buoy and / or radio buoy is deployed to start the setting of the line | YYYY-MM-DD hh:mm | e.g., `2025-09-15 12:00` |
| Latitude | O | The latitude of the position at the start of the setting operation | Decimal degrees (two decimal places) | e.g., `-20.88` |
| Longitude | O | The longitude of the position at the start of the setting operation | Decimal degrees (two decimal places) | e.g., `55.53` |
:::

| End setting

::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| Date and time | M | The date and the time in GMT/UTC that the last dhan buoy and / or radio buoy is deployed | YYYY-MM-DD hh:mm | e.g., `2023-07-01 12:00` |
| Latitude | O | The latitude of the position at the end of the setting operation | Decimal degrees (two decimal places) | e.g., `-20.88` |
| Longitude | O | The longitude of the position at the end of the setting operation | Decimal degrees (two decimal places) | e.g., `55.53` |
:::

||||||
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| Vessel speed | M | The vessel's average speed (knots) during setting | Float | **EXAMPLE TO ADD** |
| Line setter speed | M | The speed setting (m/s) of the line setter | Float | **EXAMPLE TO ADD** |

| Mainline: Mainline material and total set length, i.e., the total deployed length of the mainline for the specific set. Usually calculated by multiplying the total time to set the line and the average line setter speed, taking into account any interruption times 

::: {style="margin-left:40px"}
| Element       | Requirement | Description |          Format          | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| Material | O | **DESCRIPTION TO ADD** | **Code** from [Line Material Types](#lineMaterialTypes) | e.g., `NL` |
| Mainline length value | O | **DESCRIPTION TO ADD** | Float | **EXAMPLE TO ADD** |
| Mainline length unit | O | **DESCRIPTION TO ADD** | Indicates the unit of (kilometres (km) or nautical miles (nm) | **EXAMPLE TO ADD** |
:::

<!-- Value should read "Mainline length value"? -->

| Clip on time

::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| Branchline | O | The average time interval in seconds between the "beeps" that indicate to the crew to clip on a branchline | Float | **EXAMPLE TO ADD** |
| Buoys | O | The average time interval in seconds between the "beeps" that indicate to the crew to clip on a buoy | Float | **EXAMPLE TO ADD** |
:::

|  |  |  |  |  |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| Number of total hooks set | M | The total number of hooks deployed for the set. Usually calculated by multiplying number of baskets by the average number of hooks between the baskets | Integer | **EXAMPLE TO ADD** |
| Number of total floats on set | O | The total number of floats deployed during the set, excluding radio/dhan buoys. Usually calculated by subtracting the number of buoys in their holders before setting by the number of buoys in their holders after setting | Integer | **EXAMPLE TO ADD** |
| Number of hooks between floats | M | The number of hooks set between floats. This will correspond to the number of hooks stored in each basket/tub, or on a reel and will be equivalent to the number of branchlines set | Integer | **EXAMPLE TO ADD** |
| Shark lines |  |  |  |  |

::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| Set | M | Indicates whether or not one or more shark lines were set during the operation (Yes/No/Unk) | String | `Yes` |
| Number of lines | O | The number of shark lines set during the operation. If no shark lines are set then record zero (0) | Integer | e.g., `23` |
:::

| Leader material

::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| Material type | M | Each leader type used in the set | **Code** from [Line Material Types](#lineMaterialTypes) | e.g., `NL` |
| Percentage | M | The percentage of total branchlines in the set estimated for each leader type used | Float | **EXAMPLE TO ADD** |
:::

<!-- Why "Each" leader type? Check reporting form -->

<!-- Estimate by counting the number of branchlines in a basket by leader type and dividing each count by the total hooks in the basket. This assumes uniform use of leader types across baskets in a set. Estimates should be adjusted if there is variation across baskets (within a set) in leader proportions  -->

| Branchline length max: specify the minimum and maximum total branchline lengths observed in the set. Total branchline length is measured (in meters) from the mainline clip to the hook. If total branchline lengths are uniform across the set, write the same number in the minimum and maximum fields

::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| Branchline length minimum | M | The minimum value of the total lengths of the branchlines deployed during the fishing set | Float | **EXAMPLE TO ADD** |
| Branchline length minimum unit | M | The unit of measurement of the minimum value of branchline length (cm or m) | Float | **EXAMPLE TO ADD** | 
| Branchline length maximum | M | The maximum value of the total lengths of the branchlines deployed during the fishing set | Float | **EXAMPLE TO ADD** |
| Branchline length maximum unit | M | The unit of measurement of the maximum value of branchline length (cm or m) | Float | **EXAMPLE TO ADD** | 
:::

||||||
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| Target species 1 | M | The list of species that are intentionally targeted in the fishery | **Code** from [Target Species](#targetSpecies) | e.g., `AL` |
| Target species 2 | O | The list of species that are intentionally targeted in the fishery | **Code** from [Target Species](#targetSpecies) | e.g., `AL` |
| Target species 3 | O | The list of species that are intentionally targeted in the fishery | **Code** from [Target Species](#targetSpecies) | e.g., `AL` |
| Target species 4 | O | The list of species that are intentionally targeted in the fishery | **Code** from [Target Species](#targetSpecies) | e.g., `AL` |
| VMS_ON | O | **ADD DESCRIPTION | String | e.g., `Yes` | 

# (E-SET-LIGHTS) Longline Fishing Events > Setting Operations > Attached Lights

| Element | Requirement | Description | Format | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| Observed trip ID | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |
| Set ID | M | The parent set identifier | 4-digit number | e.g., `0001` |

## Attached Lights

| Attached lights: Number of lights attached to the branchlines per type and colour

::: {style="margin-left:40px"}
| Element          | Requirement | Description |    Format     | Input value |
|:------- |:-----:|:-----------------------|:-------------:|:-------------:|
| Type | M | **DESCRIPTION TO ADD** | **Code** from [Light Types](#lightTypes) | e.g., `CL` |
| Colour | M | **DESCRIPTION TO ADD** | **Code** from [Light Colours](#lightColours) | e.g., `BU` |
| Number of lights | M | **DESCRIPTION TO ADD** | Integer | **EXAMPLE TO ADD** |
:::

# (E-SET-MITIGATION-MEASURES)

| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Observed trip ID | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |
| Set ID | M | The parent set identifier | 4-digit number | e.g., `0001` |

## Mitigation Measures

| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Number of tori lines deployed | M | The total number of tori lines deployed during the setting operation | Integer | e.g., `8` |
| Minimum deck lighting used | M | Indicates whether or not minimum deck lighting was used during night setting (Yes/No/Unk) | String | e.g., `Yes` |
| Hooks set between dusk dawn | M | **DESCRIPTION TO ADD** | Integer | **EXAMPLE TO ADD**  |
| Branchline weighted | O | Indicates whether or not the branchline was weighted (Yes/No/Unk) | String | **EXAMPLE TO ADD** |
| Average branchline weight | M | The average weight (g) of weights or sinkers attached to the branchlines (weights deployed on the snood prior to setting) | Float | **EXAMPLE TO ADD** |
| Percent branchline weighted | M | The proportion of branchlines weighted (%) | Float | **EXAMPLE TO ADD** |
| Hook sinker distance | M | The distance (cm) of the weights/sinkers from the eye of the hook | Float | **EXAMPLE TO ADD** |
| Hook pods | M | Indicates whether or not the bait is protected on the branchlines until they are a certain depth below the surface (Yes/No/Unk) | String | e.g., `No` |

<!-- #### ALERT: check reporting format for the minimum deck lighting used -->

## Branchline Details

| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Configuration number | O | The number of branchlines set by type (branchline configuration number). Branchline types must be in accordance to types previously defined under the "Gear specifications" section | Alphanumeric code | **EXAMPLE TO ADD** |
| Number of branchlines set | O | The number of branchlines set by type (branchline configuration number). Branchline types must be in accordance to types previously defined under the “Gear specifications" section | Integer | **EXAMPLE TO ADD**  |

<!-- Configuration number should read Configuration identifier ?? -->

## Other Mitigation Measures Used

| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Measure 1 | M | Any other mitigation measures observed | **Code** from [Mitigation Devices](#mitigationDevices) | e.g., `AA` |
| Measure 2 | M | Any other mitigation measures observed | **Code** from [Mitigation Devices](#mitigationDevices) | e.g., `AA` |
| Measure 3 | M | Any other mitigation measures observed | **Code** from [Mitigation Devices](#mitigationDevices) | e.g., `AA` |
| Measure 4 | M | Any other mitigation measures observed | **Code** from [Mitigation Devices](#mitigationDevices) | e.g., `AA` |


# (E-SET-HOOKS)

| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Observed trip ID | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |
| Set ID | M | The parent set identifier | 4-digit number | e.g., `0004` |

## Setting Operations \> Hook Details \> Hook

| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Types | M | The types of hooks used | **Code** from [Hook Types](#hookTypes) | **EXAMPLE TO ADD** |
| Percentage | O | The percentage (%) of hooks set by type | Float | **EXAMPLE TO ADD** |
| Variations | O | Indicates any variations in hook type, hook material, and presence/absence of hook ring where possible | String | **EXAMPLE TO ADD** |

# (E-SET-BAITS)

| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Observed trip ID | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |
| Set ID | M | The parent set identifier | 4-digit number | e.g., `0095` |

## Setting Operations \> Bait Details \> Bait

| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Condition | M | The bait type condition used | **Code** from [Bait Conditions](#baitConditions) | e.g., `DE`  |
| Species | M | The species/species group of bait used | **Code** from [Bait Species](#baitSpecies) | e.g., `ANX` |
| Percentage | M | The approximate proportion (%) of bait species and condition used across all hooks in the set | Float | **EXAMPLE TO ADD** |
| Dye colour | O | The colour or colours that the different baits are dyed | String | e.g., `blue`  |

<!-- DO NOT UNDERSTAND THE ABOVE DEFINITION OF PERCENTAGE, WHICH INCLUDES REFERENCE TO "CONDITION"?? -->

# (E-SET-HAULING)

| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Observed trip ID | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |
| Set ID | M | The parent set identifier | 4-digit number | e.g., `0084` |

## Hauling Operations

| Element       | Requirement | Description | Format | Input value |
|:--------------|:-----------:|:------------|:------:|:-----------:|
| Start hauling |||||

::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Date and time | M | The date and the time in GMT/UTC when the first dhan buoy and / or radio buoy is hauled back on-board to start hauling the line | YYYY-MM-DD hh:mm | e.g., `2025-09-15 12:00` |
| Latitude | O | The latitude of the position at the start of the hauling operation | Decimal degrees (two decimal places) | e.g., `-20.88` |
| Longitude | O | The longitude of the position at the start of the hauling operation | Decimal degrees (two decimal places) | e.g., `55.53` |
:::

<!-- CHANGED POSITION TO EXPLICITLY INCLUDE LONGITUDE AND LATITUDE -->

| End hauling

::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Date and time | M | The date and the time when the when the last component of the longline gear (dhan buoy and / or radio buoy) is hauled back on-board | YYYY-MM-DD hh:mm | e.g., `2025-09-15 12:00` |
| Latitude | O | The latitude of the position at the end of the hauling operation | Decimal degrees (two decimal places) | e.g., `-20.88` |
| Longitude | O | The longitude of the position at the end of the hauling operation | Decimal degrees (two decimal places) | e.g., `55.53` |
:::


||||||
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Offal management | O | The fate given to the offal (fish heads, guts, etc.) and bait produced during the observed set | **Code** from [Offal Management Types](#offalManagementTypes) | e.g., `AH` |
| **Position of offal disposal:** The position where offal and used bait was disposed
::: {style="margin-left:40px"}
| Element              | Requirement | Description | Format  | Input value |
|:---------------------|:-----------:|:------------|:-------:|:-----------:|
| Position 1 | O |  |  **Code** from [Vessel Section](#vesselSection) | e.g., `BW`  |
| Position 2 | O |  |  **Code** from [Vessel Section](#vesselSection) | e.g., `BW`  |
| Position 3 | O |  |  **Code** from [Vessel Section](#vesselSection) | e.g., `BW`  |
| Position 4 | O |  |  **Code** from [Vessel Section](#vesselSection) | e.g., `BW`  |
:::

| Bird scaring device at hauler | M | Indicates whether or not a bird scaring device was deployed during hauling operations (Yes/No/Unk) | String  | e.g., `No`  |
| Number of branchline haulings observed | M | The number of branchline haulings observed | Integer | **EXAMPLE TO ADD** |
| Number of hooks retrieved during observation | M | The number of hooks retrieved during observation | Integer | **EXAMPLE TO ADD** |
| Sampling protocol | M | Sampling protocol followed by the observer | **CODE** from [Sampling Protocol](#samplingProtocol) | e.g., `EP` |

# (E-SET-HAULING-BITEOFFS)

| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Observed trip ID | M | Refers to parent observed trip | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |
| Set ID | M | Refers to parent Set ID | 4-digit number | e.g., `0023` |

## Biteoff Details - Branchline

Biteoff details - branchline: For each branchline configuration setup previously identified how many have had the hook bitten off. This only includes bite-offs observed while the observer was in a position to observe and record the hooks coming directly out of the water - from original ROS description form \*\*

::: {style="margin-left:40px"}
| Element              | Requirement | Description | Format  | Input value |
|:---------------------|:-----------:|:------------|:-------:|:-----------:|
| Configuration number | O | **DESCRIPTION TO ADD** | Integer | **EXAMPLE TO ADD** |
| Number of biteoffs   | O | **DESCRIPTION TO ADD** | Integer | **EXAMPLE TO ADD** |
:::

<!-- Configuration number to change to configuration identifier?? -->

# (E-SET-CATCHES)

| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Observed trip ID | M | Refers to parent observed trip | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |
| Set ID | M | Refers to parent Set ID | 4-digit number | e.g., `0285` |
| Catch ID | M | Unique within a specific set, as a branch of set-ID | Alphanumeric code | **EXAMPLE TO ADD** |

## Catch Details

| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Species | M | The species for each specimen observed | **Code** from [All Species](#allSpecies)| e.g., `ABL` |

| Fate: The fate which includes whether it was retained or discarded and the reason

::: {style="margin-left:40px"}
| Element              | Requirement | Description | Format  | Input value |
|:---------------------|:-----------:|:------------|:-------:|:-----------:|
| Type | M | **DESCRIPTION TO ADD** | **Code** from [Types of Fate](#fateType) | e.g., `DI` |
| Code | M | **DESCRIPTION TO ADD** | **Code** from [Fates](#fates) | e.g., `DL` |
:::

| Sampling method code | M | **DESCRIPTION TO ADD** |  **Code** from [Sampling Methods for Catch Estimation](#samplingMethodsCatchEstimation) | e.g., `EP` |
| Number of fish | M | The numbers of individuals observed/caught by species and fate (including if recording at an individual animal level) | Integer | **EXAMPLE TO ADD** |

Weight: The catch weight corresponding to the specified product type recorded in 'weight code’. If the fish has not been processed, record the unprocessed weight

::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Processing type | O | **DESCRIPTION TO ADD** | **Code** from  [Fish Processing Types](#fishProcessingTypes) | e.g., `DR` |
| Value | O | **DESCRIPTION TO ADD** | Float | **EXAMPLE TO ADD** |
| Weight units | O | **DESCRIPTION TO ADD** | Indicate units (kg or tonnes) | e.g., `kg`  |
| Estimation method | O | **DESCRIPTION TO ADD** | **Code** from [Total Catch Estimation](#totalCatchEstimation) | e.g., `EP` |
:::

# (E-SET-CATCHES-SPECIMEN)

| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Observed trip ID | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |
| Set ID | M | The parent set identifier | 4-digit number | e.g., `0003` |
| Catch ID | M | The parent catch identifier | Alphanumeric code | **EXAMPLE TO ADD** |
| Specimen ID | M | A unique four-digit numerical code for each specimen, beginning with 0001, assigned consecutively within the same catch detail of a set during the observed trip | 4-digit number | e.g., `0005` |

## Specimen Details

| Element | Requirement | Description | Format | Input value |
|:------------|:-----------:|:----------------------|:-----------:|:-----------:|
| Sampling period | M | **DESCRIPTION TO ADD** | **Code** from [Sampling Period](#samplingPeriod) | e.g., `BS` |
| Sampling method | M | The sampling method used for the collection of biological sub-sample(s) | **Code** from [Biological Sampling Method](#biologicalSamplingMethod) | e.g., `ES` |

| Length 1: Length of individual specimen

::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Type | M | The type of length used for the measurement | **Code** from [Length Measurements](#lengthMeasurements) | e.g., `CF` |
| Value | M | The value of length corresponding to the length type taken rounded to the lower centimetre | Float | e.g., `34` |
| Measuring tool | M | Specify the tool code used for the measurement | **Code** from [Length Measurement Tools](#lengthMeasurementTools)  |e.g., `CA`  |
| Is straight | M | Indicates whether the size measurement was made straight (Yes/No/Unk) | String | e.g., `Yes` |
:::

<!-- I would remove the "Is straight" field since the type of length measurements indicates how the measurement was taken (straight, curved), and the guidelines for observers should include that the measurements should be taken straight for fish (fork length, total length, etc.) -->

| Length 2: **DEFINITION TO ADD?**

::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Type | O | The length used for the measurement | **Code** from [Length Measurements](#lengthMeasurements)| e.g., `FL` |
| Value | O | The value of length (cm) corresponding to the length type taken rounded to the lower centimetre | Float | e.g., `86` |
| Measuring tool | O | The tool used for the measurement | **Code** from [Length Measurement Tools](#lengthMeasurementTools) | e.g., `CA`  |
| Is straight | O | Indicates whether the size measurement was made straight (Yes/No/Unk) | String | e.g., `No`  |
:::

<!-- I would remove the "Is straight" field since the type of length measurements indicates how the measurement was taken (straight, curved), and the guidelines for observers should include that the measurements should be taken straight for fish (fork length, total length, etc.) -->

| Weight: The specimen's weight corresponding to the specified product type recorded in 'weight code'. Unprocessed weight when the fish has not been processed

::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Processing type | O | The processing used for the weight measurement | **Code** from [Weight Measurements](#weightMeasurements)  | e.g., `GG` |
| Value | O | The weight corresponding to the measurement type code | Float | e.g., `43.2` |
| KG/T  | O | Unit of weight (kg or t) | String | e.g., `kg` |
| Estimation method code | O | Method used to estimate weight of specimen | **Code** from [Weight Estimation Methods](#weightEstimationMethods) | e.g., `BR` |
:::

<!-- PROPOSAL TO RENAME 'KG/T' to "Weight unit" or "Unit" -->


| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Sex | O | The sex of the sampled fish specimen. If unknown record "U" | **Code** from [Sex](#sex) | e.g., `F` |

| Maturity: optional reporting
| The stage of maturity of the specimen according to standard maturity scales approved by the IOTC. If unknown record UNK.

::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Scale | O | **DESCRIPTION TO ADD** | String | **Code list being developed** |
| Stage | O | **DESCRIPTION TO ADD** | String | **Code list being developed** |
:::

| Sample collected: The following details on the collection of samples: a) type (e.g., otoliths, spine clippings, and genetic samples), b) preservation method (e.g., alcohol, frozen, etc.), c) destination (i.e., location to be sent/stored)

::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Type | O | **DESCRIPTION TO ADD** | Code from [Sampling Type](#samplingMethodsForSamplingCollections) | **CODE LIST TO DEVELOP** | **EXAMPLE TO ADD**|
| Preservation method | O | **DESCRIPTION TO ADD** | Code from [Sample Preservation Method](#fishPreservationMethods) | **CODE LIST TO DEVELOP** | **EXAMPLE TO ADD** |
| **Destination** | **DESCRIPTION TO ADD & ADD FIELD TO THE FORMS** | **CODE LIST TO DEVELOP** | **EXAMPLE TO ADD** |
:::

| Depredation method:

::::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Depredation source | O | For depredated specimens/or catch, record the depredation source based on depredation scar characteristics. For non-depredated specimens record NA | **Code** from [Depredation Sources](#depredationSources) | e.g., `BA` |
| Observed predatory | O | For depredated specimens/or catch, the predator species directly observed and identified. If the predator was not observed, the value is 'UNK' (unknown). For non-depredated specimens record, the value is NA (not available) | **Code** from [Predator Species](#predatorSpecies)| e.g., AG15 |

<!-- **Is the predator codelist right? is not a 3-alpha code** -->

# (E-SET-CATCHES-SSI)

| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Observed trip ID | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` |
| Set ID | M | The parent set identifier | 4-digit number | e.g., `0004` |
| Catch ID | M | The parent catch identifier | Alphanumeric code | **EXAMPLE TO ADD** |
| Specimen ID | M | The parent specimen identifier | 4-digit code | **EXAMPLE TO ADD** |

## Additional Catch Details on SSI

| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Condition at capture | M | The condition of the specimen at capture | **Code** from [Individual Conditions](#individualConditions) | e.g., `A0` |
| Condition at release | M | The condition of the specimen at the time of release | **Code** from [Individual Conditions](#individualConditions) | e.g., `A0` |
| Gear interaction | M | The type of interaction of the specimen with the fishing gear ("UK" if unknown as not possible to collect) | **Code** from [Gear Interactions](#gearInteractions) | e.g., `EF` |
| Hook type | O | The type of hook the individual was hauled on | **Code** [Hook Types](#hookTypes) from | e.g., `C11` |
| Bait | O | The type and condition of the bait the individual was hauled on 

::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Bait condition | O | **DESCRIPTION TO ADD** | **Code** from [Bait Conditions](#baitConditions) | e.g., `DE` |
| Bait type | O |  **DESCRIPTION TO ADD** | **Code** from [Bait Types](#baitTypes) | e.g., `FF` | 
:::

| Leader ||||
::: {style="margin-left:40px"}

| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Material | M | The leader material the SSI individual was hauled on | **Code** from [Line Material Types](#lineMaterialTypes)| e.g., `MN` |
| Diameter | O | The thickness (mm) of the leader the SSI individual was hauled on | Float |  |
:::

| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| De-hooker device | O | The de-hooking or line cutting device used to extract the hook | **Code** [De-hooker Types](#dehookerTypes) from | e.g., HD  |
| Brought onboard | O | Indicates whether or not the specimen was brought onboard (Yes/No/Unk) | String | e.g., `Yes` |
| Handling method | O | Detail how the specimen was brought onboard | **Code** from [Handling Methods](#handlingMethods) | e.g., `AN` |
| Revival | O | Indicates whether or not the release took place with resuscitation for turtles (Yes/No/Unk) | String | e.g., `Yes`  |
| Photo ID | O | The unique identifier of the photo taken of a specimen | Alphanumeric code | e.g., `Doe_Hawwa_20260302_1435_hawksbill.png` |
| Depredation details |||||

::: {style="margin-left:40px"}
| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Depredation source | O | The depredation source based on depredation scar characteristics for depredated specimens (NA for non-depredated specimens) | **Code** from [Depredation Sources](#depredationSources) | e.g., `BA` |
| Observed predator | O | The predator species directly observed and identified or unknown (UNK) when not observed (NA for non-depredated specimens) | **CODE** from [Predator Species](#predatorSpecies) | e.g., `AG15` |
:::

# (E-SET-TAG-DETAILS)

| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Observed trip ID | M | The parent observed trip identifier | Alphanumeric | e.g., `2024-01-23/IOTCFRA001/IOTC012345/LL` | 
| Set ID | M | The parent set identifier | 4-digit number | e.g., `0023` |
| Catch ID | M | The parent catch identifier | Alphanumeric | **EXAMPLE TO ADD** |
| Specimen ID | M | The parent specimen identifier ID | 4-digit number | **EXAMPLE TO ADD** |

## Tag Details

| Element | Requirement | Description | Format | Input value |
|:--------------|:-------------:|:--------------|:-------------:|:-------------:|
| Release | O |  Indicates whether or not the individual was re-released with a tag attached (Yes/No/Unk) | String | e.g., `No` |
| Recovery | O | Indicates whether or not the individual was recovered with a tag attached (Yes/No/Unk) | String  | e.g., `Yes`  |
| Type | O | The type of tag used | **Code** from [Tag Types](#tagTypes) | e.g., `CP` |
| Tag number | O | The tag identifier(s) | Alphanumeric | **EXAMPLE TO ADD** |
| Finder name | O | **DESCRIPTION TO ADD** | String | e.g., `Jane Doe` |
| Finder contact details | O | **DESCRIPTION TO ADD** | String | e.g., `345 Spear Street, San Francisco, CA 94105, USA | (650) 214-6369 | jane.doe@fishing.org` |

# Reporting Deadlines

-   **Longline fisheries**: 30 June (preliminary), 30 December (final)

# Reference Code Lists

## Entities {#entities}

-   [Permalink](https://data.iotc.org/reference/latest/domain/admin/#entities)
-   **Version**: `r version_number("ENTITIES")`
-   **Last update**: `r last_update("ENTITIES")`

```{r collapse = TRUE}
out_dt(ENTITIES, "ENTITIES")
```

## Countries {#countries}

-   [Permalink](https://data.iotc.org/reference/latest/domain/admin/#countries)
-   **Version**: `r version_number("COUNTRIES")`
-   **Last update**: `r last_update("COUNTRIES")`

```{r collapse = TRUE}
out_dt(COUNTRIES, "COUNTRIES")
```

## Ports {#ports}

-   [Permalink](https://data.iotc.org/reference/latest/domain/admin/#Ports)
-   **Version**: `r version_number("PORTS")`
-   **Last update**: `r last_update("PORTS")`

```{r collapse = TRUE}
out_dt(PORTS[, -c("POINT")], "PORTS")
```

## Reasons for Days Lost {#reasonsDaysLost}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#reasonsDaysLost)
-   **Version**: `r version_number("REASONS_DAYS_LOST")`
-   **Last update**: `r last_update("REASONS_DAYS_LOST")`

```{r collapse = TRUE}
out_dt(REASONS_DAYS_LOST, "REASONS_DAYS_LOST")
```

## Target Species {#targetSpecies}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#targetSpecies)
-   **Version**: `r version_number("SPECIES_TARGET")`
-   **Last update**: `r last_update("SPECIES_TARGET")`

```{r collapse = TRUE}
out_dt(SPECIES_TARGET, "SPECIES_TARGET")
```

<!-- Code list to remove from IOTC Reference Data Catalogue to put in LEGACY?: https://data.iotc.org/reference/latest/domain/biology/#targetSpecies. Replaced by the following code list (https://data.iotc.org/reference/latest/domain/biology/#targetSpecies) used to define fisheries identifiers and developed in collaboration with CPCs through IOTC Data Reporting Workshops -->

## Fishing Gears {#fishingGear}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#gears)
-   **Version**: `r version_number("GEAR_TYPES")`
-   **Last update**: `r last_update("GEAR_TYPES")`

```{r collapse = TRUE}
out_dt(GEAR_TYPES, "GEAR_TYPES")
```

## Hull Material Types {#hullMaterialTypes}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#hullMaterialTypes)
-   **Version**: `r version_number("HULL_MATERIAL_TYPES")`
-   **Last update**: `r last_update("HULL_MATERIAL_TYPES")`

```{r collapse = TRUE}
out_dt(HULL_MATERIAL_TYPES, "HULL_MATERIAL_TYPES")
```

## Fish Preservation Methods {#fishPreservationMethods}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#fishPreservationMethods)
-   **Version**: `r version_number("FISH_PRESERVATION_METHODS")`
-   **Last update**: `r last_update("FISH_PRESERVATION_METHODS")`

```{r collapse = TRUE}
out_dt(FISH_PRESERVATION_METHODS, "FISH_PRESERVATION_METHODS")
```

## Vessel Size Types

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#vesselSizeTypes)
-   **Version**: `r version_number("VESSEL_SIZE_TYPES")`
-   **Last update**: `r last_update("VESSEL_SIZE_TYPES")`

```{r collapse = TRUE}
out_dt(VESSEL_SIZE_TYPES, "VESSEL_SIZE_TYPES")
```

## Fish Storage Types {#fishStorageTypes}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#fishStorageTypes)
-   **Version**: `r version_number("FISH_STORAGE_TYPES")`
-   **Last update**: `r last_update("FISH_STORAGE_TYPES")`

```{r collapse = TRUE}
out_dt(FISH_STORAGE_TYPES, "FISH_STORAGE_TYPES")
```

## Waste Categories {#wasteCategories}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#wasteCategories)
-   **Version**: `r version_number("WASTE_CATEGORIES")`
-   **Last update**: `r last_update("WASTE_CATEGORIES")`

```{r collapse = TRUE}
out_dt(WASTE_CATEGORIES, "WASTE_CATEGORIES")
```

## Storage/Disposal Methods {#storageDisposalMethods}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#wasteDisposalMethods)
-   **Version**: `r version_number("WASTE_DISPOSAL_METHODS")`
-   **Last update**: `r last_update("WASTE_DISPOSAL_METHODS")`

```{r collapse = TRUE}
out_dt(WASTE_DISPOSAL_METHODS, "WASTE_DISPOSAL_METHODS")
```

## Line Material Types {#lineMaterialTypes}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#lineMaterialTypes)
-   **Version**: `r version_number("LINE_MATERIAL_TYPES")`
-   **Last update**: `r last_update("LINE_MATERIAL_TYPES")`

```{r collapse = TRUE}
out_dt(LINE_MATERIAL_TYPES, "LINE_MATERIAL_TYPES")
```

## Branchline Storages {#branchlineStorages}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#branchlineStorages)
-   **Version**: `r version_number("BRANCHLINE_STORAGES")`
-   **Last update**: `r last_update("BRANCHLINE_STORAGES")`

```{r collapse = TRUE}
out_dt(BRANCHLINE_STORAGES, "BRANCHLINE_STORAGES")
```

## Streamer Types {#streamerTypes}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#streamerTypes)
-   **Version**: `r version_number("STREAMER_TYPES")`
-   **Last update**: `r last_update("STREAMER_TYPES")`

```{r collapse = TRUE}
out_dt(STREAMER_TYPES, "STREAMER_TYPES")
```

## Mitigation Devices {#mitigationDevices}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#mitigationDevices)
-   **Version**: `r version_number("MITIGATION_DEVICES")`
-   **Last update**: `r last_update("MITIGATION_DEVICES")`

```{r collapse = TRUE}
out_dt(MITIGATION_DEVICES, "MITIGATION_DEVICES")
```

## Light Types {#lightTypes}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#lightTypes)
-   **Version**: `r version_number("LIGHT_TYPES")`
-   **Last update**: `r last_update("LIGHT_TYPES")`

```{r collapse = TRUE}
out_dt(LIGHT_TYPES, "LIGHT_TYPES")
```

## Light Colours {#lightColours}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#lightColours)
-   **Version**: `r version_number("LIGHT_COLOURS")`
-   **Last update**: `r last_update("LIGHT_COLOURS")`

```{r collapse = TRUE}
out_dt(LIGHT_COLOURS, "LIGHT_COLOURS")
```

## Hook Types {#hookTypes}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#hookTypes)
-   **Version**: `r version_number("HOOK_TYPES")`
-   **Last update**: `r last_update("HOOK_TYPES")`

```{r collapse = TRUE}
out_dt(HOOK_TYPES, "HOOK_TYPES")
```

## Bait Conditions {#baitConditions}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#baitConditions)
-   **Version**: `r version_number("BAIT_CONDITIONS")`
-   **Last update**: `r last_update("BAIT_CONDITIONS")`

```{r collapse = TRUE}
out_dt(BAIT_CONDITIONS, "BAIT_CONDITIONS")
```

## Bait Species {#baitSpecies}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#baits)
-   **Version**: `r version_number("SPECIES_BAITS")`
-   **Last update**: `r last_update("SPECIES_BAITS")`

**just to double check, we don't want "bait type", but we do want "bait species"** 

```{r collapse = TRUE}
out_dt(SPECIES_BAITS, "SPECIES_BAITS")
```

## Offal Management Types {#offalManagementTypes}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#offalManagementTypes)
-   **Version**: `r version_number("OFFAL_MANAGEMENT_TYPES")`
-   **Last update**: `r last_update("OFFAL_MANAGEMENT_TYPES")`

```{r collapse = TRUE}
out_dt(OFFAL_MANAGEMENT_TYPES, "OFFAL_MANAGEMENT_TYPES")
```

## Vessel Sections {#vesselSections}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#vesselSections)
-   **Version**: `r version_number("VESSEL_SECTIONS")`
-   **Last update**: `r last_update("VESSEL_SECTIONS")`

```{r collapse = TRUE}
out_dt(VESSEL_SECTIONS, "VESSEL_SECTIONS")
```

## Sampling protocols {#samplingProtocols}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#samplingProtocols)
-   **Version**: `r version_number("SAMPLING_PROTOCOLS")`
-   **Last update**: `r last_update("SAMPLING_PROTOCOLS")`

```{r collapse = TRUE}
out_dt(SAMPLING_PROTOCOLS, "SAMPLING_PROTOCOLS")
```

## All Species {#allSpecies}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#allSpecies)
-   **Version**: `r version_number("SPECIES")`
-   **Last update**: `r last_update("SPECIES")`

```{r collapse = TRUE}
out_dt(SPECIES, "SPECIES")
```

## Types of Fate {#fateType}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#typesOfFate)
-   **Version**: `r version_number("TYPES_OF_FATE")`
-   **Last update**: `r last_update("TYPES_OF_FATE")`

```{r collapse = TRUE}
out_dt(TYPES_OF_FATE, "TYPES_OF_FATE")
```

## Fates {#fates}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#fates)
-   **Version**: `r version_number("FATES")`
-   **Last update**: `r last_update("FATES")`

```{r collapse = TRUE}
out_dt(FATES, "FATES")
```

## Sampling Method for Catch Estimation {#samplingMethodCatchEstimation}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#samplingMethodsForCatchEstimation)
-   **Version**: `r version_number("SAMPLING_METHODS_FOR_CATCH_ESTIMATION")`
-   **Last update**: `r last_update("SAMPLING_METHODS_FOR_CATCH_ESTIMATION")`

```{r collapse = TRUE}
out_dt(SAMPLING_METHODS_FOR_CATCH_ESTIMATION, "SAMPLING_METHODS_FOR_CATCH_ESTIMATION")
```


## Fish Processing Types {#fishProcessingTypes}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#fishProcessingTypes)
-   **Version**: `r version_number("FISH_PROCESSING_TYPES")`
-   **Last update**: `r last_update("FISH_PROCESSING_TYPES")`

```{r collapse = TRUE}
out_dt(FISH_PROCESSING_TYPES, "FISH_PROCESSING_TYPES")
```

## Total Catch Estimation {#totalCatchEstimation}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#samplingMethodsForCatchEstimation)
-   **Version**: `r version_number("SAMPLING_METHODS_FOR_CATCH_ESTIMATION")`
-   **Last update**: `r last_update("SAMPLING_METHODS_FOR_CATCH_ESTIMATION")`

```{r collapse = TRUE}
out_dt(SAMPLING_METHODS_FOR_CATCH_ESTIMATION, "SAMPLING_METHODS_FOR_CATCH_ESTIMATION")
```

## Sampling Period {#samplingPeriod}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#samplingPeriods)
-   **Version**: `r version_number("SAMPLING_PERIODS")`
-   **Last update**: `r last_update("SAMPLING_PERIODS")`

```{r collapse = TRUE}
out_dt(SAMPLING_PERIODS, "SAMPLING_PERIODS")
```

## Biological Sampling Method {#biologicalSamplingMethod}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#samplingMethodsForSamplingCollection)
-   **Version**: `r version_number("SAMPLING_METHODS_FOR_SAMPLING_COLLECTIONS")`
-   **Last update**: `r last_update("SAMPLING_METHODS_FOR_SAMPLING_COLLECTIONS")`

```{r collapse = TRUE}
out_dt(SAMPLING_METHODS_FOR_SAMPLING_COLLECTIONS, "SAMPLING_METHODS_FOR_SAMPLING_COLLECTIONS")
```

## Length Measurements {#lengthMeasurements}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#lengthMeasurements)
-   **Version**: `r version_number("MEASUREMENTS")`
-   **Last update**: `r last_update("MEASUREMENTS")`

```{r collapse = TRUE}
out_dt(MEASUREMENTS, "MEASUREMENTS")
```
**I do not see a more specific schema in the pgAdmin codelists**


## Length Measurement Tools {#lengthMeasurementTools}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#lengthMeasurementTools)
-   **Version**: `r version_number("MEASUREMENT_TOOLS")`
-   **Last update**: `r last_update("MEASUREMENTS_TOOLS")`

```{r collapse = TRUE}
out_dt(MEASUREMENT_TOOLS, "MEASUREMENT_TOOLS")
```

## Weight Measurements {#weightMeasurememts}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#weightMeasurements)
-   **Version**: `r version_number("MEASUREMENTS")`
-   **Last update**: `r last_update("MEASUREMENTS")`

```{r collapse = TRUE}
out_dt(MEASUREMENTS[TYPE_OF_MEASUREMENT_CODE == "WG", -c("TYPE_OF_MEASUREMENT_CODE")], "MEASUREMENTS")
```

## Weight Estimation Methods {#weightEstimationMethods}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#weightEstimationMethods)
-   **Version**: `r version_number("MEASUREMENT_TOOLS")`
-   **Last update**: `r last_update("MEASUREMENTS_TOOLS")`

```{r collapse = TRUE}
out_dt(MEASUREMENT_TOOLS[TYPE_OF_MEASUREMENT_CODE == "WG", -c("TYPE_OF_MEASUREMENT_CODE")], "MEASUREMENT_TOOLS")
```

## Sex {#sex}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#sex)
-   **Version**: `r version_number("SEX")`
-   **Last update**: `r last_update("SEX")`

```{r collapse = TRUE}
out_dt(SEX, "SEX")
```

## Sampling Type {#samplingMethodsForSamplingCollections}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#samplingMethodsForSamplingCollection)
-   **Version**: `r version_number("SAMPLING_METHODS_FOR_SAMPLING_COLLECTIONS")`
-   **Last update**: `r last_update("SAMPLING_METHODS_FOR_SAMPLING_COLLECTIONS")`

```{r collapse = TRUE}
out_dt(SAMPLING_METHODS_FOR_SAMPLING_COLLECTIONS, "SAMPLING_METHODS_FOR_SAMPLING_COLLECTIONS")
```

## Sample Preservation Methods{#fishPreservationMethods}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#fishStorageTypes)
-   **Version**: `r version_number("FISH_PRESERVATION_METHODS")`
-   **Last update**: `r last_update("FISH_PRESERVATION_METHODS")`

```{r collapse = TRUE}
out_dt(FISH_PRESERVATION_METHODS, "FISH_PRESERVATION_METHODS")
```

## Depredation Sources {#depredationSources}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#depredationSources)
-   **Version**: `r version_number("DEPREDATION_SOURCES")`
-   **Last update**: `r last_update("DEPREDATION_SOURCES")`

```{r collapse = TRUE}
out_dt(DEPREDATION_SOURCES, "DEPREDATION_SOURCES")
```

## Predator Species {#predatorSpecies}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#predators)
-   **Version**: `r version_number("SPECIES_PREDATORS")`
-   **Last update**: `r last_update("SPECIES_PREDATORS")`

```{r collapse = TRUE}
out_dt(SPECIES_PREDATORS, "SPECIES_PREDATORS")
```

## Individual Conditions {#individualConditions}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#individualConditions)
-   **Version**: `r version_number("INDIVIDUAL_CONDITIONS")`
-   **Last update**: `r last_update("INDIVIDUAL_CONDITIONS")`

```{r collapse = TRUE}
out_dt(INDIVIDUAL_CONDITIONS, "INDIVIDUAL_CONDITIONS")
```

## Gear Interactions {#gearInteractions}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#gearInteractions)
-   **Version**: `r version_number("GEAR_INTERACTIONS")`
-   **Last update**: `r last_update("GEAR_INTERACTIONS")`

```{r collapse = TRUE}
out_dt(GEAR_INTERACTIONS, "GEAR_INTERACTIONS")
```

## Hook Types {#hookTypes}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#hookTypes)
-   **Version**: `r version_number("HOOK_TYPES")`
-   **Last update**: `r last_update("HOOK_TYPES")`

```{r collapse = TRUE}
out_dt(HOOK_TYPES, "HOOK_TYPES")
```

## Bait Conditions {#baitConditions}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#baitConditions)
-   **Version**: `r version_number("BAIT_CONDITIONS")`
-   **Last update**: `r last_update("BAIT_CONDITIONS")`

```{r collapse = TRUE}
out_dt(BAIT_CONDITIONS, "BAIT_CONDITIONS")
```

## De-hooker Types {#dehookerTypes}

-   [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#dehookerTypes)
-   **Version**: `r version_number("DEHOOKER_TYPES")`
-   **Last update**: `r last_update("DEHOOKER_TYPES")`

```{r collapse = TRUE}
out_dt(DEHOOKER_TYPES, "DEHOOKER_TYPES")
```

## Handling Methods {#handlingMethods}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#handlingMethods)
-   **Version**: `r version_number("HANDLING_METHODS")`
-   **Last update**: `r last_update("HANDLING_METHODS")`

```{r collapse = TRUE}
out_dt(HANDLING_METHODS, "HANDLING_METHODS")
```

## Tag Types {#tagTypes}

-   [Permalink](https://data.iotc.org/reference/latest/domain/biology/#tagTypes)
-   **Version**: `r version_number("TAG_TYPES")`
-   **Last update**: `r last_update("TAG_TYPES")`

```{r collapse = TRUE}
out_dt(TAG_TYPES, "TAG_TYPES")
```
