---
title: "IOTC statistical data reporting: Form 7PR (v`r BASE_VERSION`)"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  word_document2:
    reference_docx: "../../templates/doc_template.docx"
    number_sections: FALSE
    reference_num: TRUE
    fig_caption: TRUE

  html_document2:
    css: "../../templates/html_template.css"
    includes: 
      in_header: "../../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---
  
# Description
  
This form supports the *voluntary* reporting of _prices of fish products for tuna and tuna-like species under IOTC mandate_.

Click [here](./Form-7PR-legacy.xlsm) to download an empty version of the legacy form 7PR, or [return](../index.html) to the list of all versions of the IOTC statistical data reporting forms. 

# Reporting deadlines

- **Longline fisheries**: 30 June (preliminary), 30 December (final)
- **Surface fisheries**: 30 June (final)
- **Coastal fisheries**: 30 June (final)

# Stratification

## General information

| Element | Requirement | Description | Input value |
| :----------------- | :-----: | :----------------------- | :-------: |
| Reporting year | M | Gregorian calendar year of the fishing activities reported through the dataset | Integer (e.g., 1996) |
| Reporting entity | M | Entity reporting the dataset to the IOTC Secretariat | **Code** from [Entities](#entities) |
| Flag state | M | Country registration of the fishing vessels | **Code** from [Countries](#countries) |

## Data elements

| Element | Requirement | Description | Input value |
| :----------------- | :-----: | :----------------------- | :-------: |
| Month | M | Gregorian calendar month of the fish sale | **1**: Jan; **2**: Feb, ... **12**: Dec |
| Currency | M | Price currency | **Code** from [Currencies](#currencies) |
| Processing | M | Processing type applied to species | **Code** from [Types of fish processing](#fishProcessingType) |
| Product type | M | Type of fish product | **Code** from [Types of product](#fishProductTypes) |
| Preservation type  | M | Type of preservation method | **Code** from [Methods of fish preservation](#FishPreservationMethod) |
| Species | M | Fish species | **Code** from [Species](#IOTCSpecies) |
| Weight unit  | M | Unit of fish weight | **Code** from [Weight units](#weightUnits) |
| Weight class(lo) | M | Lowest weight class | Numeric value |
| Weight class(hi) | M | Highest weight class | Numeric value |

# Reporting metadata

| Element | Requirement | Description | Format | Example |
| :--------| :----: | :----------------------- | :-------- | :------------ |
| Liaison officer full name | M  | Name of the liaison officer in charge of the compilation of the data | Plain text | John Doe |
| Liaison officer email	 | M | Email address of the liaison officer in charge of the compilation of the data | Valid email address | [John.Doe\@fao.org](mailto:John.Doe@fao.org){.email} |
| Organisation name | M | Name of the organisation in charge of the compilation of the data | Plain text | National Institute of Fisheries |
| Organisation email | O | Email address of the organisation in charge of the compilation of the data | [nif\@gov.sc](mailto:nif@gov.sc){.email} |
| Finalisation date | M | Date of finalisation of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1996-03-27 |
| Submission date | M | Date of submission of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1997-03-21 |

# Reference code lists

## Entities {#entities}

```{r collapse = TRUE}
out_dt(ENTITIES, "ENTITIES")
```

## Countries {#countries}

```{r collapse = TRUE}
out_dt(COUNTRIES, "COUNTRIES")
```

## Catch units {#weightUnits}

```{r collapse = TRUE}
out_dt(CATCH_UNITS, "CATCH_UNITS")
```

## IOTC species {#IOTCSpecies}

```{r collapse = TRUE}
out_dt(SPECIES[IS_IOTC == TRUE & IS_AGGREGATE == FALSE], "SPECIES") %>% formatStyle(columns = "NAME_SCIENTIFIC", fontStyle = "italic")
```

## Types of fish processing {#fishProcessingType}

```{r collapse = TRUE}
out_dt(FISH_PROCESSING_TYPES, "FISH_PROCESSING_TYPES")
```

## Types of product {#fishProductTypes}

```{r collapse = TRUE}
out_dt(FISH_PRODUCT_TYPES, "FISH_PRODUCT_TYPES")
```

## Methods of fish preservation {#fishPreservationMethod}

```{r collapse = TRUE}
out_dt(FISH_PRESERVATION_METHODS, "FISH_PRESERVATION_METHODS")
```
