---
title: "IOTC Statistical Data Reporting: Form 4SF (v`r DOI_VERSION`)"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  html_document2:
    css: "../templates/fao_template_simplified.css"
    mathjax: null
    includes: 
      in_header: "../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---

# Description

This form provides for the monthly reporting of size-frequency estimates for IOTC species, as well as common sharks and other bycatch species caught in association with IOTC fisheries. The form allows reporting data for multiple fisheries and species simultaneously.

Click [here](./Form-4SF.xlsx) to download a blank version of Form 4SF, or [return](./index.html) to the list of all IOTC statistical data reporting forms.

# Data Content

Numbers of fish sampled and raised by size category and species, along with information on the value (%) and type of sampling coverage used for the estimations by month, year, fleet, fishery, and geographical grid.

# Stratification

## General Information

| Element | Requirement | Description | Format | Example value  |
| :--------| :----: | :----------------------- | :-------- | :------------ |
| Reporting year | M | Gregorian calendar year of the fishing activities reported through the dataset | 4-digit integer | `1996` |
| Reporting entity | M | Three-letter (alpha-3) code of the entity reporting the dataset to the IOTC Secretariat | **Code** from [Entities](#entities) | `EUR` | 
| Flag state | M | Three-letter (alpha-3) code of the country registration of the fishery vessels | **Code** from [Countries](#countries) | `FRA` |
## Main Data Elements

| Element | Requirement | Description | Format | Example value |
| :--------| :----: | :----------------------- | :-------- | :------------ |
| Month | M | Month of fishing activities | Integer | `7` |
| Fishery | M | [IOTC fishery](../guidelines/#Fisheries) derived from the combination of several factors | **Code** from [Fisheries](#fisheries) | `PS-DF[IN]TR` | 
| Grid | M | Fishing area | **Code** from [Grid codes](#fishingArea) | `6100040` | 
| Species | M | Species caught and retained | **Code** from [Species](#allSpecies) | `YFT` | 
| Sex | O | Sex of the fish sampled | **Code** from [Sex](#sex) | `F` | 
| Type of fate | M | Fate of fish caught | **Code** from [Types of fate](#typesOfFate) | `RE` | 
| Fate | O | Reason for retention or discarding of the fish | **Code** from [Fate](#fates) | `FL`  |   

## Original Data

| Element | Requirement | Description | Format | Example value |
| :--------| :----: | :----------------------- | :-------- | :------------ |
| Estimation | M | Indicates whether the data were estimated | **Code** from [Estimations](#estimations) | | `AV` | 
| Original data type | M | Preliminary/final status of the data | **Code** from [Types of data](#datatypes) | `FI` |
| Original data source | M | Source of information | **Code** from [Size-frequency data sources](#sourcesSF) | `OB` | 
| Original data processing | M | Processing applied to the data | **Code** from [Size-frequency data processings](#processingsSF) | `TE` | 
| Data raising | M | Level of raising (i.e., extrapolation) | **Code** from [Raisings](#dataRaising) | `RT` |
| Source coverage type | O | Variable used for data coverage | **Code** from [Types of coverage](#coverageTypes) | `FW` |
|| Source coverage value | M | Value of coverage | Numeric with two decimal places | `0.23` |

## Measurements

| Element | Requirement | Description | Format |  Example value |
| :--------| :----: | :----------------------- | :-------- | :------------ |
| Type of Measurement | M | General type of size measurement | **Code** from [Types of measurement](#typesOfMeasurement) | `LN` | 
| Measurement | M | Nature of the size measurement | **Code** from [Measurements](#Measurement) | `FL` | 
| Measurement tool | O | Tool used to take the measurement | **Code** from [Measurement tools](#allMeasurementTools) | `CA` | 

## Sample Data

| Element | Requirement | Description | Format | Example value |
| :--------| :----: | :----------------------- | :-------- | :------------ |
| Size class (_low_) | M | The lower value of the bin size | Integer | `121`  | 
| Size class (_high_) | M | The higher vaue recorded of the bin size | Integer | `122`  | 
| Number of samples | M | Actual number of fish measured in the stratum | Integer | `182` | 
| Number of fish | M | Raised number of fish in the stratum | Numeric | `2563` | 

# Reporting Metadata

| Element | Requirement | Description | Format | Example value |
| :--------| :----: | :----------------------- | :-------- | :------------ |
| Liaison officer full name | M  | Name of the liaison officer in charge of the compilation of the data | Plain text | `John Doe` |
| Liaison officer email	 | M | Email address of the liaison officer in charge of the compilation of the data | Valid email address | `John.Doe@fao.org`|
| Organisation name | M | Name of the organisation in charge of the compilation of the data | Plain text | `National Institute of Fisheries` |
| Organisation email | O | Email address of the organisation in charge of the compilation of the data | `nif@gov.sc` |
| Finalisation date | M | Date of finalisation of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | `1996-03-27` |
| Submission date | M | Date of submission of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | `1997-03-21` |

# Reporting Deadlines

+ **Longline fisheries**: 30 June (preliminary), 30 December (final)
+ **Surface fisheries**: 30 June (final)
+ **Coastal fisheries**: 30 June (final)

# Reference Code Lists

## Entities {#entities}

+ [Permalink](https://data.iotc.org/reference/latest/domain/admin/index.html#entities)
+ **Version:** `r version_number("ENTITIES")`
+ **Last update**: `r last_update("ENTITIES")`

```{r collapse = TRUE}
out_dt(ENTITIES, "ENTITIES")
```

## Countries {#countries}

+ [Permalink](https://data.iotc.org/reference/latest/domain/admin/index.html#countries)
+ **Version:** `r version_number("COUNTRIES")`
+ **Last update**: `r last_update("COUNTRIES")`

```{r collapse = TRUE}
out_dt(COUNTRIES, "COUNTRIES")
```

## IOTC 5° grids {#5x5Grids}

+ [Permalink](https://data.iotc.org/reference/latest/domain/admin/index.html#IOTCgrids5x5)
+ **Version:** `r version_number("IOTC_GRIDS_05x05")`
+ **Last update**: `r last_update("IOTC_GRIDS_05x05")`

```{r collapse = TRUE}
out_dt(IOTC_GRIDS_05x05, "AREAS_IOTC_05")
```

## Fisheries {#fisheries}

+ [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/index.html#fisheries)
+ **Version:** `r version_number("FISHERIES")`
+ **Last update**: `r last_update("FISHERIES")`

```{r collapse = TRUE}
out_dt(FISHERIES, "FISHERIES")
```

## Types of Measurement {#typesOfMeasurement}

+ [Permalink](https://data.iotc.org/reference/latest/domain/biology/index.html#typesOfMeasurement)
+ **Version:** `r version_number("TYPES_OF_MEASUREMENT")`
+ **Last update**: `r last_update("TYPES_OF_MEASUREMENT")`

```{r collapse = TRUE}
out_dt(TYPES_OF_MEASUREMENT, "TYPES_OF_MEASUREMENT")
```

## Measurements {#Measurements}

+ [Permalink](https://data.iotc.org/reference/latest/domain/biology/index.html#allMeasurements)
+ **Version:** `r version_number("MEASUREMENTS")`
+ **Last update**: `r last_update("MEASUREMENTS")`

```{r collapse = TRUE}
out_dt(MEASUREMENTS, "MEASUREMENTS")
```

## Measurement tools {#allMeasurementTools}

+ [Permalink](https://data.iotc.org/reference/latest/domain/biology/index.html#allMeasurementTools)
+ **Version:** `r version_number("MEASUREMENT_TOOLS")`
+ **Last update**: `r last_update("MEASUREMENT_TOOLS")`

```{r collapse = TRUE}
out_dt(MEASUREMENT_TOOLS, "MEASUREMENT_TOOLS")
```

## Types of Fate {#typesOfFate}

+ [Permalink](https://data.iotc.org/reference/latest/domain/biology/index.html#typesOfFate)
+ **Version:** `r version_number("TYPES_OF_FATE")`
+ **Last update**: `r last_update("TYPES_OF_FATE")`

```{r collapse = TRUE}
out_dt(TYPES_OF_FATE, "TYPES_OF_FATE")
```

## Fates {#fates}

+ [Permalink](https://data.iotc.org/reference/latest/domain/biology/index.html#fates)
+ **Version:** `r version_number("FATES")`
+ **Last update**: `r last_update("FATES")`

```{r collapse = TRUE}
out_dt(FATES, "FATES")
```

## Sexes {#sex}

+ [Permalink](https://data.iotc.org/reference/latest/domain/biology/index.html#sex)
+ **Version:** `r version_number("SEX")`
+ **Last update**: `r last_update("SEX")`

```{r collapse = TRUE}
out_dt(SEX, "SEX")
```

## Species {#allSpecies}

+ [Permalink](https://data.iotc.org/reference/latest/domain/biology/index.html#allSpecies)
+ **Version:** `r version_number("SPECIES")`
+ **Last update**: `r last_update("SPECIES")`

```{r collapse = TRUE}
out_dt(SPECIES, "SPECIES") %>% formatStyle(columns = "NAME_SCIENTIFIC", fontStyle = "italic")
```

## Types of Data {#datatypes}

+ [Permalink](https://data.iotc.org/reference/latest/domain/data/index.html#types)
+ **Version:** `r version_number("DATA_TYPES")`
+ **Last update**: `r last_update("DATA_TYPES")`

```{r collapse = TRUE}
out_dt(DATA_TYPES, "DATA_TYPES")
```

## Data Raising {#dataRaising}

+ [Permalink](https://data.iotc.org/reference/latest/domain/data/index.html#raisings)
+ **Version:** `r version_number("DATA_RAISINGS")`
+ **Last update**: `r last_update("DATA_RAISINGS")`

```{r collapse = TRUE}
out_dt(DATA_RAISINGS, "DATA_RAISINGS")
```

## Size-Frequency Data Sources {#sourcesSF}

+ [Permalink](https://data.iotc.org/reference/latest/domain/data/index.html#sourcesSF)
+ **Version:** `r version_number("DATA_SOURCES_SF")`
+ **Last update**: `r last_update("DATA_SOURCES_SF")`

```{r collapse = TRUE}
out_dt(DATA_SOURCES_SF, "DATA_SOURCES_SF")
```

## Size-Frequency Data Processings {#processingsSF}

+ [Permalink](https://data.iotc.org/reference/latest/domain/data/index.html#processingsSF)
+ **Version:** `r version_number("DATA_PROCESSINGS_SF")`
+ **Last update**: `r last_update("DATA_PROCESSINGS_SF")`

```{r collapse = TRUE}
out_dt(DATA_PROCESSINGS_SF, "DATA_PROCESSINGS_SF")
```

## Types of Coverage {#coverageTypes}

+ [Permalink](https://data.iotc.org/reference/latest/domain/data/index.html#coverageTypes)
+ **Version:** `r version_number("COVERAGE_TYPES")`
+ **Last update**: `r last_update("COVERAGE_TYPES")`

```{r collapse = TRUE}
out_dt(COVERAGE_TYPES, "COVERAGE_TYPES")
```

## Estimations {#estimations}

+ [Permalink](https://data.iotc.org/reference/latest/domain/data/index.html#estimations)
+ **Version:** `r version_number("DATA_ESTIMATIONS")`
+ **Last update**: `r last_update("DATA_ESTIMATIONS")`

```{r collapse = TRUE}
out_dt(DATA_ESTIMATIONS, "DATA_ESTIMATIONS")
```