---
title: "IOTC Statistical Data Reporting: Form 3BU (v`r DOI_VERSION`)"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  word_document2:
    reference_docx: "../templates/doc_template.docx"
    number_sections: FALSE
    reference_num: TRUE
    fig_caption: TRUE
      
  html_document2:
    css: "../templates/html_template.css"
    includes: 
      in_header: "../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---

# Description

This form provides for the monthly reporting of daily positions for each of the buoys monitored in purse seine fisheries. Each buoy is identified by its unique identifier which is a concatenation of the acronym of the buoy commercial model (e.g., ISD+, M3+, T8E) followed by 5-9 digits depending on the buoy model.

Click [here](./Form-3BU.xlsx) to download a blank version of Form 3BU, or [return](./index.html) to the list of all IOTC statistical data reporting forms.

# Data content

Single positions (latitude and longitude in decimal degrees) by buoy and day for each purse seine vessel.

# Stratification

## General information

| Element | Requirement | Description | Format | Input value  |
| :-------- | :-----: | :----------------------- | :-------------:|:-------------:|
| Reporting year | M | Gregorian calendar year of the fishing activities reported through the dataset | 4-digit integer | e.g., `1996` |
| Reporting month | M | Month of the fishing activities reported through the dataset | Integer (1--12) | e.g., `3` | 
| Reporting entity | M | Three-letter (alpha-3) code of the entity reporting the dataset to the IOTC Secretariat | **Code** from [Entities](#entities) | e.g., `EUR` | 
| Flag state | M | Three-letter (alpha-3) code of the country registration of the fishery vessels | **Code** from [Countries](#countries) | e.g., `ESP` |
| Vessel name | M | Name of purse seine vessel monitoring the buoy as available from the IOTC Record of Authorised Vessel [RAV](https://rav.iotc.org/) | String | e.g., `DRENNEC` | 
| Vessel IOTC number | M | IOTC registered number of the purse seine vessel monitoring the buoy | String | e.g., `IOTC018542` |

## Data specifications

| Element | Requirement | Description | Format | Input value |
| :-------- | :-----: | :------------------- | :-----------: | :-------: |
| Original data type | M | Preliminary/final status of the data | **Code** from [Types of data](#types) | e.g., `FI` | 

## Main data elements

| Element | Requirement | Description | Format | Input value |
| :-------- | :-----: | :----------------------- | :-------: | :-------: |
| Day of month | M | Day of the month of the fishing activities reported through the dataset | Integer (1--31) | e.g., `23` | 
| Buoy ID | M | Unique identifier of buoy monitored generally composed of the concatenation of the buoy model with with 5-9 digits | String | e.g., `SLX328501` |  
| Latitude | M | The latitude of the buoy location, expressed in decimal degrees according to the WGS 84 reference system (EPSG:4326). Recommended precision: four decimal places (~10 m) | [ISO 6709](https://en.wikipedia.org/wiki/ISO_6709) [+/-DD.DDDD] | e.g., `-20.8854` |
| Longitude | M | The longitude of the buoy location, expressed in decimal degrees according to the WGS 84 reference system (EPSG:4326). Recommended precision: four decimal places (~10 m) | [ISO 6709](https://en.wikipedia.org/wiki/ISO_6709) [+/-DDD.DDDD] | e.g., `55.5312` |

# Reporting metadata

| Element | Requirement | Description | Format | Input value |
| :-------- | :----: | :----------------------- | :-------- | :------------ |
| Liaison officer full name | M  | Name of the liaison officer in charge of the compilation of the data | String | e.g., `John Doe` |
| Liaison officer email	| M | Email address of the liaison officer in charge of the compilation of the data | Valid email address | e.g., `John.Doe@fao.org` |
| Organisation name | M | Name of the organisation in charge of the compilation of the data | String | e.g., `Institute of Fisheries` |
| Organisation email | O | Email address of the organisation in charge of the compilation of the data | Valid email address | e.g., `nif@gov.sc` |
| Finalisation date | M | Date of finalisation of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | e.g., `1996-03-27` |
| Submission date | O | Date of submission of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | e.g., `1997-03-21` |

# Reporting deadlines

- **Surface fisheries**: To be submitted with a 30–60 day delay (Para. 23 of Res. [24/02](https://www.iotc.org/cmm/resolution-2402-management-drifting-fish-aggregating-devices-fads-iotc-area-competence))
or a 60-90 delay (Para. 24 of Res. [19/02](https://iotc.org/cmm/resolution-1902-procedures-fish-aggregating-devices-fads-management-plan), which remains binding on Oman)

# Reference code lists

## Entities {#entities}

```{r collapse = TRUE}
out_dt(ENTITIES, "ENTITIES")
```

## Countries {#countries}

```{r collapse = TRUE}
out_dt(COUNTRIES, "COUNTRIES")
```

## Types of data {#types}

```{r collapse = TRUE}
out_dt(DATA_TYPES, "DATA_TYPES")
```
