---
title: "IOTC statistical data reporting: Form 3BU (v`r BASE_VERSION`)"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  word_document2:
    reference_docx: "../templates/doc_template.docx"
    number_sections: FALSE
    reference_num: TRUE
    fig_caption: TRUE
      
  html_document2:
    css: "../templates/html_template.css"
    includes: 
      in_header: "../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---

# Description

This form provides for the monthly reporting of daily positions for each of the buoys monitored in purse seine fisheries. Each buoy is identified by its unique identifier which is a concatenation of the acronym of the buoy commercial model (e.g., ISD+, M3+, T8E) followed by 5-9 digits depending on the buoy model.

Click [here](../forms/Form-3BU.xlsx) to download a blank version of Form 3-BU, or [return](../forms) to the list of all IOTC statistical data reporting forms.

# Data content

Single positions (latitude and longitude in decimal degrees) by buoy and day for each purse seine vessel.

# Stratification

## General information

| Element | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Reporting year | M | Gregorian calendar year of the fishing activities reported through the dataset | Integer |
| Reporting month | M | Month of the fishing activities reported through the dataset | Integer 1..12 |
| Reporting entity | M | Code of the entity reporting the dataset to the IOTC Secretariat | **Code** from [Entities](#entities) |
| Flag state | M | Code of the country registration of the fishery vessels | **Code** from [Countries](#countries) |
| Vessel name | M | Name of purse seine vessel monitoring the buoy | Plain text |
| Vessel IOTC number | M | IOTC registered number of the purse seine vessel monitoring the buoy | Plain text (e.g., IOTC018542) |

## Data specifications

| Element | Requirement | Description | Code list  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Original data type | M | Preliminary/final status of the data | **Code** from [Types of data](#types) |

## Main data elements

| Element | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Day of month | M | Day of the month of the fishing activities reported through the dataset | Integer 1..31 |
| Buoy ID  | M | Unique identifier of buoy monitored| (e.g., ISD+, M3+, T8E) followed by 5-9 digits |
| Latitude | M | Horizontal distances north or south of the Equator | Decimal degrees  |
| Longitude | M | Vertical distances east or west of the prime meridian | Decimal degrees |

# Reporting metadata

| Element | Requirement | Description | Format | Example |
| :--------| :----: | :----------------------- | :-------- | :------------ |
| Liaison officer full name | M  | Name of the liaison officer in charge of the compilation of the data | Plain text | John Doe |
| Liaison officer email	| M | Email address of the liaison officer in charge of the compilation of the data | Valid email address | [John.Doe\@fao.org](mailto:John.Doe@fao.org){.email} |
| Organisation name | M | Name of the organisation in charge of the compilation of the data | Plain text | National Institute of Fisheries |
| Organisation email | O | Email address of the organisation in charge of the compilation of the data | [nif\@gov.sc](mailto:nif@gov.sc){.email} |
| Finalisation date | M | Date of finalisation of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1996-03-27 |
| Submission date | O | Date of submission of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1997-03-21 |

# Reporting deadlines

- **Surface fisheries**: To be submitted with a time delay of at least 60 days, but no longer than 90 days

# Reference code lists

## Entities {#entities}

```{r collapse = TRUE}
out_dt(ENTITIES, "ENTITIES")
```

## Countries {#countries}

```{r collapse = TRUE}
out_dt(COUNTRIES, "COUNTRIES")
```

## Types of data {#types}

```{r collapse = TRUE}
out_dt(DATA_TYPES, "DATA_TYPES")
```
