---
title: "IOTC statistical data reporting: Form 1DR (v`r BASE_VERSION`)"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  word_document2:
    reference_docx: "../templates/doc_template.docx"
    number_sections: FALSE
    reference_num: TRUE
    fig_caption: TRUE

  html_document2:
    css: "../templates/html_template.css"
    includes: 
      in_header: "../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---
  
# Description
  
This form supports the reporting of the matrix of presence of species in the retained catches and discards of each fishing fleet by gear group and broad fishery category. For each species/gear combination, the cell must be filled with either a value of one (1) in case of positive catch or a value of zero (0) in case of absence of catch (i.e., no landing and no discard). Species include IOTC species, mobulid rays, common sharks, and other bycatch species. All gear groups (hooks and lines, pole-and-lines, longlines, purse seines, gillnets, and other gears) are included and further broken down by broad fishery category, i.e., [coastal](#iotccoastalfishery) and [industrial](#iotcindustrialfishery).

Click [here](../forms/Form-1DR.xlsx) to download a blank version of Form 1DR, or [return](../forms) to the list of all IOTC statistical data reporting forms.

# Data content

Indicate presence *(one (1) for positive or zero (0) for absence)* of species in the retained catches and discards, by year, fleet, fishery, and fishery categories.

## General information

| Element | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| [Reporting year]{#repyear} | M | Gregorian calendar year of the fishing activities reported through the dataset | Integer |
| [Reporting entity]{#repentity} | M | Code of the entity reporting the dataset to the IOTC Secretariat | **Code** from [entities](#Entities) |
| [Flag state]{#repflagstate} | M | Code of the country registration of the fishery vessels | **Code** from [countries](#Countries) |

## Main data elements

| Element | Description | Codelist |
| :----------- | :-------------------------- | :-------: |
| Species | Species include IOTC species, mobulid rays, common sharks, and other bycatch species, expected to be present by respective fisheries and gear groups | [Species](#species) |
| Gear groups | Gear groups catching IOTC species and other species of interest | [Gear groups](#gearGroups) |
| Fishery categories | Fishery categories by each gear group | [Fishery categories](#fisheryCategories)|

# Reporting metadata

| Element        | Requirement | Description | Format | Example |
| :----------- | :----: | :----------------------- | :-------- | :------------ |
| [Focal point full name]{#fcname} | M | Name of the focal point in charge of the reporting of the data to the IOTC Secretariat | Plain text | John Doe  |
| [Focal point email]{#fcemail} | M | Email address of the focal point in charge of the reporting of the data to the IOTC Secretariat | Valid email address | John.Doe@fao.org |
| [Organisation name]{#orgname} | M | Name of the organisation in charge of the reporting of the data to the IOTC Secretariat | Plain text | National Institute of Fisheries |
| [Organisation email]{#orgemail} | O | Email address of the organisation in charge of the reporting of the data to the IOTC Secretariat | Valid email address | nif@gov.sc |
| [Finalisation date]{#findate} | M | Date of finalisation of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1996-03-27 |
| [Submission date]{#subdate} | M | Date of submission of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1997-03-21 |


# Reporting deadlines

- **All fisheries**: 30 June (final)

# Reference codelists

## Entities {#entities}

Reference codes modelling the entity submitting the dataset to the IOTC Secretariat.

```{r collapse = TRUE}
out_dt(ENTITIES, "ENTITIES")
```

## Countries {#countries}

Reference codes modelling the flag / reporting country submitting the dataset to the IOTC Secretariat.

```{r collapse = TRUE}
out_dt(COUNTRIES, "COUNTRIES")
```

## Gear groups {#gearGroups}

Reference codes modelling the gear groups used to catch the fish species.

```{r collapse = TRUE}
out_dt(GEAR_GROUPS, "GEAR_GROUPS")
```

## Species {#species}

Reference codes modelling the species caught with the gear groups.

```{r collapse = TRUE}
out_dt(SPECIES, "SPECIES")
```

## Fishery categories {#fisheryCategories}

Reference of the fisheries categories of the different gear groups used to catch the fish species.

```{r collapse = TRUE}
out_dt(FISHERY_CATEGORIES, "FISHERY_CATEGORIES")
```
