---
title: "IOTC statistical data reporting: Form 3BU (v`r BASE_VERSION`)"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  word_document2:
    reference_docx: "../templates/doc_template.docx"
    number_sections: FALSE
    reference_num: TRUE
    fig_caption: TRUE
      
  html_document2:
    css: "../templates/html_template.css"
    includes: 
      in_header: "../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---

# Description

This form supports the reporting of single daily buoy position (latitude and longitude in decimal degrees) for each of the buoys monitored by each purse seine vessel. Each buoy is identified by its unique identifier which is a concatenation of the acronym of the buoy commercial model (e.g., ISD+, M3+, T8E) followed by 5-9 digits depending on the buoy model.

Click [here](../forms/Form-3BU.xlsx) to download a blank version of Form 3-BU, or [return](../forms) to the list of all IOTC statistical data reporting forms.

# Reporting deadlines

- _Surface fisheries_: **To be submitted with a time delay of at least 60 days, but no longer than 90 days**

# Stratification

## Reporting metadata

### Submission information

| Element        | Requirement | Description | Format | Example |
| :--------| :----: | :----------------------- | :-------- | :------------ |
| [Focal point full name]{#fcname} | M | Name of the focal point in charge of the reporting of the data to the IOTC Secretariat | Plain text | John Doe  |
| [Focal point email]{#fcemail} | M | Email address of the focal point in charge of the reporting of the data to the IOTC Secretariat | Valid email address | John.Doe@fao.org |
| [Organisation name]{#orgname} | M | Name of the organisation in charge of the reporting of the data to the IOTC Secretariat | Plain text | National Institute of Fisheries |
| [Organisation email]{#orgemail} | O | Email address of the organisation in charge of the reporting of the data to the IOTC Secretariat | Valid email address | nif@gov.sc |
| [Finalisation date]{#findate} | M | Date of finalisation of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1996-03-27 |
| [Submission date]{#subdate} | M | Date of submission of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1997-03-21 |

### General information

| Element        | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| [Reporting year]{#repyear} | M | Gregorian calendar year of the fishing activities reported through the dataset | Integer |
| [Reporting month] | M | Month of the fishing activities reported through the dataset | Integer 1..12 |
| [Reporting entity]{#repentity} | M | Code of the entity reporting the dataset to the IOTC Secretariat | **Code** from [Entities](#entities) |
| [Flag state]{#repflagstate} | M | Code of the country registration of the fishery vessels | **Code** from [Countries](#countries) |
| Vessel name | M | Name of vessel monitoring the buoy  | Plain text  |
| Vessel IOTC number | M | IOTC registered number of the vessel monitoring the buoy  | Plain text (_IOTCxxxxxx_) |

### Data specifications

| Element        | Requirement | Description | Code list  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Original data type       | M | Preliminary/final status of the data | **Code** from [Types of data](#types)      |

## Data elements

### Main data elements

| Element        | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Day of Month | M | Day of the month of the fishing activities reported through the dataset | Integer 1..31 |
| Buoy ID   | M | Unique identifier of buoy monitored| (e.g., ISD+, M3+, T8E) followed by 5-9 digit |

### Buoy position

| Element        | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Latitude| M | Horizontal distances north or south of the Equator   | Decimal degrees  |
| Longitude | M | Vertical distances east or west of the prime meridian | Decimal degrees |

# Reference codelists

## Entities {#entities}

Reference codes modelling the entity submitting the dataset to the IOTC Secretariat.

```{r collapse = TRUE}
out_dt(ENTITIES, "ENTITIES")
```

## Countries {#countries}

Reference codes modelling the flag / reporting country submitting a dataset to the IOTC Secretariat.
                  
```{r collapse = TRUE}
out_dt(COUNTRIES, "COUNTRIES")
```

## Data types {#types}

Reference codes modelling the type of statistics provided through a specific form, and in particular if these are:

a. Preliminary if the statistics were estimated by using some information from the fishery and year concerned, and the data reported are likely to change in the future as more information become available; or

b. Final if the statistics were estimated by using the complete set of data from the fishery and year concerned, and the data reported are unlikely to change in the future.

```{r collapse = TRUE}
out_dt(DATA_TYPES, "DATA_TYPES")
```
