---
title: "IOTC statistical data reporting: Form 3CE (v`r BASE_VERSION`)"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  word_document2:
    reference_docx: "../templates/doc_template.docx"
    number_sections: FALSE
    reference_num: TRUE
    fig_caption: TRUE

  html_document2:
    css: "../templates/html_template.css"
    includes: 
      in_header: "../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---
  
# Description
  
This form supports the reporting of *Estimates of species-specific catches and efforts by fishing fleet, fishery, and space and time strata* for a given CPC / fleet.

# Resources

Click [here](https://data.iotc.org/reference/latest/forms/Form-3CE.xlsx) to download an empty version of form 3-CE, or [return back](..) to the list of all IOTC statistical data reporting forms.

# Supported resolutions

- Res. [15/01](https://www.iotc.org/cmm/resolution-1501-recording-catch-and-effort-data-fishing-vessels-iotc-area-competence) -- _On the recording of catch and effort data by fishing vessels in the IOTC area of competence_
- Res. [15/02](https://www.iotc.org/cmm/resolution-1502-mandatory-statistical-reporting-requirements-iotc-contracting-parties-and) -- _On mandatory statistical reporting requirements for IOTC Contracting Parties and Cooperating Non-Contracting Parties (CPCs)_
- Res. [18/05](https://www.iotc.org/cmm/resolution-1805-management-measures-conservation-billfishes-striped-marlin-black-marlin-blue) -- _On management measures for the conservation of the billfishes: striped marlin, black marlin, blue marlin and Indo-Pacific sailfish_
- Res. [17/05](https://www.iotc.org/cmm/resolution-1705-conservation-sharks-caught-association-fisheries-managed-iotc) -- _On the conservation of sharks caught in association with fisheries managed by IOTC_
- Res. [18/02](https://iotc.org/cmm/resolution-1802-management-measures-conservation-blue-shark-caught-association-iotc-fisheries) -- _On management measures for the conservation of blue shark caught in association with IOTC fisheries_
- Res. [12/09](https://iotc.org/cmm/resolution-1209-conservation-thresher-sharks-family-alopiidae-caught-association-fisheries-iotc) -- _On the conservation of thresher sharks (family Alopiidae) caught in association with fisheries in the IOTC agreement area_
- Res. [13/06](https://iotc.org/cmm/resolution-1306-scientific-and-management-framework-conservation-sharks-species-caught) -- _On a scientific and management framework on the conservation of sharks in association with IOTC managed fisheries_
- Res. [19/03](https://iotc.org/cmm/resolution-1903-conservation-mobulid-rays-caught-association-fisheries-iotc-area-competence) -- _On the conservation of mobulid species caught in association with fisheries in the IOTC area of competence_

# Reference species groups

-   **IOTC species** [ mandatory ]
-   **Sharks** [ mandatory ]
-   **Mobulids and rays** [ mandatory ]
-   **Other bycatch / non-IOTC species** [ voluntary ]

# Reporting deadlines

-   **Longline fisheries**: 30 June (preliminary), 30 December (final)
-   **Surface fisheries**: 30 June (final)
-   **Coastal fisheries**: 30 June (final)

# Stratification

## Main data fields

-   Monthly ( for industrial fisheries; yearly or monthly for coastal fisheries )
-   [IOTC area](#IOTCgridsCESF)
-   [Fishery](#fisheries)
-   [Species](#allSpecies)

## Additional Data fields

-   [EStimation](#estimations)
-   [Types of data](#types)
-   [Data sources](#sourcesCE)
-   [Data processings](#processingsCE)
-   [Raisings](#raisings)
-   [Types of Coverage](#coverageTypes)


# Referenced codelists

## Administrative and geospatial domains

### Countries (ADM.COU) {#countries}

Reference codes modeling the flag / reporting country submitting a dataset to the IOTC Secretariat.

```{r collapse = TRUE}
out_dt(COUNTRIES, "COUNTRIES")
```

### IOTC regular and irregular areas (GIS.IOTC.MA) {#IOTC_areas_(GISIOIAA)}

Reference the types grid:
-  (1° grid area)[#IOgrids1x1] for surface fisheries
-  (5° grid area)[#IOgrids5x5] or finer for the SC for longline fisheries
-  (irregular areas) [#IOTCareasAR] for coastal fisheries.

## Fisheries and fishing technologies domains

### Fisheries (FIS) {#fisheries}

An *ad-hoc* classification derived from a combination of several factors (purpose, area of operation, vessel size category, gear, gear configuration, fishing mode and target species) that uniquely describe fishing practices for groups of vessels.

An [*interactive wizard*](https://data.iotc.org/fisheries/wizard) to help CPCs identify the IOTC code for their fisheries (among those currently considered of relevance in the Indian Ocean).

```{r collapse = TRUE}
out_dt(FISHERIES, "FISHERIES")
```

## Biological and morphometrics domains

### All species (SPC.ALL) {#allSpecies}

Reference codes modeling the species interacting with the fisheries as:

-   target species (retained or discarded)
-   bycatch species (retained or discarded)
-   sampled individuals
-   etc.

These codelists are subsets of the entries in the [ASFIS](https://www.fao.org/fishery/en/collection/asfis/en) list of species for fishery statistics purposes, from which they inherit the alphabetic codes, English, French and scientific names, as well as the family and order, and add the species category (in the IOTC sense), the IUCN status (retrieved from the [IUCN red list](https://www.iucnredlist.org) of endangered species) and other characteristics of each entry such as their status of single species / species aggregate, bait species, SSI species, IOTC species.

```{r collapse = TRUE}
out_dt(SPECIES, "SPECIES")
```

### Reasons for retaining (SPC.FTE.RE) {#retainReasons}

Reference codes that model the reasons why aquatic creatures caught by the fishery are retained onboard.

```{r collapse = TRUE}
out_dt(RETAIN_REASONS, "RETAIN_REASONS")
```

## Data and metadata domains

### Data types (DTA.TY) {#types}

Reference codes modeling the type of statistics provided through a specific form, and in particular if these are:

a)    preliminary if the statistics were estimated by using some information from the fishery and year concerned, and the data reported are likely to change in the future as more information become available; or
b)    final if the statistics were estimated by using the complete set of data from the fishery and year concerned, and the data reported are unlikely to change in the future.

```{r collapse = TRUE}
out_dt(DATA_TYPES, "DATA_TYPES")
```

### Retained catches data sources (DTA.SRC.RC) {#dataSourcesRC}

Reference codes modeling the source of the data provided through the retained catches data form.

```{r collapse = TRUE}
out_dt(DATA_SOURCES_RC, "DATA_SOURCES_RC")
```

### Retained catches data processings (DTA.PRO.RC) {#dataProcessingsRC}

Reference codes modeling the processing applied to the data provided through the retained catches data form.

```{r collapse = TRUE}
out_dt(DATA_PROCESSINGS_RC, "DATA_PROCESSINGS_RC")
```

### Coverage types (DTA.COV.TY) {#coverageTypes}

Reference codes modeling the type of coverage for the raw information used to obtain the data provided through a specific form.

```{r collapse = TRUE}
out_dt(COVERAGE_TYPES, "COVERAGE_TYPES")
```

