---
title: "IOTC statistical data reporting: Form 2FC (v`r BASE_VERSION`)"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  word_document2:
    reference_docx: "../templates/doc_template.docx"
    number_sections: FALSE
    reference_num: TRUE
    fig_caption: TRUE

  html_document2:
    css: "../templates/html_template.css"
    includes: 
      in_header: "../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---

# Description

This form provides for the reporting of the total annual numbers of fishing vessels involved in operation by fishery, boat type, mechanisation type, onboard fish preservation type, and size class.

For each stratum, the data coverage -- i.e., the percentage (%) of vessels or fishing activities sampled -- derived from the coverage type must be reported to assess the representativeness and quality of the estimates.

Click [here](../latest/forms/Form-2FC.xlsx) to download a blank version of Form 1-RC, or [return](../forms) to the list of IOTC statistical data reporting forms.

# Data content

Number of fishing vessel by size category, along with information on the value (%) and type of sampling coverage used for the estimations by year, fleet, fishery, and vessel characteristics.

# Stratification

## General information

| Element | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Reporting year | M | Gregorian calendar year of the fishing activities reported through the dataset | Integer |
| Reporting entity | M | Code of the entity reporting the dataset to the IOTC Secretariat | **Code** from [Entities](#entities) |
| Flag state | M | Code of the country registration of the fishery vessels | **Code** from [Countries](#countries) |

## Main data elements

| Element | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Fisheries | M | Type of fishing practices based on several factors| **Code** from [Fisheries](#fisheries) |

## Original data

| Element        | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Original data type       | M | Preliminary/final status of the data | **Code** from [Types of data](#types) |
| Original data source     | M | Source of information | **Code** from [Fishing craft data sources](#sourcesFC) |
| Original data processing | M | Processing applied to the data | **Code** from [Fishing craft data processings](#dataProcessingsFC) |
| Source coverage type     | M | Variable used for data coverage | **Code** from [Types of coverage](#coverageTypes) |

## Vessel characteristics

| Element        | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Boat type | M | Fishing boat classification based on shape and purpose| **Code** from [Boat types](#boatTypes)      |
| Mechanisation type | M | Type of boat mechanization| **Code** from [Mechanisation types](#mechanizationTypes)          |
| Boat class types | M |  Vessel size categories  | **Code** from [Boat class types](#boatClassTypes) |
| Fish preservation method | M | Type of preservation methods being used for target species onboard boats | **Code** from [Fish preservation methods](#fishPreservationMethods) |
| Fish storage | M | Type of structures present on-board and used by the vessel to store the catch | **Code** from [Fish storage method](#fishStorageTypes) |

# Reporting metadata

| Element | Requirement | Description | Format | Example |
| :--------| :----: | :----------------------- | :-------- | :------------ |
| Liaison officer full name | M  | Name of the liaison officer in charge of the compilation of the data | Plain text | John Doe |
| Liaison officer email	 | M | Email address of the liaison officer in charge of the compilation of the data | Valid email address | [John.Doe\@fao.org](mailto:John.Doe@fao.org){.email} |
| Organisation name | M | Name of the organisation in charge of the compilation of the data | Plain text | National Institute of Fisheries |
| Organisation email | O | Email address of the organisation in charge of the compilation of the data | [nif\@gov.sc](mailto:nif@gov.sc){.email} |
| Finalisation date | M | Date of finalisation of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1996-03-27 |
| Submission date | O | Date of submission of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1997-03-21 |

# Reporting deadlines

+ **Longline fisheries**: 30 June (preliminary), 30 December (final)
+ **Surface fisheries**: 30 June (final)
+ **Coastal fisheries**: 30 June (final)

# Reference code lists

## Entities {#entities}

```{r collapse = TRUE}
out_dt(ENTITIES, "ENTITIES")
```

## Countries {#countries}

```{r collapse = TRUE}
out_dt(COUNTRIES, "COUNTRIES")
```

## IOTC main areas {#IOTCareasMain}

```{r collapse = TRUE}
out_dt(IOTC_MAIN_AREAS, "IOTC_MAIN_AREAS")
```

## Fisheries {#fisheries}

```{r collapse = TRUE}
out_dt(FISHERIES, "FISHERIES")
```

## Types of boats {#boatTypes}

```{r collapse = TRUE}
out_dt(BOAT_TYPES, "BOAT_TYPES")
```

## Types of mechanization {#mechanizationTypes}

```{r collapse = TRUE}
out_dt(MECHANIZATION_TYPES, "MECHANIZATION_TYPES")
```

## Methods of fish preservation {#fishPreservationMethods}

```{r collapse = TRUE}
out_dt(FISH_PRESERVATION_METHODS, "FISH_PRESERVATION_METHODS")
```

## Types of fish storage {#fishStorageTypes}

```{r collapse = TRUE}
out_dt(FISH_STORAGE_TYPES, "FISH_STORAGE_TYPES")
```

## Types of boat class {#boatClassTypes}

```{r collapse = TRUE}
out_dt(BOAT_CLASS_TYPES, "BOAT_CLASS_TYPES")
```

## Types of data {#types}

```{r collapse = TRUE}
out_dt(DATA_TYPES, "DATA_TYPES")
```

## Fishing crafts data sources {#sourcesFC}

```{r collapse = TRUE}
out_dt(DATA_SOURCES_FC, "DATA_SOURCES_FC")
```

## Fishing crafts data processings {#dataProcessingsFC}

```{r collapse = TRUE}
out_dt(DATA_PROCESSINGS_FC, "DATA_PROCESSINGS_FC")
```

## Types of coverage {#coverageTypes}

```{r collapse = TRUE}
out_dt(COVERAGE_TYPES, "COVERAGE_TYPES")
```