---
title: "IOTC statistical data reporting: Form 2FC (v`r BASE_VERSION`)"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  word_document2:
    reference_docx: "../templates/doc_template.docx"
    number_sections: FALSE
    reference_num: TRUE
    fig_caption: TRUE

  html_document2:
    css: "../templates/html_template.css"
    includes: 
      in_header: "../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---

# Description

This form supports the reporting of the total annual numbers of fishing vessels involved in operation by fishery, boat type, mechanisation type, onboard fish preservation type, and size class.

For each stratum, the data coverage -- i.e., the percentage (%) of vessels or fishing activities sampled -- derived from the coverage type must be reported to assess the representativeness and quality of the estimates.

Click [here](../latest/forms/Form-2FC.xlsx) to download an empty version of form 1-RC, or [return](../forms) to the list of all new versions of the IOTC statistical data reporting forms.

# Reporting deadlines

+ **Longline fisheries**: 30 June (preliminary), 30 December (final)
+ **Surface fisheries**: 30 June (final)
+ **Coastal fisheries**: 30 June (final)

# Stratification

## Reporting metadata

### Submission information

| Element        | Requirement | Description | Format | Example |
| :--------| :----: | :----------------------- | :-------- | :------------ |
| [Focal point full name]{#fcname} | M | Name of the focal point in charge of the reporting of the data to the IOTC Secretariat | Plain text | John Doe  |
| [Focal point email]{#fcemail} | M | Email address of the focal point in charge of the reporting of the data to the IOTC Secretariat | Valid email address | John.Doe@fao.org |
| [Organisation name]{#orgname} | M | Name of the organisation in charge of the reporting of the data to the IOTC Secretariat | Plain text | National Institute of Fisheries |
| [Organisation email]{#orgemail} | O | Email address of the organisation in charge of the reporting of the data to the IOTC Secretariat | Valid email address | nif@gov.sc |
| [Finalisation date]{#findate} | M | Date of finalisation of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1996-03-27 |
| [Submission date]{#subdate} | M | Date of submission of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1997-03-21 |

### General information

| Element | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| [Reporting year]{#repyear} | M | Gregorian calendar year of the fishing activities reported through the dataset | Integer |
| [Reporting entity]{#repentity} | M | Code of the entity reporting the dataset to the IOTC Secretariat | **Code** from [Entities](#entities) |
| [Flag state]{#repflagstate} | M | Code of the country registration of the fishery vessels | **Code** from [Countries](#countries) |

## Data elements

### Main data elements

| Element | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Fisheries | M | Type of fishing practices based on several factors| **Code** from [Fisheries](#fisheries) |

### Original data

| Element        | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Original data type       | M | Preliminary/final status of the data | **Code** from [Types of data](#types) |
| Original data source     | M | Source of information | **Code** from [Fishing craft data sources](#sourcesFC) |
| Original data processing | M | Processing applied to the data | **Code** from [Fishing craft data processings](#dataProcessingsFC) |
| Source coverage type     | M | Variable used for data coverage | **Code** from [Coverage types](#coverageTypes) |

### Vessel characteristics

| Element        | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Boat type | M | Fishing boat classification based on shape and purpose| **Code** from [Boat types](#boatTypes)      |
| Mechanisation type | M | Type of boat mechanization| **Code** from [Mechanisation types](#mechanizationTypes)          |
| Boat class types | M |  Vessel size categories  | **Code** from [Boat class types](#boatClassTypes) |
| Fish preservation method | M | Type of preservation methods being used for target species onboard boats | **Code** from [Fish preservation methods](#fishPreservationMethods) |
| Fish storage | M | Type of structures present on-board and used by the vessel to store the catch | **Code** from [Fish storage method](#fishStorageTypes) |

# Referenced codelists

## Entities {#entities}

Reference codes modelling the entity submitting the dataset to the IOTC Secretariat.

```{r collapse = TRUE}
out_dt(ENTITIES, "ENTITIES")
```

### Countries {#countries}

Reference codes modelling the flag / reporting country submitting a dataset to the IOTC Secretariat.

```{r collapse = TRUE}
out_dt(COUNTRIES, "COUNTRIES")
```

### IOTC main areas {#IOTCareasMain}

Reference codes modelling the two main areas in which the IOTC area of competence is split (western / eastern IOTC area, _roughly_ coinciding with FAO areas F51 and F57).

```{r collapse = TRUE}
out_dt(IOTC_MAIN_AREAS, "IOTC_MAIN_AREAS")
```

### Fisheries {#fisheries}

An *ad-hoc* classification derived from a combination of several factors (purpose, area of operation, vessel size category, gear, gear configuration, fishing mode, and target species) that uniquely describes fishing practices for groups of vessels.

An [*interactive wizard*](https://data.iotc.org/fisheries/wizard) to help CPCs identify the IOTC code for their fisheries (among those currently considered of relevance in the Indian Ocean).

```{r collapse = TRUE}
out_dt(FISHERIES, "FISHERIES")
```

### Boat types {#boatTypes}

This codelist includes several types of boat currently known to the IOTC: countries using types of boat other than those specified are encouraged to provide this information to the Secretariat.

```{r collapse = TRUE}
out_dt(BOAT_TYPES, "BOAT_TYPES")
```

### Mechanization types {#mechanizationTypes}

Reference codes modelling the type of boat mechanization known in the IOTC and for which fleet / effort statistics might be provided to the Secretariat.

```{r collapse = TRUE}
out_dt(MECHANIZATION_TYPES, "MECHANIZATION_TYPES")
```

### Fish preservation methods {#fishPreservationMethods}

Reference codes modelling the type of preservation methods being used for target species onboard boats of a given type, and for which fleet / effort statistics might be provided to the Secretariat.

```{r collapse = TRUE}
out_dt(FISH_PRESERVATION_METHODS, "FISH_PRESERVATION_METHODS")
```

### Fish storage types {#fishStorageTypes}

Reference codes modelling the type of processing applied to the retained fish.

```{r collapse = TRUE}
out_dt(FISH_STORAGE_TYPES, "FISH_STORAGE_TYPES")
```

### Boat class types {#boatClassTypes}

CPCs should make every possible effort to classify their fleets according to the categories recorded in this codelist and report this information to the Secretariat.

```{r collapse = TRUE}
out_dt(BOAT_CLASS_TYPES, "BOAT_CLASS_TYPES")
```

### Data types {#types}

Reference codes modelling the type of statistics provided through a specific form, and in particular if these are:

a. Preliminary if the statistics were estimated by using some information from the fishery and year concerned, and the data reported are likely to change in the future as more information become available; or

b. Final if the statistics were estimated by using the complete set of data from the fishery and year concerned, and the data reported are unlikely to change in the future.

```{r collapse = TRUE}
out_dt(DATA_TYPES, "DATA_TYPES")
```

### Fishing crafts data sources {#sourcesFC}

Reference codes modelling the source of the data provided through the fishing craft data form.

```{r collapse = TRUE}
out_dt(DATA_SOURCES_FC, "DATA_SOURCES_FC")
```

### Fishing crafts data processings {#dataProcessingsFC}

Reference codes modelling the processing applied to the data provided through the fishing craft form.

```{r collapse = TRUE}
out_dt(DATA_PROCESSINGS_FC, "DATA_PROCESSINGS_FC")
```

### Coverage types {#coverageTypes}

Reference codes modelling the type of coverage for the raw information used to obtain the data provided through a specific form.

```{r collapse = TRUE}
out_dt(COVERAGE_TYPES, "COVERAGE_TYPES")
```