---
title: "IOTC statistical data reporting: Form 3CE (v`r BASE_VERSION`)"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  word_document2:
    reference_docx: "../templates/doc_template.docx"
    number_sections: FALSE
    reference_num: TRUE
    fig_caption: TRUE

  html_document2:
    css: "../templates/html_template.css"
    includes: 
      in_header: "../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---
  
# Description
  
This form supports the reporting of *Estimates of species-specific catches and efforts by fishing fleet, fishery, and space and time strata* for a given CPC / fleet.

This form supports the reporting of estimates of geo-referenced of species-specific catches and efforts by fishing fleet, fishery, and space and time strata, _as update following revision of previously submitted catch and effort data_.
Estimates of efforts expressed in units consistent with the recording requirements established in Res. 15/01 and complemented by numbers of fishing operations for longline fisheries and surface fisheries (IOTC-2022-SC25-R). The use of trips as effort unit is not recommended as trip length may vary substantially according to vessel length, fishing success, and multiple technical factors (e.g., fuel exhaustion). In the case of purse seine fisheries, other units could be added to refine the information on effort such as searching time and surface area explored.



# Resources

Click [here](https://data.iotc.org/reference/latest/forms/Form-3CE.xlsx) to download an empty version of form 3-CE, or [return back](..) to the list of all IOTC statistical data reporting forms.

# Supported resolutions

- Res. [15/01](https://www.iotc.org/cmm/resolution-1501-recording-catch-and-effort-data-fishing-vessels-iotc-area-competence) -- _On the recording of catch and effort data by fishing vessels in the IOTC area of competence_
- Res. [15/02](https://www.iotc.org/cmm/resolution-1502-mandatory-statistical-reporting-requirements-iotc-contracting-parties-and) -- _On mandatory statistical reporting requirements for IOTC Contracting Parties and Cooperating Non-Contracting Parties (CPCs)_
- Res. [18/05](https://www.iotc.org/cmm/resolution-1805-management-measures-conservation-billfishes-striped-marlin-black-marlin-blue) -- _On management measures for the conservation of the billfishes: striped marlin, black marlin, blue marlin and Indo-Pacific sailfish_
- Res. [17/05](https://www.iotc.org/cmm/resolution-1705-conservation-sharks-caught-association-fisheries-managed-iotc) -- _On the conservation of sharks caught in association with fisheries managed by IOTC_
- Res. [18/02](https://iotc.org/cmm/resolution-1802-management-measures-conservation-blue-shark-caught-association-iotc-fisheries) -- _On management measures for the conservation of blue shark caught in association with IOTC fisheries_
- Res. [12/09](https://iotc.org/cmm/resolution-1209-conservation-thresher-sharks-family-alopiidae-caught-association-fisheries-iotc) -- _On the conservation of thresher sharks (family Alopiidae) caught in association with fisheries in the IOTC agreement area_
- Res. [13/06](https://iotc.org/cmm/resolution-1306-scientific-and-management-framework-conservation-sharks-species-caught) -- _On a scientific and management framework on the conservation of sharks in association with IOTC managed fisheries_
- Res. [19/03](https://iotc.org/cmm/resolution-1903-conservation-mobulid-rays-caught-association-fisheries-iotc-area-competence) -- _On the conservation of mobulid species caught in association with fisheries in the IOTC area of competence_

# Reporting deadlines

-   **Longline fisheries**: 30 June (preliminary), 30 December (final)
-   **Surface fisheries**: 30 June (final)
-   **Coastal fisheries**: 30 June (final)

# Stratification

## Reporting metadata

### Submission information

| Element        | Requirement | Description | Format | Example |
| :--------| :----: | :----------------------- | :-------- | :------------ |
| [Focal point full name]{#fcname} | M | Name of the focal point in charge of the reporting of the data to the IOTC Secretariat | Plain text | John Doe  |
| [Focal point email]{#fcemail} | M | Email address of the focal point in charge of the reporting of the data to the IOTC Secretariat | Valid email address | John.Doe@fao.org |
| [Organisation name]{#orgname} | M | Name of the organisation in charge of the reporting of the data to the IOTC Secretariat | Plain text | National Institute of Fisheries |
| [Organisation email]{#orgemail} | O | Email address of the organisation in charge of the reporting of the data to the IOTC Secretariat | Valid email address | nif@gov.sc |
| [Finalisation date]{#findate} | M | Date of finalisation of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1996-03-27 |
| [Submission date]{#subdate} | M | Date of submission of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1997-03-21 |


### General information

| Element        | Requirement | Description | Code list  |
| :----------------- | :-----: | :----------------------- | :-------: |
| [Reporting year]{#repyear} | M | Gregorian calendar year of the fishing activities reported through the dataset | Integer |
| [Reporting entity]{#repentity} | M | Code of the entity reporting the dataset to the IOTC Secretariat | [Entity](#countries) |
| [Flag state]{#repflagstate} | M | Code of the country registration of the fishery vessels | [Countries](#countries) |

## Data elements

### Main data elements

| Element        | Requirement | Description | Code list  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Month | M | The month of the fishing activities reported through the dataset | Integer |
| Fisheries   | M | Type of fishing practices based on several factors| [Fisheries](#fisheries)            |
|Grid| M | the seven digits grid square of the fishing area in Indian Ocean   | [Grid codes](#IOTCgridsCESF) |
| Species    | M | Species caught and discarded| [Species](#allSpecies)           |
| Type of fate    | M | Fate of fish caught (retained or discarded)| [Types of fate](#typesOfFate)           |
| Data raising             | M | Level of raising (i.e., extrapolation) | [Raisings](#raisings)| 
| Catch unit   | M | Units used to report the level of catches of a given species,|[Catch units](#catchUnits) |



### Original data

| Element        | Requirement | Description | Code list  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Estimation   | M | Indicate if the data was estimated or actual recorded data | [Estimations](#estimations)     |
| Original data type      | M | Preliminary/final status of the data | [Type of data](#types)      |
| Original data source     | M | Source of information | [Catch and effort data sources](#dataSourcesCE)          |
| Original data processing | M | Processing applied to the data    | [Catch and effort data processings](#dataProcessingsCE) |
| Data raising             | M | Level of raising (i.e., extrapolation) | [Raisings](#dataRaising)| 
| Source coverage type     | M | Variable used for data coverage | [Coverage types](#coverageTypes) |
|Source coverage value   | M | Value of coverage |in percentage |


### Effort units

| Element        | Requirement | Description | Code list  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Primary     | M | Primary effort unit | [Effort units](#effortUnits)     |
| Secondary    | O | Secondary effort unit (if any) | [Effort units](#effortUnits)     |
| Tertiary    | O | Tertiary effort unit (if any) | [Effort units](#effortUnits)     |





## Additional information

### The recommended effort units for each fishery:

| Gear group | Primary effort | Secondary effort | Tertiary effort 
| :------------ | :------------------------- | :------------------------- | :------------------------- |
Gillnets (GI)        | Number of fishing days   | Number of nets deployed | Total net surface deployed |
Hooks and lines (HL) | Number of fishing days   | Number of hooks deployed | - |
Longlines (LL)       | Number of hooks deployed | Number of sets | - |
Other gears (OT)     | Number of days at sea    | - | - |
Pole-and-lines (PL)  | Number of fishing days   | Number of sets | Number of day-poles |
Purse seines (PS)    | Number of fishing hours  | Number of sets | Number of successful/null sets |

### The spatial and temporal resolutions, catch units, and level of extrapolation vary according to the fishery category.

| Category | Temporal resolution | Spatial resolution | Catch unit | Extrapolation | 
| :-------- | :--------- | :---------- | :------------- | :-------: |
[Surface fisheries](#iotcsurfacefishery)  | Month | [1째 grid area](https://data.iotc.org/reference/1.0.0/domain/admin/#IOgrids1x1) | Live weight equivalent | M |
[Longline fisheries](#iotclonglinefishery) | Month or finer for the SC | [5째 grid area](https://data.iotc.org/reference/1.0.0/domain/admin/#IOgrids5x5) or finer for the SC | Numbers or live weight equivalent | M |
[Coastal fisheries](#iotccoastalfishery) | Year or finer | [Irregular areas](https://data.iotc.org/reference/latest/domain/admin/#IOTCareasAR) | Numbers or live weight equivalent | O |




# Referenced codelists

## Administrative and geospatial domains

### Countries (ADM.COU) {#countries}

Reference codes modeling the flag / reporting country submitting a dataset to the IOTC Secretariat.

```{r collapse = TRUE}
out_dt(COUNTRIES, "COUNTRIES")
```

### IOTC regular and irregular areas (GIS.IOTC.MA) {#IOTC_areas_(GISIOIAA)}

Reference the types grid:
-  (1째 grid area)[#IOgrids1x1] for surface fisheries
-  (5째 grid area)[#IOgrids5x5] or finer for the SC for longline fisheries
-  (irregular areas) [#IOTCareasAR] for coastal fisheries.

## Fisheries and fishing technologies domains

### Fisheries (FIS) {#fisheries}

An *ad-hoc* classification derived from a combination of several factors (purpose, area of operation, vessel size category, gear, gear configuration, fishing mode and target species) that uniquely describe fishing practices for groups of vessels.

An [*interactive wizard*](https://data.iotc.org/fisheries/wizard) to help CPCs identify the IOTC code for their fisheries (among those currently considered of relevance in the Indian Ocean).

```{r collapse = TRUE}
out_dt(FISHERIES, "FISHERIES")
```

## Biological and morphometrics domains

### All species (SPC.ALL) {#allSpecies}

Reference codes modeling the species interacting with the fisheries as:

-   target species (retained or discarded)
-   bycatch species (retained or discarded)
-   sampled individuals
-   etc.

These codelists are subsets of the entries in the [ASFIS](https://www.fao.org/fishery/en/collection/asfis/en) list of species for fishery statistics purposes, from which they inherit the alphabetic codes, English, French and scientific names, as well as the family and order, and add the species category (in the IOTC sense), the IUCN status (retrieved from the [IUCN red list](https://www.iucnredlist.org) of endangered species) and other characteristics of each entry such as their status of single species / species aggregate, bait species, SSI species, IOTC species.

```{r collapse = TRUE}
out_dt(SPECIES, "SPECIES")
```

### Reasons for retaining (SPC.FTE.RE) {#retainReasons}

Reference codes that model the reasons why aquatic creatures caught by the fishery are retained onboard.

```{r collapse = TRUE}
out_dt(RETAIN_REASONS, "RETAIN_REASONS")
```

## Data and metadata domains

### Data types (DTA.TY) {#types}

Reference codes modeling the type of statistics provided through a specific form, and in particular if these are:

a)    preliminary if the statistics were estimated by using some information from the fishery and year concerned, and the data reported are likely to change in the future as more information become available; or
b)    final if the statistics were estimated by using the complete set of data from the fishery and year concerned, and the data reported are unlikely to change in the future.

```{r collapse = TRUE}
out_dt(DATA_TYPES, "DATA_TYPES")
```

### Data raising (DTA.RA) {#dataRaising}

Reference codes modeling the level of raising applied to the data (raised to totals / not raised to totals / unknown).

```{r collapse = TRUE}
out_dt(DATA_RAISINGS, "DATA_RAISINGS")
```

### Retained catches data sources (DTA.SRC.CE) {#dataSourcesCE}

Reference codes modeling the source of the data provided through the retained catches data form.

```{r collapse = TRUE}
out_dt(DATA_SOURCES_CE, "DATA_SOURCES_CE")
```

### Retained catches data processings (DTA.PRO.CE) {#dataProcessingsCE}

Reference codes modeling the processing applied to the data provided through the retained catches data form.

```{r collapse = TRUE}
out_dt(DATA_PROCESSINGS_CE, "DATA_PROCESSINGS_CE")
```

### Coverage types (DTA.COV.TY) {#coverageTypes}

Reference codes modeling the type of coverage for the raw information used to obtain the data provided through a specific form.

```{r collapse = TRUE}
out_dt(COVERAGE_TYPES, "COVERAGE_TYPES")
```

### Estimations (DTA.ES) {#estimations}

Reference codes indicating if the data estimated for a stratum was actually recorded in the stratum or derived from comparable strata through a substitution scheme.

```{r collapse = TRUE}
out_dt(DATA_ESTIMATIONS, "DATA_ESTIMATIONS")
```

### Effort units (FIA.EU) {#effortUnits}

Reference codes that model the units used to report the level of effort, further stratified by the specific criteria characterizing each reporting form.

```{r collapse = TRUE}
out_dt(EFFORT_UNITS, "EFFORT_UNITSS")
```