---
title: "IOTC Statistical Data Reporting: Form 5MB (v`r DOI_VERSION`)"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  html_document2:
    css: "../templates/fao_template_simplified.css"
    mathjax: null
    includes: 
      in_header: "../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---

# Description

This form provides for the reporting of morphometric measurements and biological sample information for any species caught in association with IOTC fisheries.

Click [here](./Form-5MB.xlsx) to download a blank version of Form 5MB, or [return](./index.html) to the list of all IOTC statistical data reporting forms.

# Metadata

## Submission Information

| Element | Requirement | Description | Format | Input value |
| :--------| :----: | :----------------------- | :-------- | :------------ |
| Liaison officer full name | M | Name of the liaison officer in charge of the compilation of the data | String | e.g., `John Doe` |
| Liaison officer email	| M | Email address of the liaison officer in charge of the compilation of the data | Valid email address | e.g., `John.Doe@fao.org` |
| Organisation name | M | Name of the organisation in charge of the compilation of the data | String | e.g., `Institute of Fisheries` |
| Organisation email | O | Email address of the organisation in charge of the compilation of the data | Valid email address | e.g., `nif@gov.sc` |
| Finalisation date | M | Date of finalisation of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | e.g., `1996-03-27` |
| Submission date | M | Date of submission of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | e.g., `1997-03-21` |

## General Information

| Element | Description | Format | Input value |
|:------- |:-----------------------|:-------------:|:-------------:|
| Reporting year | Gregorian calendar year of the fishing activities reported through the dataset | 4-digit integer	 | e.g., `1996` | 
| Reporting entity | Three-letter (alpha-3) code of the entity reporting the dataset to the IOTC Secretariat | **Code** from [Entities](#entities) | e.g., `EUR` | 
| Flag state | Three-letter (alpha-3) code of the country registration of the fishing vessels | **Code** from [Countries](#countries) | e.g., `EUR.FRA` |

# Morphometric Data

| Element | Description | Format | Input value |
|:------- |:-----------------------|:-------------:|:-------------:|
| SpecimenID | The unique identifier for the sampled fish specimen | String | e.g., `IFRFRI000142` |
| Date start | The earliest date on which the fish could have been caught (start of the sampling period) | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) [YYYY-MM-DD] | e.g., `2025-01-01` |
| Date end | The latest date on which the fish could have been caught (end of the sampling period) | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) [YYYY-MM-DD] | e.g., `2025-01-03` | 
| Area | The area of origin of the sampled fish specimen | **Code** from [Areas](#areas) | e.g., `6100050` |
| Gear group | The group of fishing gears that caught the sampled fish specimen | **Code** from [Gear groups](#gearGroups) | e.g., `PL` |
| Species | The species of the sampled specimen | **Code** from [Species](#allSpecies) | e.g., `FRI` |
| Sex | The sex of the sampled fish specimen | **Code** from [Sex](#sexes) | e.g., `F` |
| Status | The preservation or processing condition of the sampled fish | **Code** from [Fish status](#fishStatus) | e.g., `DEF` |
| Maturity | The reproductive stage of the fish determined by visual inspection of the gonads without a microscope | **Code** from [Maturity Stages](#maturityStages) | e.g., `DEV` |
| Measurement | The type of morphometric measurement taken | **Code** from [Measurements](#measurements) | e.g., `FL` | 
| Measurement tool | The tool used to take the morphometric measurement | **Code** from [Measurement tools](#allMeasurementTools) | e.g., `CA` | 
| Value | The morphometric measurement expressed in the appropriate standard unit, i.e., centimetres (cm) for lengths and kilogrammes (kg) for weights | Numeric with one decimal place | e.g., `35.5` |

# Sample Data

| Element | Description | Format | Input value |
|:------- |:-----------------------|:-------------:|:-------------:|
| SampleID | Unique identifier for the sample | String | e.g., `LIV0018` | 
| Materials | The type of biological materials collected | **Code** from [Biological Materials](#biologicalMaterials) | e.g., `LI` | 
| Protocol  | The reference to the sampling protocol used | String (free entry text) | e.g., [protocols.io](https://www.protocols.io/view/c-elegans-worm-size-measurement-e6nvwke4wvmk/v1) | 
| Preservation | The type of preservation of the sample | **Code** from [preservation type](#samplePreservationMethods) | e.g., `FR80` |
| Location | The location of the sample | String (free entry text) | e.g., `Ifremer Freezer in room A5` | 

# Reference Code Lists

## Entities {#entities}

+ [Permalink](https://data.iotc.org/reference/latest/domain/admin/#entities)
+ **Version:** `r version_number("ENTITIES")`
+ **Last update**: `r last_update("ENTITIES")`

```{r collapse = TRUE}
out_dt(ENTITIES, "ENTITIES")
```

## Countries {#countries}

+ [Permalink](https://data.iotc.org/reference/latest/domain/admin/#countries)
+ **Version:** `r version_number("COUNTRIES")`
+ **Last update**: `r last_update("COUNTRIES")`

```{r collapse = TRUE}
out_dt(COUNTRIES, "COUNTRIES")
```

## Areas {#areas}

+ [Permalink](https://data.iotc.org/reference/latest/domain/admin/#IOTCgridsCESFAR)
+ **Version:** `r version_number("IOTC_GRIDS_CE_SF_AR")`
+ **Last update**: `r last_update("IOTC_GRIDS_CE_SF_AR")`

```{r collapse = TRUE, warning = FALSE}
out_dt(IOTC_GRIDS_CE_SF_AR, "IOTC_GRIDS_CE_SF_AR")
```

## Gear Groups {#gearGroups}

+ [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#gearGroups)
+ **Version:** `r version_number("GEAR_GROUPS")`
+ **Last update**: `r last_update("GEAR_GROUPS")`

```{r collapse = TRUE}
out_dt(GEAR_GROUPS, "GEAR_GROUPS")
```

## Species {#allSpecies}

+ [Permalink](https://data.iotc.org/reference/latest/domain/biology/#allSpecies)
+ **Version:** `r version_number("SPECIES")`
+ **Last update**: `r last_update("SPECIES")`

```{r collapse = TRUE}
out_dt(SPECIES, "SPECIES") %>% formatStyle(columns = "NAME_SCIENTIFIC", fontStyle = "italic")
```

## Sexes {#sexes}

+ [Permalink](https://data.iotc.org/reference/latest/domain/biology/#sex)
+ **Version:** `r version_number("SEX")`
+ **Last update**: `r last_update("SEX")`

```{r collapse = TRUE}
out_dt(SEX, "SEX")
```

## Fish Status {#fishStatus}

+ [Permalink](https://data.iotc.org/reference/latest/domain/biology/#maturityStages)
+ **Version:** `r version_number("MATURITY_STAGES")`
+ **Last update**: `r last_update("MATURITY_STAGES")`

```{r collapse = TRUE}
out_dt(FISH_STATUS, "MATURITY_STAGES")
```

## Maturity Stages {#maturityStages}

+ [Permalink](https://data.iotc.org/reference/latest/domain/biology/#maturityStages)
+ **Version:** `r version_number("MATURITY_STAGES")`
+ **Last update**: `r last_update("MATURITY_STAGES")`

```{r collapse = TRUE}
out_dt(MATURITY_STAGES, "MATURITY_STAGES")
```

## Measurements {#measurements}

+ [Permalink](https://data.iotc.org/reference/latest/domain/biology/#lengthMeasurements)
+ **Version:** `r version_number("MEASUREMENTS")`
+ **Last update**: `r last_update("MEASUREMENTS")`

```{r collapse = TRUE}
out_dt(MEASUREMENTS, "MEASUREMENTS")
```

## Measurement Tools {#measurementTools}

+ [Permalink](https://data.iotc.org/reference/latest/domain/biology/#MeasurementTools)
+ **Version:** `r version_number("LENGTH_MEASUREMENT_TOOLS")`
+ **Last update**: `r last_update("LENGTH_MEASUREMENT_TOOLS")`

```{r collapse = TRUE}
out_dt(MEASUREMENT_TOOLS, "MEASUREMENT_TOOLS")
```

## Biological Materials {#biologicalMaterials}

+ [Permalink](https://data.iotc.org/reference/latest/domain/biology/#biologicalMaterials)
+ **Version:** `r version_number("BIOLOGICAL_MATERIALS")`
+ **Last update**: `r last_update("BIOLOGICAL_MATERIALS")`

```{r collapse = TRUE}
out_dt(BIOLOGICAL_MATERIALS, "BIOLOGICAL_MATERIALS")
```

## Sample preservation Methods {#samplePreservationMethods}

+ [Permalink](https://data.iotc.org/reference/latest/domain/biology/#samplePreservationMethods)
+ **Version:** `r version_number("SAMPLE_PRESERVATION_METHODS")`
+ **Last update**: `r last_update("SAMPLE_PRESERVATION_METHODS")`

```{r collapse = TRUE}
out_dt(SAMPLE_PRESERVATION_METHODS, "SAMPLE_PRESERVATION_METHODS")
```
