---
title: "IOTC statistical data reporting: Form 3CE (v`r BASE_VERSION`-update)"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  word_document2:
    reference_docx: "../templates/doc_template.docx"
    number_sections: FALSE
    reference_num: TRUE
    fig_caption: TRUE

  html_document2:
    css: "../templates/html_template.css"
    includes: 
      in_header: "../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---
  
# Description

This form provides for the reporting of estimates of geo-referenced species-specific catches and efforts by fishing fleet, fishery, and space and time strata.

Click [here](../forms/Form-3CE-update.xlsx) to download a blank version of Form 3-CE-update, or [return](../forms) to the list of all IOTC statistical data reporting forms. The form allows reporting updated data for a single fishery. Click [here](../forms/Form-3CE.xlsx) to download a blank version of Form 3-CE which has been designed to report data for multiple fisheries simultaneously.

# Data content

Total number and/or live weight of retained catches by species and effort by stratum, along with information on the value (%) and type of sampling coverage used for the estimations by month, year, fleet, fishery, raising status, and fishing area.

# Stratification

## General information

| Element | Requirement | Description | Input value |
| :------------- | :-----: | :----------------------- | :------------: |
| Reporting year | M | Gregorian calendar year of the fishing activities | Integer |
| Reporting entity | M | Code of the entity reporting the dataset to the IOTC Secretariat | **Code** from [Entities](#entities) |
| Flag state | M | Code of the country registration of the fishery vessels | **Code** from [Countries](#countries) |
| Fisheries | M | Type of fishing practices based on several factors | **Code** from [Fisheries](#fisheries)            |

## Main data elements

| Element | Requirement | Description |Input value  |
| :------------- | :-----: | :----------------------- | :-----------: |
| Month | M | Month of fishing activities | Integer 1..12 |
| Grid  | M | Fishing area | **Code** from [Grid codes](#fishingArea) |
| Species | M | Species caught and discarded | **Code** from [Species](#allSpecies) |

## Data specifications

| Element | Requirement | Description | Input value  |
| :------------- | :-----: | :----------------------- | :------------: |
| Original data type | M | Preliminary/final status of the data | **Code** from [Types of data](#types)      |
| Original data source | M | Source of information | **Code** from [Catch and effort data sources](#sourcesCE)          |
| Original data processing | M | Processing applied to the data | **Code** from  [Catch and effort data processings](#dataProcessingsCE) |
| Data raising  | M | Level of raising (i.e., extrapolation) | **Code** from [Raisings](#dataRaising)| 
| Source coverage type | M | Variable used for data coverage | **Code** from [Types of coverage](#coverageTypes) |
|Source coverage value | M | Value of coverage |in percentage |
| Catch unit | M | Units used to report the level of catches of a given species | **Code** from [Catch units](#catchUnits) |

## Effort units

| Element | Requirement | Description |Input value  |
| :------------- | :-----: | :----------------------- | :-----------: |
| Primary | M | Primary effort unit | **Code** from  [Effort units](#effortUnits)     |
| Secondary | O | Secondary effort unit (if any) | **Code** from [Effort units](#effortUnits)     |
| Tertiary | O | Tertiary effort unit (if any) | **Code** from [Effort units](#effortUnits)     |

## Original data

| Element | Requirement | Description | Input value  |
| :------------- | :-----: | :----------------------- | :-----------: |
| Estimation | M | Indicates whether the data were estimated or actual recorded data | **Code** from [Estimations](#estimations) |

# Reporting metadata

| Element | Requirement | Description | Format | Example |
| :--------| :----: | :----------------------- | :-------- | :------------ |
| Liaison officer full name | M  | Name of the liaison officer in charge of the compilation of the data | Plain text | John Doe |
| Liaison officer email	 | M | Email address of the liaison officer in charge of the compilation of the data | Valid email address | [John.Doe\@fao.org](mailto:John.Doe@fao.org){.email} |
| Organisation name | M | Name of the organisation in charge of the compilation of the data | Plain text | National Institute of Fisheries |
| Organisation email | O | Email address of the organisation in charge of the compilation of the data | [nif\@gov.sc](mailto:nif@gov.sc){.email} |
| Finalisation date | M | Date of finalisation of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1996-03-27 |
| Submission date | M | Date of submission of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1997-03-21 |

# Reporting deadlines

+ **Longline fisheries**: 30 June (preliminary), 30 December (final)
+ **Surface fisheries**: 30 June (final)
+ **Coastal fisheries**: 30 June (final)

# Additional information

### Effort units recommended by fishery

Effort units must be consistent with the recording requirements established in Res. [15/01](https://www.iotc.org/cmm/resolution-1501-recording-catch-and-effort-data-fishing-vessels-iotc-area-competence) complemented by numbers of fishing operations for [longline fisheries](#iotclonglinefishery) and [surface fisheries](#iotcsurfacefishery) ([IOTC-2022-SC25-R](https://iotc.org/documents/SC/25/RE)). For coastal fisheries, it is recommended that effort data be submitted in the same units as those prescribed for longline fisheries and surface fisheries characterised by the same fishing gear. 

| Gear group | Primary effort | Secondary effort | 
| :------------ | :-------------------- | :------------------- |
Gillnets (GI)        | Number of fishing days   | Number of fishing operations |
Hooks and lines (HL) | Number of fishing days   | Number of fishing operations |
Longlines (LL)       | Number of hooks deployed | Number of fishing operations |
Other gears (OT)     | Number of days at sea    | Number of active gears/fishing operations |
Pole-and-lines (PL)  | Number of fishing days   | Number of fishing operations |
Purse seines (PS)    | Number of fishing hours  | Number of fishing operations |

From a general perspective, using trips as a unit of effort is not recommended because trip duration can vary widely due to factors such as vessel size, fishing success, and technical considerations (e.g., fuel availability).

Additional units may be considered to refine and standardise the estimation of nominal fishing effort:

i. In gillnet fisheries, the surface area of the nets deployed may better reflect effort intensity by accounting for differences in net length and height;

ii. In hooks and line fisheries, the number of hooks may be used as required for longline fisheries;

iii. In pole-and-line fisheries, the number of day-poles used may help account for differences in the number of fishers onboard the vessels;

iv. In purse seine fisheries, the numbers of successful and null fishing operations, searching time, and surface area explored may complement the information provided by fishing time and the total number of fishing sets. 

### Other dimensions

The spatial and temporal resolutions, catch units, and level of extrapolation vary according to the fishery category.

| Category | Temporal resolution | Spatial resolution | Catch unit | Extrapolation | 
| :-------- | :--------- | :---------- | :------------- | :-------: |
[Surface fisheries](#iotcsurfacefishery)  | Month | [1° grid area](https://data.iotc.org/reference/1.0.0/domain/admin/#IOgrids1x1) | Live weight equivalent | M |
[Longline fisheries](#iotclonglinefishery) | Month or finer for the SC | [5° grid area](https://data.iotc.org/reference/1.0.0/domain/admin/#IOgrids5x5) or finer for the SC | Numbers or live weight equivalent | M |
[Coastal fisheries](#iotccoastalfishery) | Year or finer | [Irregular areas](https://data.iotc.org/reference/latest/domain/admin/#IOTCareasAR) | Numbers or live weight equivalent | O |

# Reference code lists

## Entities {#entities}

```{r collapse = TRUE}
out_dt(ENTITIES, "ENTITIES")
```

## Countries {#countries}

```{r collapse = TRUE}
out_dt(COUNTRIES, "COUNTRIES")
```

## Fisheries {#fisheries}

```{r collapse = TRUE}
out_dt(FISHERIES, "FISHERIES")
```

## Fishing area {#fishingArea}

```{r collapse = TRUE}
out_dt(IOTC_GRIDS_CE_SF, "")
```

## Species {#allSpecies}

```{r collapse = TRUE}
out_dt(SPECIES, "SPECIES") %>% formatStyle(columns = "NAME_SCIENTIFIC", fontStyle = "italic")
```

## Types of data {#types}

```{r collapse = TRUE}
out_dt(DATA_TYPES, "DATA_TYPES")
```

## Data raisings {#dataRaising}

```{r collapse = TRUE}
out_dt(DATA_RAISINGS, "DATA_RAISINGS")
```

## Catches and effort data sources {#sourcesCE}

```{r collapse = TRUE}
out_dt(DATA_SOURCES_CE, "DATA_SOURCES_CE")
```

## Catches and effort data processings (DTA.PRO.DI) {#dataProcessingsCE}

```{r collapse = TRUE}
out_dt(DATA_PROCESSINGS_CE, "DATA_PROCESSINGS_CE")
```

## Types of coverage {#coverageTypes}

```{r collapse = TRUE}
out_dt(COVERAGE_TYPES, "COVERAGE_TYPES")
```

## Catch units {#catchUnits}

```{r collapse = TRUE}
out_dt(CATCH_UNITS, "CATCH_UNITS")
```

## Estimations {#estimations}

```{r collapse = TRUE}
out_dt(DATA_ESTIMATIONS, "DATA_ESTIMATIONS")
```

## Effort units {#effortUnits}

```{r collapse = TRUE}
out_dt(EFFORT_UNITS, "EFFORT_UNITS")
```