---
title: "IOTC statistical data reporting: Form 7PR (v`r BASE_VERSION`)"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  word_document2:
    reference_docx: "../templates/doc_template.docx"
    number_sections: FALSE
    reference_num: TRUE
    fig_caption: TRUE

  html_document2:
    css: "../templates/html_template.css"
    includes: 
      in_header: "../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---
  
# Description
  
This form supports the *voluntary* reporting of _monthly time series of price of fish products for tuna and tuna-like species_ caught in the Indian Ocean.

Click [here](../forms/legacy/Form-7PR-legacy.xlsm) to download an empty version of the legacy form 7-PR, or [return](../forms) to the list of all new versions of the IOTC statistical data reporting forms. 

<!-- The new reporting form 7-PR is under construction and should become available soon. The information below pertains to the new form. -->

# Reporting deadlines

- **Longline fisheries**: 30 June (preliminary), 30 December (final)
- **Surface fisheries**: 30 June (final)
- **Coastal fisheries**: 30 June (final)

# Stratification

## Reporting metadata

### Submission information

| Element        | Requirement | Description | Format | Example |
| :--------| :----: | :----------------------- | :-------- | :------------ |
| [Focal point full name]{#fcname} | M | Name of the focal point in charge of the reporting of the data to the IOTC Secretariat | Plain text | John Doe  |
| [Focal point email]{#fcemail} | M | Email address of the focal point in charge of the reporting of the data to the IOTC Secretariat | Valid email address | John.Doe@fao.org |
| [Organisation name]{#orgname} | M | Name of the organisation in charge of the reporting of the data to the IOTC Secretariat | Plain text | National Institute of Fisheries |
| [Organisation email]{#orgemail} | O | Email address of the organisation in charge of the reporting of the data to the IOTC Secretariat | Valid email address | nif@gov.sc |
| [Finalisation date]{#findate} | M | Date of finalisation of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1996-03-27 |
| [Submission date]{#subdate} | M | Date of submission of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1997-03-21 |

### General information

| Element        | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| [Reporting year]{#repyear} | M | Gregorian calendar year of the fishing activities reported through the dataset | Integer |
| [Reporting entity]{#repentity} | M | Entity reporting the dataset to the IOTC Secretariat | **Code** from [Entity](#entities) |
| [Flag state]{#repflagstate} | M | Country registration of the fishing vessels | **Code** from [Countries](#countries) |

## Data elements

### Main data elements

| Element | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Month | M | Gregorian calendar month of the fish sale | **1**: Jan; **2**: Feb, ... **12**: Dec |
| Currency | M | Price currency | **Code** from [Currencies](#currencies) |
| Processing | M | Processing type applied to species | **Code** from [Fish processing types](#fishProcessingType) |
| Product type | M | Type of fish product | **Code** from [Product types](#fishProductTypes) |
| Preservation type  | M | Type of preservation method | **Code** from [Fish preservation methods](#FishPreservationMethod) |
| Species | M | Fish species | **Code** from [Species](#IOTCSpecies) |
| Weight unit  | M | Unit of fish weight | **Code** from [Weight units](#weightUnits) |
| Weight class(lo) | M | Lowest weight class | Numeric value |
| Weight class(hi) | M | Highest weight class | Numeric value |

# Reference codelists

## Entities {#entities}

Reference codes modelling the entity submitting the dataset to the IOTC Secretariat.

```{r collapse = TRUE}
out_dt(ENTITIES, "ENTITIES")
```

## Countries {#countries}

Reference codes modelling the flag / reporting country submitting a dataset to the IOTC Secretariat.

```{r collapse = TRUE}
out_dt(COUNTRIES, "COUNTRIES")
```

## Catch units {#weightUnits}

Units of fish weight.

```{r collapse = TRUE}
out_dt(CATCH_UNITS, "CATCH_UNITS")
```

## IOTC species {#IOTCSpecies}

List of IOTC species.

```{r collapse = TRUE}
out_dt(SPECIES[IS_IOTC == TRUE & IS_AGGREGATE == FALSE], "SPECIES")
```

## Fish processing types {#fishProcessingType}

Types of processing applied to the fish prior to sale.

```{r collapse = TRUE}
out_dt(FISH_PROCESSING_TYPES, "FISH_PROCESSING_TYPES")
```

## Fish preservation method {#fishPreservationMethod}

Main method used to preserve the fish between its capture and sale.

```{r collapse = TRUE}
out_dt(FISH_PRESERVATION_METHODS, "FISH_PRESERVATION_METHODS")
```
