---
title: "IOTC Statistical Data Reporting: Form 1DR (v`r DOI_VERSION`)"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  html_document2:
    css: "../templates/fao_template_simplified.css"
    mathjax: null
    includes: 
      in_header: "../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---
  
# Description
  
This form provides for the reporting of the matrix of presence of species in the retained catches and discards of each fishing fleet by gear group and broad fishery category. Species include IOTC species, mobulid rays, common sharks, and other bycatch species caught in association with IOTC fisheries. All gear groups (hooks and lines, pole-and-lines, longlines, purse seines, gillnets, and other gears) are included and further broken down by broad fishery category.

Click [here](./Form-1DR.xlsx) to download a blank version of Form 1DR, or [return](./index.html) to the list of all IOTC statistical data reporting forms.

# Data Content

For the combination of each taxon, gear group, and fishery category listed in the form, the cell must be completed with a value of one (1) in the case of a positive catch, or zero (0) if no catch occurred -- that is, there were neither landings nor discards.

## General Information

| Element | Requirement | Description | Format | Input value  |
| :-------- | :-----: | :----------------------- | :----- | :-------: |
| Reporting year | M | Gregorian calendar year of the fishing activities reported through the dataset | 4-digit integer | e.g. `1996` |
| Reporting entity | M | Three-letter (alpha-3) code of the entity reporting the dataset to the IOTC Secretariat | **Code** from [Entities](#entities) | e.g., `EUR` | 
| Flag state | M | Three-letter (alpha-3) code of the country registration of the fishing vessels | **Code** from [Countries](#countries) | e.g., `FRA` |

## Main Data Elements

| Element | Description | Format | Input value |
| :-------- | :-------------------------- | :----- | :-------: |
| Species | Fish species caught, whether retained or discarded | **Code** from [Species](#1DRspecies) | e.g., `YFT` |
| Gear groups | Classification of different types of fishing gear that share similar characteristics or functions | **Code** from [Gear groups](#gearGroups) | e.g., `PL` | 
| Fishery categories | One of the three main IOTC fishery categories defined according to the main gear used by the vessel and their recording in the IOTC Record of Authorised Vessels | **Code** from [Fishery categories](#fisheryCategories) | e.g., `COASTAL` | 

# Reporting Metadata

| Element | Requirement | Description | Format | Input value |
| :-------- | :----: | :----------------------- | :------- | :------------ |
| Liaison officer full name | M  | Name of the liaison officer in charge of the compilation of the data | String | e.g., `John Doe` |
| Liaison officer email | M | Email address of the liaison officer in charge of the compilation of the data | Valid email address | e.g., `John.Doe@fao.org` |
| Organisation name | M | Name of the organisation in charge of the compilation of the data | String | e.g., `Institute of Fisheries` |
| Organisation email | O | Email address of the organisation in charge of the compilation of the data | Valid email address | e.g., `nif@gov.sc` |
| Finalisation date | M | Date of finalisation of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | e.g., `1996-03-27` |
| Submission date | O | Date of submission of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | e.g., `1997-03-21` |

# Reporting Deadlines

- **All fisheries**: 30 June (final)

# Reference Code Lists

## Entities {#entities}

+ [Permalink](https://data.iotc.org/reference/latest/domain/admin/#entities)
+ **Version**: `r version_number("ENTITIES")`
+ **Last update**: `r last_update("ENTITIES")`

```{r collapse = TRUE}
out_dt(ENTITIES, "ENTITIES")
```

## Countries {#countries}

+ [Permalink](https://data.iotc.org/reference/latest/domain/admin/#countries)
+ **Version**: `r version_number("COUNTRIES")`
+ **Last update**: `r last_update("COUNTRIES")`

```{r collapse = TRUE}
out_dt(COUNTRIES, "COUNTRIES")
```

## Gear Groups {#gearGroups}

+ [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#gearGroups)
+ **Version**: `r version_number("GEAR_GROUPS")`
+ **Last update**: `r last_update("GEAR_GROUPS")`

```{r collapse = TRUE}
out_dt(GEAR_GROUPS, "GEAR_GROUPS")
```

## Species {#1DRspecies}

+ [Permalink](https://data.iotc.org/reference/latest/domain/biology/#allSpecies)
+ **Version**: `r version_number("SPECIES")`
+ **Last update**: `r last_update("SPECIES")`

```{r collapse = TRUE}
out_dt(SPECIES_1DR, "SPECIES") %>% formatStyle(columns = "NAME_SCIENTIFIC", fontStyle = "italic")
```

## Fishery Categories {#fisheryCategories}

+ [Permalink](https://data.iotc.org/reference/latest/domain/fisheries/#fisheryCategories)
+ **Version**: `r version_number("FISHERY_CATEGORIES")`
+ **Last update**: `r last_update("FISHERY_CATEGORIES")`

```{r collapse = TRUE}
out_dt(FISHERY_CATEGORIES, "FISHERY_CATEGORIES")
```
