---
title: "IOTC statistical data reporting: form 1-CE (v`r BASE_VERSION`)"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  word_document2:
    reference_docx: "../templates/doc_template.docx"
    number_sections: FALSE
    reference_num: TRUE
    fig_caption: TRUE

  html_document2:
    css: "../templates/html_template.css"
    includes: 
      in_header: "../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---

# Description

The term fishery fleet or fishery vessel refers to mobile floating platforms of any kind and size, operating in fresh, brackish or marine waters which are used for catching, harvesting, searching, transporting, landing, preserving and/or processing fish, where the term fishing vessel is used instead when the vessel is engaged only in catching operations [CWP](The measure of effort (unit of fishing effort). IOTC classification of fishery vessels by fishery types relate to [FAO ISSCFV code](https://www.fao.org/3/cb5201en/cb5201en.pdf). 
                                                                                                                                                                                                                                                                                                                                                                            
CPCs can use the IOTC [Fisheries Identification wizard](https://iotc.org/data/fisheries/wizard) as guide to define their type of fisheries


This form supports the reporting of _number of operated fishing vessels_ for a given CPC / fleet, *on a voluntary* basis.

# Resources

Fishing craft statistics data should be reported through the form [2-FC](https://data.iotc.org/reference/latest/forms/Form-2FC.xlsx)


[return back](..) to the list of all IOTC statistical data reporting forms.

# Supported resolutions

+ [FSA-Annex I, Article 4]() - _Mandatory statistical reporting requirements for IOTC Contracting Parties and Cooperating Non-contracting Parties (CPCs)_


# Reference species groups

+ **IOTC species** [ mandatory ] 
+ **Sharks** [ mandatory ]
+ **Mobulids and rays** [ mandatory ]
+ **Other bycatch / non-IOTC species** [ voluntary ]

# Reporting deadlines

+ **Longline fisheries**: 30 June (preliminary), 30 December (final)
+ **Surface fisheries**: 30 June (final)
+ **Coastal fisheries**: 30 June (final)

# Stratification

## Main data fields
+ [IOTC area](#IOTCareasMain)
  + [Gear](#Gear)
    + [boat type](#boatTypes)
      + [Mechanisation type](#mechanizationTypes)
        + [Fish preservation method](#fishPreservationMethods)
          + [Fish processing type](#fishProcessingTypes)
            + [Fish processing type](#boatClassTypes)
              + Size class
              + Vessel number
              
              
              ## Additional data fields
              
              # Referenced codelists
              
              ## Administrative and geospatial domains
              
              ### Countries (ADM.COU) {#countries}
              
              Reference codes modeling the flag / reporting country submitting a dataset to the IOTC Secretariat.
              
              ```{r collapse = TRUE}
              out_dt(COUNTRIES, "COUNTRIES")
              ```
              
              ### IOTC main areas (GIS.IOTC.MA) {#IOTCareasMain}
              
              Reference codes modeling the two main areas in which the IOTC area of competence is split (western / eastern IOTC area, _roughly_ coinciding with FAO areas F51 and F57).
              
              ```{r collapse = TRUE}
              out_dt(IOTC_MAIN_AREAS, "IOTC_MAIN_AREAS")
              ```
              
              ## Fisheries and fishing technologies domains
              
              ### Gears (FIS.GE) {#gears}
              
              An _ad-hoc_ classification derived from a combination of several factors (purpose, area of operation, vessel size category, gear, gear configuration, fishing mode and target species) that uniquely describe fishing practices for groups of vessels.
              
              An [_interactive wizard_](https://data.iotc.org/fisheries/wizard) to help CPCs identify the IOTC code for  their fisheries (among those currently considered of relevance in the Indian Ocean).
              
              ```{r collapse = TRUE}
              out_dt(FISHERIES, "FISHERIES")
              ```
              
              ### Boat types (VES.BT) {#boatTypes}
              
              This codelist includes several types of boat currently known to the IOTC: countries using types of boat other than those specified are encouraged to provide this information to the Secretariat.
              
              ```{r collapse = TRUE}
              out_dt(BOAT_TYPES, "BOAT_TYPES")
              ```
              
              ### Mechanization types (VES.MT) {#mechanizationTypes}
              
              Reference codes modeling the type of boat mechanization known in the IOTC and for which fleet / effort statistics might be provided to the Secretariat.
              
              ```{r collapse = TRUE}
              out_dt(MECHANIZATION_TYPES, "MECHANIZATION_TYPES")
              ```
              
              ### Fish preservation methods (VES.PM) {#fishPreservationMethods}
              
              Reference codes modeling the type of preservation methods being used for target species onboard boats of a given type, and for which fleet / effort statistics might be provided to the Secretariat.
              
              ```{r collapse = TRUE}
              out_dt(FISH_PRESERVATION_METHODS, "FISH_PRESERVATION_METHODS")
              ```
              
              ### Fish processing types (VES.PR) {#fishProcessingTypes}
              
              Reference codes modeling the type of processing applied to the retained fish.
              
              ```{r collapse = TRUE}
              out_dt(FISH_PROCESSING_TYPES, "FISH_PROCESSING_TYPES")
              ```
              
              ### Boat class types (VES.BC) {#boatClassTypes}
              
              IOTC CPCs should make every possible effort to classify their fleets according to the categories recorded in this codelist and report this information to the Secretariat.
              
              ```{r collapse = TRUE}
              out_dt(BOAT_CLASS_TYPES, "BOAT_CLASS_TYPES")
              ```
              
              ## Data and metadata domains
              
              ### Data types (DTA.TY) {#dataTypes}
              
              Reference codes modeling the type of data provided through a specific form (preliminary / final / unknown).
              
              ```{r collapse = TRUE}
              out_dt(DATA_TYPES, "DATA_TYPES")
              ```
              
              ### Fishing crafts data sources (DTA.SRC.FC) {#sourcesFC}
              
              Reference codes modeling the source of the data provided through the fishing craft data form.
              
              ```{r collapse = TRUE}
              out_dt(DATA_SOURCES_FC, "DATA_SOURCES_FC")
              ```
              
              ### Fishing crafts data processings (DTA.PRO.FC) {#dataProcessingsFC}
              
              Reference codes modeling the processing applied to the data provided through the fishing craft form.
              
              ```{r collapse = TRUE}
              out_dt(DATA_PROCESSINGS_FC, "DATA_PROCESSINGS_FC")
              ```
              
              ### Coverage types (DTA.COV.TY) {#coverageTypes}
              
              Reference codes modeling the type of coverage for the raw information used to obtain the data provided through a specific form.
              
              ```{r collapse = TRUE}
              out_dt(COVERAGE_TYPES, "COVERAGE_TYPES")
              ```