---
title: "IOTC statistical data reporting: Form 4SF (v`r BASE_VERSION`-update)"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  word_document2:
    reference_docx: "../templates/doc_template.docx"
    number_sections: FALSE
    reference_num: TRUE
    fig_caption: TRUE
      
  html_document2:
    css: "../templates/html_template.css"
    includes: 
      in_header: "../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---

# Description

This form supports the reporting of annual estimates of sample size taken by number (or weight) measures of individual sizes of fish for the IOTC species, common sharks, and other bycatch species. Length frequency is defined as the number of individuals of a catch or catch sample in each length interval ([UN ESCWA](https://www.unescwa.org/sd-glossary/length-frequency-distribution-lfd)). The modal size is the length group with the higher number of individuals.

Straight length measurements made with a calliper or measuring board are recommended over fish weights and vary according to fish groups: (i) lower-jaw fork length for billfish, (ii) upper-jaw fork length for tunas, mackerels, sharks, and all other bycatch fish species with forked or lunate tails, (iii) standard length for bycatch fish species with rounded or truncate tails, and (iv) disc width for rays. The Secretariat further recommends the use of length intervals for the IOTC species and most commonly caught sharks along with maximum length intervals and ranges of valid values which are used to filter and consolidate the size-frequency datasets made available to support the IOTC process (see Recommended measurements).

Sampling coverage shall be set to at least one (1) fish measured by tonne caught by fishery and species, with samples being representative of all the periods and areas fished. For each stratum, the data coverage – i.e., the percentage (%) of catch/effort sampled – derived from the coverage type must be reported to assess the representativeness and quality of the estimates. In addition, raised estimates of the size samples must be reported to the Secretariat to account for bias due to unrepresentative sampling. Documents covering sampling and raising procedures must be provided for each fishery and species.

Click [here](../forms/Form-4SF-update.xlsx) to download a blank version of Form 4-SF-update, or [return](../forms) to the list of all IOTC statistical data reporting forms.

# Data content

Number (or weight) of fish sample and raised estimates by size category and species, along with information on the value (%) and type of sampling coverage used for the estimations by month, year, fleet, fishery and geographical grid.

# Stratification

## General information

| Element | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Reporting year | M | Gregorian calendar year of the fishing activities reported through the dataset | Integer |
| Reporting entity | M | Code of the entity reporting the dataset to the IOTC Secretariat | **Code** from [Entities](#entities) |
| Flag state | M | Code of the country registration of the fishery vessels | **Code** from [Countries](#countries) |
| Fisheries | M | Type of fishing practices based on several factors| **Code** from [Fisheries](#fisheries) |
| Species | M | Species caught and discarded | **Code** from [Species](#allSpecies) |

## Main data elements

| Element | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Month | M | The month of the fishing activities reported through the dataset | Integer |
| Grid | M | the seven digits grid square of the fishing area in Indian Ocean   | **Code** from [Grid codes](#geospatialData) |
| Sex | M | The sex of species sampled | **Code** from [Sex](#sex) |

## Sample data

| Element | Requirement | Description | Input value |
| :----------------- | :-----: | :----------------------- | :-------: |
| Size class (_low_)  | M | The lowest size recorded for the sample | Integer |
| Number of samples | M | The sample size of strata | Integer |
| Number of fish  | M | The number of fish measured | Integer |

## Data specifications

| Element | Requirement | Description | Code list |
| :----------------- | :-----: | :----------------------- | :-------: |
| Original data type | M | Preliminary/final status of the data | **Code** from [Type of data](#datatypes)      |
| Original data source | M | Source of information | **Code** from [Size frequency data sources](#sourcesSF)          |
| Original data processing | M | Processing applied to the data | **Code** from [Size frequency data processings](#processingsSF) |
| Data raising | M | Level of raising (i.e., extrapolation) | **Code** from [Raisings](#dataRaising)| 
| Source coverage type | M | Variable used for data coverage | **Code** from [Types of coverage](#coverageTypes) |
|Source coverage value | M | Value of coverage | Percentage (%) |
| Type of fate  | M | Fate of fish caught (retained or discarded)| **Code** from [Types of fate](#typesOfFate)           |
| Fate   | M | Reason for retained or discarded of the catch | **Code** from [Fate](#fates)  

## Measurements

| Element | Requirement | Description | Code list |
| :----------------- | :-----: | :----------------------- | :-------: |
| Type of Measurement | M | Given measurement types (weight or length) | **Code** from [Types of measurement](#typesOfMeasurement) |
| Measured type | M | Type of measure recorded | **Code** from [Measurements](#Measurement) |
| Measurement Tool | M | Tool used to take the measurement | **Code** from [Measurement tools](#allMeasurementTools) |
| Size interval | M | Size interval between lowest and highest measurements of the sampled species | Integer |

## Original data

| Element | Requirement | Description | Code list |
| :----------------- | :-----: | :----------------------- | :-------: |
| Estimation   | M | Indicate if the data was estimated or actual recorded data | **Code** from [Estimations](#estimations) |

# Reporting metadata

| Element | Requirement | Description | Format | Example |
| :--------| :----: | :----------------------- | :-------- | :------------ |
| Liaison officer full name | M  | Name of the liaison officer in charge of the compilation of the data | Plain text | John Doe |
| Liaison officer email	 | M | Email address of the liaison officer in charge of the compilation of the data | Valid email address | [John.Doe\@fao.org](mailto:John.Doe@fao.org){.email} |
| Organisation name | M | Name of the organisation in charge of the compilation of the data | Plain text | National Institute of Fisheries |
| Organisation email | O | Email address of the organisation in charge of the compilation of the data | [nif\@gov.sc](mailto:nif@gov.sc){.email} |
| Finalisation date | M | Date of finalisation of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1996-03-27 |
| Submission date | M | Date of submission of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1997-03-21 |

# Reporting deadlines

+ **Longline fisheries**: 30 June (preliminary), 30 December (final)
+ **Surface fisheries**: 30 June (final)
+ **Coastal fisheries**: 30 June (final)

# Additional information

### The spatial and temporal resolutions, and catch units

| Category | Temporal resolution | Spatial resolution | Catch unit |
| :-------- | :--------- | :---------- | :------------- |
All fisheries  | Month | [5° grid area](https://data.iotc.org/reference/1.0.0/domain/admin/#IOgrids5x5) or finer for the SC  | number of fish |

Paragraph 5 of resolution 15/02: Alternatively, size data for longline fleets may be provided as part of the Regional Observer Scheme where such fleets have at least 5% observer coverage of all fishing operations.

# Reference code lists

## Entities {#entities}

```{r collapse = TRUE}
out_dt(ENTITIES, "ENTITIES")
```

## Countries {#countries}

```{r collapse = TRUE}
out_dt(COUNTRIES, "COUNTRIES")
```

## IOTC regular grids {#geospatialData}

Codes for all 1°x1° and 5°x5° grids that overlap - at least partially - with the IOTC convention area.

Due to to the large size of the dataset, this is not included for filtering / browsing, but can be directly downloaded as a CSV from here: [IOTC_GRIDS_CE_SF](`r paste0("https://data.iotc.org/reference/latest/domain/admin/codelists/IOTC_GRIDS_CE_SF_", version_number("IOTC_GRIDS_CE_SF"), ".csv")`).

## Fisheries {#fisheries}

```{r collapse = TRUE}
out_dt(FISHERIES, "FISHERIES")
```

## Types of measurement {#typesOfMeasurement}

```{r collapse = TRUE}
out_dt(TYPES_OF_MEASUREMENT, "TYPES_OF_MEASUREMENT")
```

## Measurements {#Measurements}

```{r collapse = TRUE}
out_dt(MEASUREMENTS, "MEASUREMENTS")
```

## Measurement tools {#allMeasurementTools}

```{r collapse = TRUE}
out_dt(MEASUREMENT_TOOLS, "MEASUREMENT_TOOLS")
```

## Types of fate {#typesOfFate}

```{r collapse = TRUE}
out_dt(TYPES_OF_FATE, "TYPES_OF_FATE")
```

## Fates {#fates}

```{r collapse = TRUE}
out_dt(FATES, "FATES")
```

## Sexes {#sex}

```{r collapse = TRUE}
out_dt(SEX, "SEX")
```

## Species {#allSpecies}

```{r collapse = TRUE}
out_dt(SPECIES, "SPECIES") %>% formatStyle(columns = "NAME_SCIENTIFIC", fontStyle = "italic")
```

## Types of data {#datatypes}

```{r collapse = TRUE}
out_dt(DATA_TYPES, "DATA_TYPES")
```

## Data raising {#dataRaising}

```{r collapse = TRUE}
out_dt(DATA_RAISINGS, "DATA_RAISINGS")
```

## Size-frequency data sources {#sourcesSF}

```{r collapse = TRUE}
out_dt(DATA_SOURCES_SF, "DATA_SOURCES_SF")
```

## Size-frequency data processings {#processingsSF}

```{r collapse = TRUE}
out_dt(DATA_PROCESSINGS_SF, "DATA_PROCESSINGS_SF")
```

## Types of coverage types {#coverageTypes}

```{r collapse = TRUE}
out_dt(COVERAGE_TYPES, "COVERAGE_TYPES")
```

## Estimations {#estimations}

```{r collapse = TRUE}
out_dt(DATA_ESTIMATIONS, "DATA_ESTIMATIONS")
```