---
title: "IOTC statistical data reporting: form 3-BU (v`r BASE_VERSION`)"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  word_document2:
    reference_docx: "../templates/doc_template.docx"
    number_sections: FALSE
    reference_num: TRUE
    fig_caption: TRUE
      
  html_document2:
    css: "../templates/html_template.css"
    includes: 
      in_header: "../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---

# Description

This form supports the reporting of _daily buoys positions_ for a given CPC / fleet / vessel.

# Resources

[return back](..) to the list of all IOTC statistical data reporting forms.

# Supported resolutions

+ [15/02](https://iotc.org/cmm/resolution-1502-mandatory-statistical-reporting-requirements-iotc-contracting-parties-and) - _Mandatory statistical reporting requirements for IOTC Contracting Parties and Cooperating Non-contracting Parties (CPCs)_
+ [19/02](https://iotc.org/cmm/resolution-1902-procedures-fish-aggregating-devices-fads-management-plan) - _Procedures on a Fish Aggregating Devices (FADs) Management Plan_

# Reporting deadlines

+ **Surface fisheries**: 

# Stratification

## Main data fields

+ Daily(mandatory)
+ Bouy ID
+ [IOTC  geospatial area](#geospatialData)

## Additional data fields

+ [Estimation](#estimationTypes)

# Referenced codelists

## Administrative and geospatial domains
                  
### Countries (ADM.COU) {#countries}

Reference codes modeling the flag / reporting country submitting a dataset to the IOTC Secretariat.
                  
```{r collapse = TRUE}
out_dt(COUNTRIES, "COUNTRIES")
```

## Data and metadata domains

### Data types (DTA.TY) {#dataTypes}

Reference codes modeling the type of data provided through a specific form (preliminary / final / unknown).

```{r collapse = TRUE}
out_dt(DATA_TYPES, "DATA_TYPES")
```

### Data raising (DTA.RA) {#dataRaising}

Reference codes modeling the level of raising applied to the data (raised to totals / not raised to totals / unknown).

```{r collapse = TRUE}
out_dt(DATA_RAISINGS, "DATA_RAISINGS")
```