---
title: "IOTC statistical data reporting: Form 3AA (v`r BASE_VERSION`-update)"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  word_document2:
    reference_docx: "../templates/doc_template.docx"
    number_sections: FALSE
    reference_num: TRUE
    fig_caption: TRUE

  html_document2:
    css: "../templates/html_template.css"
    includes: 
      in_header: "../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---
  
# Description
  
This form supports the reporting of geographic position and description of each _fishing activity conducted around each anchored fish aggregated devices(AFAD), as **update,**_ along with estimates of retained catches and discards in numbers or live weight equivalent for the IOTC species, common sharks, and other bycatch species.

Click [here](https://data.iotc.org/reference/latest/forms/Form-3AA-update.xlsx) to download an empty version of form 3-AA-update, or [return back](../forms) to the list of all IOTC statistical data reporting forms.

# Reporting deadlines

- **Surface fisheries**: 30 June (final)

## Reporting metadata

### Submission information

| Element        | Requirement | Description | Format | Example |
| :--------| :----: | :----------------------- | :-------- | :------------ |
| [Focal point full name]{#fcname} | M | Name of the focal point in charge of the reporting of the data to the IOTC Secretariat | Plain text | John Doe  |
| [Focal point email]{#fcemail} | M | Email address of the focal point in charge of the reporting of the data to the IOTC Secretariat | Valid email address | John.Doe@fao.org |
| [Organisation name]{#orgname} | M | Name of the organisation in charge of the reporting of the data to the IOTC Secretariat | Plain text | National Institute of Fisheries |
| [Organisation email]{#orgemail} | O | Email address of the organisation in charge of the reporting of the data to the IOTC Secretariat | Valid email address | nif@gov.sc |
| [Finalisation date]{#findate} | M | Date of finalisation of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1996-03-27 |
| [Submission date]{#subdate} | M | Date of submission of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1997-03-21 |

### General information

| Element        | Requirement | Description | Code list  |
| :----------------- | :-----: | :----------------------- | :-------: |
| [Reporting year]{#repyear} | M | Gregorian calendar year of the fishing activities reported through the dataset | Integer |
| [Reporting entity]{#repentity} | M | Code of the entity reporting the dataset to the IOTC Secretariat | [Entity](#countries) |
| [Flag state]{#repflagstate} | M | Code of the country registration of the fishery vessels | [Countries](#countries) |
| Month | M | Gregorian calendar month of the fishing activities reported through the dataset | Integer |
| Fisheries   | M | Type of fishing practices based on several factors| [Fisheries](#fisheries)            |

### Data specifications

| Element        | Requirement | Description | Code list  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Original data type       | M | Preliminary/final status of the data | [Type of data](#types)      |

## Data elements

### Main data elements

| Element        | Requirement | Description | Code list  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Day of the Month | M | Day of the month of the fishing activities reported through the dataset | Integer |
| Latitude| M | Horizontal distances north or south of the Equation   | in decimal degrees  |
| Longitude | M | Vertical distances east or west of the prime meridian | in decimal degrees |
| Species    | M | Species caught and discarded| [Species](#allSpecies)           |
| Type of fate    | M | Fate of fish caught (retained or discarded)| [Types of fate](#typesOfFate)           |
| Data raising             | M | Level of raising (i.e., extrapolation) | [Raisings](#raisings)| 
| Catch unit   | M | Units used to report the level of catches of a given species,|[Catch units](#catchUnits) |

### aFOB data

| Element        | Requirement | Description | Code list  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Identifier   | M | FOB identification (Deacon ID) | Plain text      |
| Type| M | Type of FOBs    | [AFOB types](#FOBtypes) |
| Activity    | M | Type of activities undertaken when visiting or deploying  FOB | [AFOB activity types](#FOBactivityTypes) |


## Additional information

Updated information of daily activities conducted around AFADs, including catches retained and discarded, of previously submitted data.

# Referenced codelists

## Administrative and geospatial domains

### Countries (ADM.COU) {#countries}

Reference codes modeling the flag / reporting country submitting a dataset to the IOTC Secretariat.

```{r collapse = TRUE}
out_dt(COUNTRIES, "COUNTRIES")
```


## Fisheries and fishing technologies domains

### Fisheries (FIS) {#fisheries}

An *ad-hoc* classification derived from a combination of several factors (purpose, area of operation, vessel size category, gear, gear configuration, fishing mode and target species) that uniquely describe fishing practices for groups of vessels.

An [*interactive wizard*](https://data.iotc.org/fisheries/wizard) to help CPCs identify the IOTC code for their fisheries (among those currently considered of relevance in the Indian Ocean).

```{r collapse = TRUE}
out_dt(FISHERIES, "FISHERIES")
```
### Data types (DTA.TY) {#types}

Reference codes modeling the type of statistics provided through a specific form, and in particular if these are:

a)    preliminary if the statistics were estimated by using some information from the fishery and year concerned, and the data reported are likely to change in the future as more information become available; or
b)    final if the statistics were estimated by using the complete set of data from the fishery and year concerned, and the data reported are unlikely to change in the future.

```{r collapse = TRUE}
out_dt(DATA_TYPES, "DATA_TYPES")
```

## Biological and morphometrics domains

### All species (SPC.ALL) {#allSpecies}

Reference codes modeling the species interacting with the fisheries as:

-   target species (retained or discarded)
-   bycatch species (retained or discarded)
-   sampled individuals
-   etc.

These codelists are subsets of the entries in the [ASFIS](https://www.fao.org/fishery/en/collection/asfis/en) list of species for fishery statistics purposes, from which they inherit the alphabetic codes, English, French and scientific names, as well as the family and order, and add the species category (in the IOTC sense), the IUCN status (retrieved from the [IUCN red list](https://www.iucnredlist.org) of endangered species) and other characteristics of each entry such as their status of single species / species aggregate, bait species, SSI species, IOTC species.

```{r collapse = TRUE}
out_dt(SPECIES, "SPECIES")
```


## Data and metadata domains


### Types of anchored fishing object (aFOB) (FOB.AFT) {#FOBtypes}

Reference codes that model the types of anchored FOBs.

```{r collapse = TRUE}
out_dt(FOB_TYPES, "FOB_TYPES")
```

### Types of anchored fishing activity types (aFOB) (FOB.AAT) {#FOBactivityTypes}

Reference codes that model the type of activities undertaken when interacting with an anchored FOB.

```{r collapse = TRUE}
out_dt(AFOB_ACTIVITIES, "AFOB_ACTIVITIES")
```

### Type of fate (SPC.FTT) {#typesOfFate}

Reference codes used to identify a given fate as indicating that the fish has been retained or discarded.

```{r collapse = TRUE}
out_dt(TYPES_OF_FATE, "TYPES_OF_FATE")
```

### Raising (DTA.RA) {#raisings}

Reference codes modeling the level of raising applied to the data, and in particular if data:

-  have been raised to the represent the total catches and effort in the year concerned (RT),
-  have been raised but does not represent the total catches and effort in the year concerned (PR), or
-  have not been raised at all (NR)

```{r collapse = TRUE}
out_dt(DATA_RAISINGS, "DATA_RAISINGS")
```

### Catch units (FIA.CU) {#catchUnits}

Reference codes that model the units used to report the level of catches / discards of a given species, further stratified by the specific criteria characterizing each reporting form.

```{r collapse = TRUE}
out_dt(CATCH_UNITS, "CATCH_UNITS")
```