---
title: "IOTC statistical data reporting: Form 3AA (v`r BASE_VERSION`)"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  word_document2:
    reference_docx: "../templates/doc_template.docx"
    number_sections: FALSE
    reference_num: TRUE
    fig_caption: TRUE

  html_document2:
    css: "../templates/html_template.css"
    includes: 
      in_header: "../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---
  
# Description
  
This form provides for the annual reporting of fishing activities conducted around anchored fish aggregated devices (AFADs) located in the IOTC area of competence along with estimates of retained catches and discards for the IOTC species, common sharks, and other bycatch species caught in association with IOTC fisheries.

Click [here](../forms/Form-3AA.xlsx) to download a blank version of Form 3-AA, or [return](../forms) to the list of all IOTC statistical data reporting forms. The form allows reporting updated data for multiple fisheries simultaneously. Click [here](../forms/Form-3AA-update.xlsx) to download a blank version of Form 3-AA which has been designed to report updated data for a single fishery.

# Data content

Daily information on AFOB-related activities along with estimates of total number and/or live weight of retained catches and discards by species, fate, raising status, and catch unit.

## General information

| Element | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Reporting year | M | Gregorian calendar year of the fishing activities reported through the dataset | Integer |
| Reporting entity | M | Entity reporting the dataset to the IOTC Secretariat | **Code** From [Entities](#entities) |
| Flag state | M | Country registration of the fishing vessels | **Code** from [Countries](#countries) |

## Main data elements

| Element | Requirement | Description | Input value |
| :----------------- | :-----: | :----------------------- | :-------: |
| Month | M | Gregorian calendar month of the fishing activities reported through the dataset | Integer 1..12 |
| Day of the month | M | Day of the month of the fishing activities reported through the dataset | Integer 1..31 |
| Fisheries | M | Type of fishing practices based on several factors| **Code** from [Fisheries](#fisheries)            |
| Latitude | M | Horizontal distances north or south of the Equator | Decimal degrees  |
| Longitude | M | Vertical distances east or west of the prime meridian | Decimal degrees |
| Species | M | Species caught and discarded | **Code** from [Species](#allSpecies)           |
| Type of fate | M | Fate of fish caught (retained or discarded) | **Code** from [Types of fate](#typesOfFate)           |
| Data raising | M | Level of raising (i.e., extrapolation) | **Code** from [Raisings](#raisings) | 
| Catch unit | M | Units used to report the level of catches of a given species | **Code** from [Catch units](#catchUnits) |

## AFOB data

| Element | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Identifier | M | Unique identifier of the floating object | Plain text      |
| Type | M | Type of anchored floating object | **Code** from [AFOB types](#AFOBtypes) |
| Activity | M | Type of activities undertaken when visiting or deploying an anchored floating object | **Code** from [AFOB activity types](#AFOBactivityTypes) |

# Reporting metadata

| Element | Requirement | Description | Format | Example |
| :--------| :----: | :----------------------- | :-------- | :------------ |
| Liaison officer full name | M  | Name of the liaison officer in charge of the compilation of the data | Plain text | John Doe |
| Liaison officer email	 | M | Email address of the liaison officer in charge of the compilation of the data | Valid email address | [John.Doe\@fao.org](mailto:John.Doe@fao.org){.email} |
| Organisation name | M | Name of the organisation in charge of the compilation of the data | Plain text | National Institute of Fisheries |
| Organisation email | O | Email address of the organisation in charge of the compilation of the data | [nif\@gov.sc](mailto:nif@gov.sc){.email} |
| Finalisation date | M | Date of finalisation of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1996-03-27 |
| Submission date | O | Date of submission of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1997-03-21 |

# Reporting deadlines

- **Surface fisheries**: 30 June (final)

# Reference code lists

## Entities {#entities}

```{r collapse = TRUE}
out_dt(ENTITIES, "ENTITIES")
```

## Countries {#countries}

```{r collapse = TRUE}
out_dt(COUNTRIES, "COUNTRIES")
```

## Fisheries {#fisheries}

```{r collapse = TRUE}
out_dt(FISHERIES, "FISHERIES")
```

## Species {#allSpecies}

```{r collapse = TRUE}
out_dt(SPECIES, "SPECIES") %>% formatStyle(columns = "NAME_SCIENTIFIC", fontStyle = "italic")
```

## Types of data {#types}

```{r collapse = TRUE}
out_dt(DATA_TYPES, "DATA_TYPES")
```

## Types of anchored fishing objects {#AFOBtypes}

```{r collapse = TRUE}
out_dt(AFOB_TYPES, "AFOB_TYPES")
```

## Types of activities on anchored floating objects {#AFOBactivityTypes}

```{r collapse = TRUE}
out_dt(AFOB_ACTIVITIES, "AFOB_ACTIVITIES")
```

## Types of fates {#typesOfFate}

```{r collapse = TRUE}
out_dt(TYPES_OF_FATE, "TYPES_OF_FATE")
```

## Raisings {#raisings}

```{r collapse = TRUE}
out_dt(DATA_RAISINGS, "DATA_RAISINGS")
```

## Catch units {#catchUnits}

```{r collapse = TRUE}
out_dt(CATCH_UNITS, "CATCH_UNITS")
```
