---
title: "IOTC statistical data reporting: Form 3DA (v`r BASE_VERSION`)"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  word_document2:
    reference_docx: "../templates/doc_template.docx"
    number_sections: FALSE
    reference_num: TRUE
    fig_caption: TRUE

  html_document2:
    css: "../templates/html_template.css"
    includes: 
      in_header: "../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---
  
# Description

This form provides for the reporting of data on operational activities conducted by purse seine and support vessels on drifting floating objects (DFOBs) and buoys. When present, data include information on buoy identifier, knowledge of the buoy position, and type of activity conducted on the buoy. For each DFOB, information on materials (i.e., presence of plastic or metal), dimensions (i.e., length, width, and height), and presence of mesh with value of mesh size for both the surface (i.e., raft) and subsurface (i.e., tail) components must be recorded. Finally, species-specific estimates of catches retained and discarded in numbers or live weight equivalent for the IOTC species, common sharks, and other bycatch species caught in association with IOTC fisheries must also be included in the dataset.

Click [here](../forms/Form-3DA.xlsx) to download a blank version of Form 3-DA, or [return](../forms) to the list of all IOTC statistical data reporting forms.

# Data content

Operational information on DFOB-related activities, including buoys and DFOB characteristics and dimensions, along with estimates of retained catches and discards (in numbers or live weight equivalent) by species, fate, raising status, and catch unit.

# Stratification

## General information

| Element | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Reporting year | M | Gregorian calendar year of the fishing activities reported through the dataset | Integer, e.g., 1996 |
| Reporting entity | M | Code of the entity reporting the dataset to the IOTC Secretariat | **Code** from [Entities](#entities) |
| Flag state | M | Code of the country registration of the fishery vessels | **Code** from [Countries](#countries) |
| Reporting month | M | Calendar month of the fishing activities reported through the dataset | Integer 1..12 |

## Data specifications

| Element | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Original data type | M | Preliminary/final status of the data | **Code** from [Types of data](#datatypes) |

## Main data elements

| Element | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Vessel name | M | Name of vessel monitoring the buoy | Plain text  |
| Vessel IOTC number | M | IOTC registered number of the vessel monitoring the buoy | Plain text (e.g., IOTC013542) || Day of the month | M | Day of the month of the fishing activities reported through the dataset | Integer 1..31 |
| UTC time  | M | Universal time at which the drifting floating object was visited | time (_hh:mm_) |
| Latitude  | M | Horizontal distances north or south of the Equator | Decimal degrees  |
| Longitude | M | Vertical distances east or west of the prime meridian | Decimal degrees |
| Species | M | Species caught and discarded | **Code** from [Species](#allSpecies) |
| Type of fate | M | Fate of fish caught (retained or discarded) | **Code** from [Types of fate](#typesOfFate) |
| Data raising | M | Level of raising (i.e., extrapolation) | **Code** from [Raisings](#raisings) | 
| Catch unit   | M | Unit used to report the value of catch of a given species | **Code** from [Catch units](#catchUnits) |

## Buoy data

| Element | Requirement | Description | Input value |
| :----------------- | :-----: | :----------------------- | :-------: |
| Present | M | Indicates whether a buoy is attached to the drifting floating object | Boolean (Y/N) |
| Identifier | M | Unique identifier of buoy monitored | (e.g., ISD+, M3+, T8E) followed by 5-9 digits | Plain text |
| Position | M | Indicates whether the vessel have access/knowledge of the buoy position | Boolean (Y/N) |
| Activity | M | Type of activities undertaken when visiting or deploying the drifting floating object | **Code** from [Buoy activity types](#DFOBbuoyActivityTypes) |

## DFOB data

| Element | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Identifier | M | Unique identifier of the drifting floating object | Plain text |
| Type | M | Type of drifting floating object | **Code** from [Types of DFOBs](#FOBtypes) |
| Activity | M | Type of activity undertaken when visiting or deploying the drifting floating object | **Code** from [Types of DFOB activities](#FOBactivityTypes) |

### DFOB characteristics 

Description of the materials and dimensions of both *surface* and *subsurface* components of the drifting floating objects.

#### Surface (raft)

| Element | Requirement | Description | Unit  | Format  |
|:---------------| :----: | :----------------------|:------------|:------------------|
| Plastic  | M | Indicates whether the surface or near-surface structure of the drifting floating object contains some plastic materials | - | Boolean (Y/N) |
| Metal  | M | Indicates whether the surface or near-surface structure of the drifting floating object contains some metal materials | - | Boolean (Y/N) |
| Length | M | Length of the surface or near-surface structure of the drifting floating object | cm | Decimal |
| Width  | O |  Width of the surface or near-surface structure of the drifting floating object  | cm | Decimal |
| Height | O | Height of the surface or near-surface structure of the drifting floating object | cm | Decimal | 
| Mesh   | M | Indicates whether the surface or near-surface structure of the drifting floating object contains mesh | - | Boolean (Y/N) |
| Mesh size | O | Size of the main net mesh used on the surface or near-surface structure of the drifting floating object (if any) | mm | Decimal |

#### Subsurface (tail)

| Element | Requirement | Description | Unit  | Format  |
| :---------------| :---: | :----------------------|:------------|:------------------|
| Plastic  | M | Indicates whether the tail of the drifting floating object contains some plastic materials | - | Boolean (Y/N) |
| Metal | M | Indicates whether the tail of the drifting floating object contains some metal materials | - | Boolean (Y/N) |
| Length | M |  Length of the subsurface structure of the drifting floating object | cm | Decimal |
| Width  | O | Width of the subsurface structure of the drifting floating object  | cm | Decimal |
| Height | O | Height of the subsurface structure of the drifting floating object | cm | Decimal |
| Mesh | M | Indicates whether the subsurface structure of the drifting floating object contains mesh | - | Boolean (Y/N) |
| Mesh size | O | Size of the main net mesh used on the subsurface structure of the drifting floating object (if any) | mm | Decimal |

# Reporting metadata

| Element | Requirement | Description | Format | Example |
| :--------| :----: | :----------------------- | :-------- | :------------ |
| Liaison officer full name | M  | Name of the liaison officer in charge of the compilation of the data | Plain text | John Doe |
| Liaison officer email	 | M | Email address of the liaison officer in charge of the compilation of the data | Valid email address | [John.Doe\@fao.org](mailto:John.Doe@fao.org){.email} |
| Organisation name | M | Name of the organisation in charge of the compilation of the data | Plain text | National Institute of Fisheries |
| Organisation email | O | Email address of the organisation in charge of the compilation of the data | [nif\@gov.sc](mailto:nif@gov.sc){.email} |
| Finalisation date | M | Date of finalisation of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1996-03-27 |
| Submission date | O | Date of submission of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1997-03-21 |

# Reporting deadlines

- **Surface fisheries**: 30 June (final)

# Reference code lists

## Entities {#entities}

```{r collapse = TRUE}
out_dt(ENTITIES, "ENTITIES")
```

## Countries {#countries}

```{r collapse = TRUE}
out_dt(COUNTRIES, "COUNTRIES")
```

## Types of data {#datatypes}

```{r collapse = TRUE}
out_dt(DATA_TYPES, "DATA_TYPES")
```

## Fisheries {#fisheries}

```{r collapse = TRUE}
out_dt(FISHERIES, "FISHERIES")
```

## Species {#allSpecies}

```{r collapse = TRUE}
out_dt(SPECIES, "SPECIES")
```

## Types of buoy activities {#FOBbuoyActivityTypes}

```{r collapse = TRUE}
out_dt(BUOY_ACTIVITIES, "BUOY_ACTIVITIES")
```

## Types of drifting floating objects {#FOBtypes}

```{r collapse = TRUE}
out_dt(DFOB_TYPES, "DFOB_TYPES")
```

## Types of activities on drifting floating objects {#DFOBactivityTypes}

```{r collapse = TRUE}
out_dt(DFOB_ACTIVITIES, "DFOB_ACTIVITIES")
```

## Types of fates {#typesOfFate}

```{r collapse = TRUE}
out_dt(TYPES_OF_FATE, "TYPES_OF_FATE")
```

## Raisings {#raisings}

```{r collapse = TRUE}
out_dt(DATA_RAISINGS, "DATA_RAISINGS")
```

## Catch units {#catchUnits}

```{r collapse = TRUE}
out_dt(CATCH_UNITS, "CATCH_UNITS")
```