---
title: "IOTC statistical data reporting: Form 3BU (v`r BASE_VERSION`)"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  word_document2:
    reference_docx: "../templates/doc_template.docx"
    number_sections: FALSE
    reference_num: TRUE
    fig_caption: TRUE
      
  html_document2:
    css: "../templates/html_template.css"
    includes: 
      in_header: "../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---

# Description

This form supports the reporting of _single daily buoy position (latitude and longitude in decimal degrees)_ for each of the buoys monitored by each purse seine vessel. Each buoy is identified by its unique identifier which is a concatenation of the acronym of the buoy commercial model (e.g., ISD+, M3+, T8E) followed by 5-9 digits depending on the buoy model.

# Resources

Click [here](https://data.iotc.org/reference/latest/forms/Form-3BU.xlsx) to download an empty version of form 3-BU, or
[return back](..) to the list of all IOTC statistical data reporting forms.

# Supported resolutions

Daily positions of active buoys equipping FADs and natural floating objects for each purse seine vessel

- Res. [19/02, para.24](https://iotc.org/cmm/resolution-1902-procedures-fish-aggregating-devices-fads-management-plan) -- _Procedures on a fish aggregating devices (FADS) management plan_


# Reporting deadlines

- _Surface fisheries_: 
**To be submitted with a time delay of at least 60 days, but no longer than 90 days**


# Stratification

## Reporting metadata

- [Focal point full name](#fcname)
- [Focal point email](#fcemail)
- [Organisation name](#orgname)
- [Organisation email](#orgemail)
- [Finalisation date](#findate)
- [Submission date](#subdate)
- [Reporting year](#repyear)
- [Reporting entity](#repentity)
- [Flag state](#repflagstate)
- [Types of data](#types)

### Vessel operation

- Month
- Vessel IOTC number
- Vessel name


## Main data elements

- Day of month
- Buoy ID
- Latitude (in decimal degrees)
- Longitude (in decimal degrees)


# Referenced codelists

## Administrative and geospatial domains
                  
### Countries (ADM.COU) {#countries}

Reference codes modeling the flag / reporting country submitting a dataset to the IOTC Secretariat.
                  
```{r collapse = TRUE}
out_dt(COUNTRIES, "COUNTRIES")
```

## Data and metadata domains

### Data types (DTA.TY) {#types}

Reference codes modeling the type of statistics provided through a specific form, and in particular if these are:

a)    preliminary if the statistics were estimated by using some information from the fishery and year concerned, and the data reported are likely to change in the future as more information become available; or
b)    final if the statistics were estimated by using the complete set of data from the fishery and year concerned, and the data reported are unlikely to change in the future.

```{r collapse = TRUE}
out_dt(DATA_TYPES, "DATA_TYPES")
```

