---
title: "IOTC statistical data reporting: Form 7PR (v`r BASE_VERSION`)"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  word_document2:
    reference_docx: "../templates/doc_template.docx"
    number_sections: FALSE
    reference_num: TRUE
    fig_caption: TRUE

  html_document2:
    css: "../templates/html_template.css"
    includes: 
      in_header: "../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---
  
# Description
  
This form supports the *voluntary* reporting of _average market prices of fish per type of fish product_ for a given CPC / fleet.

Data should be provided per type of fish product, preservation, processing and monthly.

# Resources

Click [here](https://data.iotc.org/reference/latest/forms/Form-7PR.xlsx) to download an empty version of form 7-PR, or [return back](..) to the list of all IOTC statistical data reporting forms.

# Reporting deadlines

-   **Longline fisheries**: 30 June (preliminary), 30 December (final)
-   **Surface fisheries**: 30 June (final)
-   **Coastal fisheries**: 30 June (final)

# Stratification

## Reporting metadata

### Submission information

| Element        | Requirement | Description | Format | Example |
| :--------| :----: | :----------------------- | :-------- | :------------ |
| [Focal point full name]{#fcname} | M | Name of the focal point in charge of the reporting of the data to the IOTC Secretariat | Plain text | John Doe  |
| [Focal point email]{#fcemail} | M | Email address of the focal point in charge of the reporting of the data to the IOTC Secretariat | Valid email address | John.Doe@fao.org |
| [Organisation name]{#orgname} | M | Name of the organisation in charge of the reporting of the data to the IOTC Secretariat | Plain text | National Institute of Fisheries |
| [Organisation email]{#orgemail} | O | Email address of the organisation in charge of the reporting of the data to the IOTC Secretariat | Valid email address | nif@gov.sc |
| [Finalisation date]{#findate} | M | Date of finalisation of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1996-03-27 |
| [Submission date]{#subdate} | M | Date of submission of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1997-03-21 |


### General information


| Element        | Requirement | Description | Code list  |
| :----------------- | :-----: | :----------------------- | :-------: |
| [Reporting year]{#repyear} | M | Gregorian calendar year of the fishing activities reported through the dataset | Integer |
| [Reporting entity]{#repentity} | M | Code of the entity reporting the dataset to the IOTC Secretariat | [Entity](#countries) |
| [Flag state]{#repflagstate} | M | Code of the country registration of the fishery vessels | [Countries](#countries) |


## Data elements

### Main data elements

| Element        | Requirement | Description | Code list  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Quarter | M | Gregorian calendar quarterly of the fishing activities reported through the dataset | Integer |
| Ocean   | M | The ocean the species caught| [Fisheries](#fisheries)            |
| Pricing location| M | Location the price collected   | [IOTC main areas](#IOTCareasMain)  |
| Currency | M | Currency of the price| [Reasons for retaining](#retainReasons) |
| Species    | M | Species caught and discarded| [Species](#allSpecies)           |
| Processing    | M | Species processing type for the price reported| [Species](#allSpecies)           |
| Product type    | M | The type of product for price reported| [Species](#allSpecies)           |
| Preservation type    | M | The type of preservation of product | [Species](#allSpecies)           |
| Destination    | M | Market destination| [Species](#allSpecies)           |
| Weight unit    | M | Weight units used| [Species](#allSpecies)           |
| Weight class(lo)    | M | Lowest size class of the weight| [Species](#allSpecies)           |
| Weight class(hi)   | M | Highest size class of the weight| [Species](#allSpecies)           |







# Reference species groups

+ **IOTC species** [ mandatory ] 
+ **Sharks** [ mandatory ]
+ **Mobulids and rays** [ mandatory ]
+ **Other bycatch / non-IOTC species** [ voluntary ]

# Reporting deadlines

+ **All fisheries**: 30 June

# Stratification

## Main data fields

+ Monthly (possibly)
+ [Ocean](#IOTCareas)
+ [Price location](#location)

      
## Additional data fields

+ [Destination](#destination)
+ [Spcies](#species)

# Referenced codelists

## Administrative and geospatial domains

### Countries (ADM.COU) {#countries}

Reference codes modeling the flag / reporting country submitting a dataset to the IOTC Secretariat.

```{r collapse = TRUE}
out_dt(COUNTRIES, "COUNTRIES")
```

### FAO areas (GIS.FAO) {#FAO_AREAS}

[FAO fishing areas](https://www.fao.org/fishery/en/area/search)


Reference codes modelling the FAO main areas.

```{r collapse = TRUE}
out_dt(FAO_AREAS, "FAO_AREAS")
```


## Fisheries and fishing technologies domains

### Fisheries (FIS) {#fisheries}

An _ad-hoc_ classification derived from a combination of several factors (purpose, area of operation, vessel size category, gear, gear configuration, fishing mode and target species) that uniquely describe fishing practices for groups of vessels.

An [_interactive wizard_](https://data.iotc.org/fisheries/wizard) to help CPCs identify the IOTC code for  their fisheries (among those currently considered of relevance in the Indian Ocean).

```{r collapse = TRUE}
out_dt(FISHERIES, "FISHERIES")
```

### Catch units (FIA.CU) {#catchUnits}

Reference codes that model the units used to report the level of catches / discards of a given species, further stratified by the specific criteria characterizing each reporting form.

```{r collapse = TRUE}
out_dt(CATCH_UNITS, "CATCH_UNITS")
```

## Biological and morphometrics domains

### All species (SPC.ALL) {#allSpecies}

Reference codes modeling the species interacting with the fisheries as:
  
  + target species (retained or discarded)
+ bycatch species (retained or discarded)
+ sampled individuals
+ etc.

These codelists are subsets of the entries in the [ASFIS](https://www.fao.org/fishery/en/collection/asfis/en) list of species for fishery statistics purposes, from which they inherit the alphabetic codes, English, French and scientific names, as well as the family and order, and add the species category (in the IOTC sense), the IUCN status (retrieved from the [IUCN red list](https://www.iucnredlist.org
) of endangered species) and other characteristics of each entry such as their status of single species / species aggregate, bait species, SSI species, IOTC species.

```{r collapse = TRUE}
out_dt(SPECIES, "SPECIES")
```

### Reasons for discarding (SPC.FTE.DI) {#discardReasons}

Reference codes that model the reasons why aquatic creatures caught by the fishery are then discarded at sea.

```{r collapse = TRUE}
out_dt(DISCARD_REASONS, "DISCARD_REASONS")
```

### Individual conditions (SPC.CN) {#individualConditions}

Reference codes modeling the conditions (at capture / at release) of individual aquatic creatures being discarded at sea or measured.

```{r collapse = TRUE}
out_dt(INDIVIDUAL_CONDITIONS, "INDIVIDUAL_CONDITIONS")
```

## Data and metadata domains

### Data types (DTA.TY) {#dataTypes}

Reference codes modeling the type of data provided through a specific form (preliminary / final / unknown).

```{r collapse = TRUE}
out_dt(DATA_TYPES, "DATA_TYPES")
```

### Data raising (DTA.RA) {#dataRaising}

Reference codes modeling the level of raising applied to the data (raised to totals / not raised to totals / unknown).

```{r collapse = TRUE}
out_dt(DATA_RAISINGS, "DATA_RAISINGS")
```

### Discarded catches data sources (DTA.SRC.DI) {#dataSourcesDI}

Reference codes modeling the source of the data provided through the discards data form.

```{r collapse = TRUE}
out_dt(DATA_SOURCES_DI, "DATA_SOURCES_DI")
```

### Discarded catches data processings (DTA.PRO.DI) {#dataProcessingsDI}

Reference codes modeling the processing applied to the data provided through the discards data form.

```{r collapse = TRUE}
out_dt(DATA_PROCESSINGS_DI, "DATA_PROCESSINGS_DI")
```

### Coverage types (DTA.COV.TY) {#coverageTypes}

Reference codes modeling the type of coverage for the raw information used to obtain the data provided through a specific form.

```{r collapse = TRUE}
out_dt(COVERAGE_TYPES, "COVERAGE_TYPES")
```