---
title: "IOTC statistical data reporting: Form 4SF (v`r BASE_VERSION`-update)"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  word_document2:
    reference_docx: "../templates/doc_template.docx"
    number_sections: FALSE
    reference_num: TRUE
    fig_caption: TRUE
      
  html_document2:
    css: "../templates/html_template.css"
    includes: 
      in_header: "../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---

# Description

This form provides for the monthly reporting of size-frequency estimates for IOTC species, as well as common sharks and other bycatch species caught in association with IOTC fisheries. The form allows reporting updated data for a single fishery.

Click [here](../forms/Form-4SF-update.xlsx) to download a blank version of Form 4-SF-update, or [return](../forms) to the list of all IOTC statistical data reporting forms.

# Data content

Number (or weight) of fish sample and raised estimates by size category and species, along with information on the value (%) and type of sampling coverage used for the estimations by month, year, fleet, fishery and geographical grid.

# Stratification

## General information

| Element | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Reporting year | M | Gregorian calendar year of the fishing activities reported through the dataset | Integer (e.g., 1996)  |
| Reporting entity | M | Code of the entity reporting the dataset to the IOTC Secretariat | **Code** from [Entities](#entities) |
| Flag state | M | Code of the country registration of the fishery vessels | **Code** from [Countries](#countries) |
| Fisheries | M | Type of fishing practices based on several factors| **Code** from [Fisheries](#fisheries) |
| Species | M | Species sampled | **Code** from [Species](#allSpecies) |

## Main data elements

| Element | Requirement | Description | Input value  |
| :----------------- | :-----: | :----------------------- | :-------: |
| Month | M | Month of the fishing activities reported through the dataset | Integer 1..12 |
| Grid | M | 5° grid area | **Code** from [Grid codes](#5x5Grids) |
| Sex | O | Sex of the fish sampled | **Code** from [Sex](#sex) |

## Sample data

| Element | Requirement | Description | Input value |
| :----------------- | :-----: | :----------------------- | :-------: |
| Size class (_low_) | M | The lowest size recorded for the sample | Integer |
| Size class (_high_) | M | The highest size recorded for the sample | Integer |
| Number of samples | M | Actual number of fish measured in the stratum | Integer |
| Number of fish  | M | Raised number of fish in the stratum | Integer |

## Data specifications

| Element | Requirement | Description | Code list |
| :----------------- | :-----: | :----------------------- | :-------: |
| Original data type | M | Preliminary/final status of the data | **Code** from [Type of data](#datatypes)      |
| Original data source | M | Source of information | **Code** from [Size frequency data sources](#sourcesSF)          |
| Original data processing | M | Processing applied to the data | **Code** from [Size frequency data processings](#processingsSF) |
| Data raising | M | Level of raising (i.e., extrapolation) | **Code** from [Raisings](#dataRaising)| 
| Source coverage type | O | Variable used for data coverage | **Code** from [Types of coverage](#coverageTypes) |
| Source coverage value | O | Value of coverage | Percentage (%) |
| Type of fate | M | Fate of fish caught (retained or discarded)| **Code** from [Types of fate](#typesOfFate)           |
| Fate | O | Reason for retained or discarded of the catch | **Code** from [Fate](#fates)  

## Measurements

| Element | Requirement | Description | Code list |
| :----------------- | :-----: | :----------------------- | :-------: |
| Type of Measurement | M | Given measurement types (weight or length) | **Code** from [Types of measurement](#typesOfMeasurement) |
| Measured type | M | Type of measure recorded | **Code** from [Measurements](#Measurement) |
| Measurement Tool | M | Tool used to take the measurement | **Code** from [Measurement tools](#allMeasurementTools) |
| Size interval | M | Size interval between lowest and highest measurements of the sampled species | Integer |

## Original data

| Element | Requirement | Description | Code list |
| :----------------- | :-----: | :----------------------- | :-------: |
| Estimation | M | Indicates if the data was estimated or actual recorded data | **Code** from [Estimations](#estimations) |

# Reporting metadata

| Element | Requirement | Description | Format | Example |
| :--------| :----: | :----------------------- | :-------- | :------------ |
| Liaison officer full name | M  | Name of the liaison officer in charge of the compilation of the data | Plain text | John Doe |
| Liaison officer email	 | M | Email address of the liaison officer in charge of the compilation of the data | Valid email address | [John.Doe\@fao.org](mailto:John.Doe@fao.org){.email} |
| Organisation name | M | Name of the organisation in charge of the compilation of the data | Plain text | National Institute of Fisheries |
| Organisation email | O | Email address of the organisation in charge of the compilation of the data | [nif\@gov.sc](mailto:nif@gov.sc){.email} |
| Finalisation date | M | Date of finalisation of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1996-03-27 |
| Submission date | M | Date of submission of the dataset | [ISO 8601](https://en.wikipedia.org/wiki/ISO_8601) | 1997-03-21 |

# Reporting deadlines

+ **Longline fisheries**: 30 June (preliminary), 30 December (final)
+ **Surface fisheries**: 30 June (final)
+ **Coastal fisheries**: 30 June (final)

# Additional information

### The spatial and temporal resolutions, and catch units

| Category | Temporal resolution | Spatial resolution | Catch unit |
| :-------- | :--------- | :---------- | :------------- |
All fisheries  | Month | [5° grid area](https://data.iotc.org/reference/1.0.0/domain/admin/#IOgrids5x5) or finer for the SC | number of fish |

# Reference code lists

## Entities {#entities}

```{r collapse = TRUE}
out_dt(ENTITIES, "ENTITIES")
```

## Countries {#countries}

```{r collapse = TRUE}
out_dt(COUNTRIES, "COUNTRIES")
```

## IOTC 5° grids {#5x5Grids}

```{r collapse = TRUE}
out_dt(IOTC_GRIDS_SF, "AREAS_IOTC_05")
```

## Fisheries {#fisheries}

```{r collapse = TRUE}
out_dt(FISHERIES, "FISHERIES")
```

## Types of measurement {#typesOfMeasurement}

```{r collapse = TRUE}
out_dt(TYPES_OF_MEASUREMENT, "TYPES_OF_MEASUREMENT")
```

## Measurements {#Measurements}

```{r collapse = TRUE}
out_dt(MEASUREMENTS, "MEASUREMENTS")
```

## Measurement tools {#allMeasurementTools}

```{r collapse = TRUE}
out_dt(MEASUREMENT_TOOLS, "MEASUREMENT_TOOLS")
```

## Types of fate {#typesOfFate}

```{r collapse = TRUE}
out_dt(TYPES_OF_FATE, "TYPES_OF_FATE")
```

## Fates {#fates}

```{r collapse = TRUE}
out_dt(FATES, "FATES")
```

## Sexes {#sex}

```{r collapse = TRUE}
out_dt(SEX, "SEX")
```

## Species {#allSpecies}

```{r collapse = TRUE}
out_dt(SPECIES, "SPECIES") %>% formatStyle(columns = "NAME_SCIENTIFIC", fontStyle = "italic")
```

## Types of data {#datatypes}

```{r collapse = TRUE}
out_dt(DATA_TYPES, "DATA_TYPES")
```

## Data raising {#dataRaising}

```{r collapse = TRUE}
out_dt(DATA_RAISINGS, "DATA_RAISINGS")
```

## Size-frequency data sources {#sourcesSF}

```{r collapse = TRUE}
out_dt(DATA_SOURCES_SF, "DATA_SOURCES_SF")
```

## Size-frequency data processings {#processingsSF}

```{r collapse = TRUE}
out_dt(DATA_PROCESSINGS_SF, "DATA_PROCESSINGS_SF")
```

## Types of coverage types {#coverageTypes}

```{r collapse = TRUE}
out_dt(COVERAGE_TYPES, "COVERAGE_TYPES")
```

## Estimations {#estimations}

```{r collapse = TRUE}
out_dt(DATA_ESTIMATIONS, "DATA_ESTIMATIONS")
```