---
title: "IOTC statistical data reporting: Legacy Form 1DR (v`r BASE_VERSION`)"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)" 
output:
  word_document2:
    reference_docx: "../templates/doc_template.docx"
    number_sections: FALSE
    reference_num: TRUE
    fig_caption: TRUE

  html_document2:
    css: "../templates/html_template.css"
    includes: 
      in_header: "../templates/google-analytics.html"
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
    smooth_scroll: FALSE
---
  
# Description
  
This form supports the reporting of the matrix of presence of species in the retained catches and discards of each fishing fleet and gear group. For each species/gear combination, the cell must be filled with either a value of one (1) in case of positive catch or a value of zero (0) in case of absence of catch (i.e., no landing and no discard). Species include IOTC species, mobulid rays, common sharks, and other bycatch species.

Click [here](../forms/legacy/Form-1DR-legacy.xlsx) to download a blank version of Form 1DR, or [return](../forms) to the list of all IOTC statistical data reporting forms.

# Data content

Indicate presence *(one (1) for positive or zero (0) for absence)* of species in the retained catches and discards, by year, fleet, fishery, and fishery categories.

## General information

| Element | Requirement | Description | Input value |
|:-----------------|:------------:|:------------------------|:------------:|
| [Reporting year]{#repyear}     | M | Gregorian calendar year of the fishing activities reported through the dataset |  Integer  |
| [CPC]{#repentity} | M | Entity reporting the dataset to the IOTC Secretariat |  **Code** from [Fleet](#LEGACY_FLEETS) |


## Main data elements

| Element | Description | Codelist |
| :----------- | :-------------------------- | :-------: |
| Species | Species include IOTC species, mobulid rays, common sharks, and other bycatch species, expected to be present by respective fisheries and gear groups | [Species](#species) |
| Gear groups | Gear groups catching IOTC species and other species of interest | [Gear groups](#gearGroups) |


# Reporting deadlines

- **All fisheries**: 30 June (final)

# Reference codelists

## Fleet {#LEGACY_FLEETS}

Reference codes modelling the flag / reporting country submitting the dataset to the IOTC Secretariat.

```{r collapse = TRUE}
out_dt(LEGACY_FLEETS, "LEGACY_FLEETS")
```

## Gear groups {#gearGroups}

Reference codes modelling the gear groups used to catch the fish species.

```{r collapse = TRUE}
out_dt(GEAR_GROUPS, "GEAR_GROUPS")
```

## Species {#species}

Reference codes modelling the species caught with the gear groups.

```{r collapse = TRUE}
out_dt(SPECIES, "SPECIES")
```

